### 2024-04-02 outputs/paper.qmd
new

---
title: "Evidence and Lessons from Public Health Funding's Impact on HIV/AIDS"
author: Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Funding_Fuels_the_HIV-AIDS_Fight.git. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
date: "April 2, 2024"
date-format: long
abstract: "This paper replicates and critically examines the study conducted by Marcus Dillender (2023) on the impact of the Ryan White CARE Act's Title I funding on HIV/AIDS outcomes. My replication focuses on the study's methodology, data integrity, and the robustness of its conclusions, particularly in the context of diagnosis and prevalence data. I assess the original findings through a reanalysis of public data sources and discuss the implications of our results for public health policy and future research directions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

# Introduction

Public health funding plays a crucial role in optimizing public health outcomes. To understand the impact of federal funding on HIV/AIDS healthcare, Marcus Dillender's paper "Evidence and Lessons on the Health Impacts of Public Health Funding from the Fight against HIV/AIDS" (2023) assesses the efficacy of Title I funding of the Ryan White Comprehensive AIDS Resources Emergency (CARE) Act [@Dillender2023]. By examining its impact on HIV/AIDS-related mortality and incidence rates, the paper reveals the impact of public funding.

In this paper, I aim to replicate Dillender's research using available public data and direct my attention to the non-mortality outcomes of the Ryan White CARE Act's Title I funding. I examine its influence on the diagnosis and prevalence rates of HIV/AIDS. It offers a unique perspective on HIV/AIDS-affected populations and potential public health interventions for enhancing their quality of life. Based on Dillender's methodology, I employ difference-in-differences and regression discontinuity designs to examine the sensitivity of the findings to different analyses. As a result of this reanalysis, the original study's results are validated and a dialogue on how to interpret public health data regarding policy impact assessments is stimulated.

This critical replication explores the complex issues surrounding public health funding. I analyze the interplay of financial inputs, health outcomes, and the socio-economic fabrics they weave into. I hope that this critical replication encourages a more nuanced approach to future research in public health finance and policy-making. Throughout this investigation, I keep an eye on societal, economic, and systemic factors that influence public health and how federal funding operates within that ecosystem.

# Data
My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].My reproduction seeks to address two findings written in the original paper.

## Source
The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from Evidence and Lessons on the Health Impacts of Public Health Funding from the Fight against HIV/AIDS, under Additional Materials.

## Variables
In progress

# Results
In progress

# Discussion
In progress

# Reference

### 2024-04-02 scripts/cdc_city_data.R

@@ -1,0 +1,5 @@
+library(dplyr)
+library(readr)
+library(readxl)
+
+

### 2024-04-02 scripts/city_data_preparation.R

@@ -1,0 +1,95 @@
+library(dplyr)
+library(readr)
+library(readxl)
+library(haven)
+library(tidyr)
+
+
+data_loc <- "/cloud/project/data" 
+
+
+# 1994 AIDS cases
+aids_cases_1994 <- read_tsv(file.path(data_loc, "aids_cases_rwca_1994.txt")) %>%
+  filter(!is.na(`Location Code`)) %>%
+  select(Cases, `Location Code`, Location) %>%
+  rename(cityfip = `Location Code`, aids_reported_by_1995 = Cases)
+write_csv(aids_cases_1994, file.path(data_loc, "interim/aids_cases_rwca_1994.csv"))
+
+# 1995 AIDS cases
+aids_cases_1995 <- read_tsv(file.path(data_loc, "aids_cases_rwca_1995.txt")) %>%
+  filter(!is.na(`Location Code`)) %>%
+  select(Cases, `Location Code`, Location) %>%
+  rename(cityfip = `Location Code`, aids_reported_in_1995 = Cases)
+write_csv(aids_cases_1995, file.path(data_loc, "interim/aids_cases_rwca_1995.csv"))
+
+title1_info <- read_excel(file.path(data_loc, "t1years.xlsx"), sheet = "Sheet1") %>%
+  filter(city != "Honolulu, HI", city != "San Juan, PR") %>%
+  mutate(
+    state_postal = substr(city, nchar(city)-1, nchar(city)),
+    state_postal = if_else(state_postal == "M.", "NM", state_postal),
+    cityfip = as.character(cityfip)  
+  ) %>%
+  left_join(read_csv(file.path(data_loc, "interim/aids_cases_rwca_1995.csv"), col_types = cols(cityfip = col_character())), by = "cityfip") %>%
+  left_join(read_csv(file.path(data_loc, "interim/aids_cases_rwca_1994.csv"), col_types = cols(cityfip = col_character())), by = "cityfip") %>%
+  mutate(
+    aids_ever_1995_imp = round(aids_reported_by_1995 + 0.25 * aids_reported_in_1995),
+    rank_1995 = row_number()
+  ) %>%
+  select(cityfip, year_rwca_status, aids_ever_1995_imp, rank_1995, state_postal)
+
+write_csv(title1_info, file.path(data_loc, "interim/t1years.csv"))
+
+
+# AIDS cases reported by year
[…]

### 2024-04-02 scripts/combine.R

@@ -1,0 +1,39 @@
+# Load necessary libraries
+if (!requireNamespace("dplyr", quietly = TRUE)) install.packages("dplyr")
+if (!requireNamespace("haven", quietly = TRUE)) install.packages("haven")
+
+library(dplyr)
+library(haven)
+
+# Define your data location (change paths as necessary)
+data_loc <- "/path/to/your/data"
+
+# Load your data
+seer_info_by_city <- read_dta(file.path(data_loc, "interim/seer_info_by_city.dta"))
+seer_info_by_city_hisp <- read_dta(file.path(data_loc, "interim/seer_info_by_city_hisp.dta"))
+vs_city_year <- read_dta(file.path(data_loc, "interim/vs_city_year.dta"))
+laus_city_data <- read_dta(file.path(data_loc, "interim/laus_city_data.dta"))
+t1years <- read_dta(file.path(data_loc, "interim/t1years.dta"))
+aids_cases_reported <- read_dta(file.path(data_loc, "interim/aids_cases_reported.dta"))
+aids_cases_diagnosed <- read_dta(file.path(data_loc, "interim/aids_cases_diagnosed.dta"))
+cdc_city_aids_prev <- read_dta(file.path(data_loc, "interim/cdc_city_aids_prev.dta"))
+cdc_city_aids_diagnosis <- read_dta(file.path(data_loc, "interim/cdc_city_aids_diagnosis.dta"))
+rwca_non_city <- read_dta(file.path(data_loc, "interim/rwca_non_city.dta"))
+agg_title1_funding_by_city <- read_dta(file.path(data_loc, "interim/agg_title1_funding_by_city.dta"))
+state_year_controls <- read_dta(file.path(data_loc, "interim/state_year_controls.dta"))
+vs_city_age_adjusted <- read_dta(file.path(data_loc, "interim/vs_city_age_adjusted.dta"))
+ann_years_lost_aids <- read_dta(file.path(data_loc, "interim/ann_years_lost_aids.dta"))
+
+# Example merge and manipulation (repeating this pattern for each merge)
+merged_data <- seer_info_by_city %>%
+  left_join(seer_info_by_city_hisp, by = c("year", "cityfip")) %>%
+  left_join(vs_city_year, by = c("cityfip", "year")) %>%
+  left_join(laus_city_data, by = c("cityfip", "year")) %>%
+  # Continue with the other datasets as above
+  # After all merges, perform any necessary mutations or filtering
[…]

### 2024-04-02 scripts/interim.R

@@ -1,0 +1,43 @@
+library(dplyr)
+library(haven)
+
+data_loc <- "path_to_your_data_folder" # Update with actual data location
+
+# Reading initial dataset
+seer_info <- read_dta(file.path(data_loc, "interim/seer_info_by_city.dta"))
+
+# Merge function to simplify merging process
+merge_data <- function(data, path, type = "inner", by = c("year", "cityfip")) {
+  file_path <- file.path(data_loc, path)
+  merge_func <- match.fun(paste0(type, "_join"))
+  data <- merge_func(data, read_dta(file_path), by = by)
+  if ("_merge" %in% names(data)) data <- data %>% select(-_merge) # Drop _merge if present
+  data
+}
+
+# Sequential merges
+files_to_merge <- c("interim/seer_info_by_city_hisp.dta", "interim/vs_city_year.dta", 
+                    "interim/laus_city_data.dta", "interim/t1years.dta", 
+                    "interim/aids_cases_reported.dta", "interim/aids_cases_diagnosed.dta", 
+                    "interim/cdc_city_aids_prev", "interim/cdc_city_aids_diagnosis", 
+                    "interim/rwca_non_city", "interim/agg_title1_funding_by_city.dta", 
+                    "interim/state_year_controls.dta", "interim/vs_city_age_adjusted.dta", 
+                    "interim/ann_years_lost_aids.dta")
+
+# Adjust merge type and by columns as needed per file
+for (file in files_to_merge) {
+  seer_info <- merge_data(seer_info, file, type = "inner")
+}
+
+# Generating new variables and replacing missing values
+seer_info <- seer_info %>%
+  mutate(across(starts_with("funding_"), ~replace(., is.na(.), 0)),
+         aids_dths_all_100k = aids_dths_all / pop_all * 100000,
+         laids_dths_all_100k = log(aids_dths_all_100k),
+         within30 = aids_ever_1995_imp < 7500 & aids_ever_1995_imp > 750,
+         # Add more conditions and variables as needed
+  ) %>%
+  arrange(cityfip, year)
+
+# Save processed data
+write_dta(seer_info, file.path(data_loc, "cleaned/rwca_sample.dta"))

### 2024-04-02 scripts/life_years_saved.R

@@ -1,0 +1,66 @@
+library(readxl)
+library(dplyr)
+library(haven)
+
+data_loc <- "/cloud/project/data"
+
+# Import Excel file
+ssa_life_tables <- read_excel(file.path(data_loc, "ssa_life_tables_2005.xlsx"), sheet = "Sheet1")
+
+# Temporarily save the data frame to an RDS file
+tempfile1 <- tempfile(fileext = ".rds")
+saveRDS(ssa_life_tables, tempfile1)
+
+library(readr)
+
+# Define the path to your raw data file
+raw_file_path <- "/cloud/project/data/Vs88mort.raw"
+
+
+vs_raw_data <- read_delim(raw_file_path, 
+                          delim = " ", 
+                          col_names = c("year", "aids_dths", "age_years", "male", "female"), 
+                          col_types = cols(
+                            year = col_integer(),
+                            aids_dths = col_integer(),
+                            age_years = col_integer(),
+                            male = col_integer(),
+                            female = col_integer()
+                          ),
+                          trim_ws = TRUE)
+
+# Check the first few rows to ensure it was read correctly
+head(vs_raw_data)
+
+
+
+
+# Read the Stata data file
+vs_raw_data <- read_csv(file.path(data_loc, "interim/vs_raw_data.csv")) %>%
+  filter(year > 1987 & year < 2019, aids_dths == 1, !is.na(age_years)) %>%
+  select(year, age_years, male, female) %>%
+  rename(age = age_years)
+
+# Load the life tables data from the temporary file
+life_tables <- readRDS(tempfile1)
+
+# Merge the data frames
+merged_data <- vs_raw_data %>%
+  left_join(life_tables, by = c("age" = "age")) %>%
+  filter(!is.na(male_life_expectancy), !is.na(female_life_expectancy)) %>%
+  mutate(
+    from_2018 = 2019 - year,
+    years_lost_proj = if_else(male == 1, male_life_expectancy, female_life_expectancy),
+    years_lost_proj_10y = if_else(years_lost_proj > 10, 10, years_lost_proj),
+    years_lost_through_2018 = if_else(years_lost_proj > from_2018, from_2018, years_lost_proj),
+    years_lost_through_2018_10y = if_else(years_lost_through_2018 > 10, 10, years_lost_through_2018)
+  ) %>%
+  group_by(year) %>%
+  summarise(
[…]

### 2024-04-02 scripts/mortality.R

@@ -1,0 +1,12 @@
+library(dplyr)
+library(readr)
+library(readxl)
+library(stringr)
+
+# Define the data location
+data_loc <- "path/to/your/data"
+do_loc <- "path/to/dictionary/location"
+
+# Adjust the paths to your actual files
+mortality_file_path <- file.path(data_loc, "data_restricted/mortality_from_cdc/MortAC1995/MULT1995.AllCnty/MULT1995.AllCnty.txt")
+vital_stats_1995_dict_path <- file.path(do_loc, "build/vital_stats_1995_dict.dct")

### 2024-04-02 scripts/pop_emp.R

@@ -1,0 +1,26 @@
+library(readr)
+
+data_file_path <- paste0(data_loc, "/data_public/us.1969_2018.singleages.adjusted.txt")
+
+seer_population_data <- read_fwf(file = data_file_path,
+                                 col_positions = fwf_positions(
+                                   start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
+                                   end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
+                                   col_names = c("year", "state_postal", "statefip", "countyfip", "registry", "race", "origin", "sex", "age", "population")
+                                 ),
+                                 col_types = cols(
+                                   year = col_integer(),
+                                   state_postal = col_character(),
+                                   statefip = col_integer(),
+                                   countyfip = col_integer(),
+                                   registry = col_integer(),
+                                   race = col_integer(),
+                                   origin = col_integer(),
+                                   sex = col_integer(),
+                                   age = col_integer(),
+                                   population = col_double()
+                                 )
+)
+
+
+

### 2024-04-02 scripts/read_pub_mort.R

@@ -1,0 +1,13 @@
+library(readr)
+
+
+col_widths <- fwf_widths(c(5, 3, 2, 4, 1, 3, 2, 4, 3),
+                         c("STATEOCC", "CONTYOCC", "ICD34", "RACE_DET", "DEATHMO", "SEX", "ICD9", "AGEREC12", "AGEDET"))
+
+file_path_87 <- "/cloud/project/data/MORT87.PUB"
+file_path_88 <- "/cloud/project/data/Vs88mort.raw" 
+
+# Read the files
+mort_87_data <- read_fwf(file_path_87, col_positions = col_widths)
+mort_88_data <- read_fwf(file_path_88, col_positions = col_widths)
+

### 2024-04-02 scripts/rwca_allocations.R

@@ -1,0 +1,52 @@
+library(readxl)
+library(dplyr)
+library(readr)
+
+data_loc <- "/cloud/project/data" 
+
+# Read the prices data and process it
+prices_fred <- read_excel(file.path(data_loc, "prices_fred.xls"), sheet = "FRED Graph") %>%
+  mutate(year = lubridate::year(date)) %>%
+  group_by(year) %>%
+  summarise(cpi = mean(cpi, na.rm = TRUE)) %>%
+  filter(year > 1990, year < 2019)
+
+# Temporarily save the processed data
+tempfile1 <- tempfile(fileext = ".rds")
+saveRDS(prices_fred, tempfile1)
+
+# Read the title1 funding data and merge with the prices data
+title1_funding <- read_excel(file.path(data_loc, "title1.xls"), sheet = "Sheet1") %>%
+  left_join(readRDS(tempfile1), by = "year") %>%
+  mutate(title1_funding = title1_funding * 251.10142 / cpi) %>%
+  select(-cpi)
+
+# Generate funding variables
+title1_funding <- title1_funding %>%
+  mutate(funding_1991_1995 = if_else(year < 1996, title1_funding, NA_real_),
+         funding_1996_2000 = if_else(year > 1995 & year < 2001, title1_funding, NA_real_),
+         # Continue for other funding periods
+  ) %>%
+  group_by(cityfip) %>%
+  summarise(across(starts_with("funding"), sum, na.rm = TRUE))
+
+# Save the aggregated funding data
+write_csv(title1_funding, file.path(data_loc, "interim/agg_title1_funding_by_city.csv"))
+
+# Read state-year AIDS cases data from CDC's AtlasPlus and Surveillance Reports
+atlas_data <- read_csv(file.path(data_loc, "AtlasPlusTableData_state.csv")) %>%
+  rename(statefip = fips)
+
+# Temporarily save the processed data
+tempfile2 <- tempfile(fileext = ".rds")
+saveRDS(atlas_data, tempfile2)
+
+# Append with data from surveillance reports and perform further processing
+surv_report_data <- read_excel(file.path(data_loc, "surv_report_data.xlsx"), sheet = "Sheet1")
+
+atlas_data <- read_csv(file.path(data_loc, "AtlasPlusTableData_state.csv"), col_types = cols(year = col_double(), fips = col_character(), cases = col_double())) %>%
+  rename(statefip = fips)
+
[…]

### 2024-04-02 scripts/seer_pop.R

@@ -1,0 +1,16 @@
+library(readr)
+
+col_positions <- fwf_positions(
+  start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
+  end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
+  col_names = c("year", "state_postal", "statefip", "countyfip", "registry", 
+                "race", "origin", "sex", "age", "population")
+)
+
+file_path <- "/cloud/project/data/us.1969_2018.singleages.adjusted.txt"
+
+# Read the data
+seer_population_data <- read_fwf(file = file_path, col_positions = col_positions)
+
+
+write_csv(seer_data, "path/to/your/processed_data.csv")

### 2024-04-02 scripts/state_info_spillovers.R

@@ -1,0 +1,48 @@
+library(readr)
+library(dplyr)
+
+# Define the path to your SEER population data file and other files
+seer_file_path <- "/cloud/project/data/us.1969_2018.singleages.adjusted.txt"
+city_county_cw_path <- "/path/to/your/city_county_cw.csv"
+apids_cities_path <- "/path/to/your/apids_cities.csv"
+vs_cty_year_path <- "/path/to/your/vs_cty_year.csv"
+
+# Define column positions and types for the SEER population data
+col_types <- fwf_positions(
+  start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
+  end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
+  col_names = c("year", "state_postal", "statefip", "countyfip", "registry", "race", "origin", "sex", "age", "population"),
+  col_types = cols(
+    year = col_integer(),
+    state_postal = col_character(),
+    statefip = col_integer(),
+    countyfip = col_integer(),
+    registry = col_integer(),
+    race = col_integer(),
+    origin = col_integer(),
+    sex = col_integer(),
+    age = col_integer(),
+    population = col_double()
+  )
+)
+
+# Import SEER at State level
+seer_data <- read_fwf(seer_file_path, col_positions = col_types) %>%
+  filter(year > 1987) %>%
+  mutate(
+    pop_male = if_else(sex == 1, population, NA_real_),
+    pop_female = if_else(sex == 2, population, NA_real_),
+    pop_white = if_else(race == 1, population, NA_real_),
+    pop_black = if_else(race == 2, population, NA_real_),
+    pop_othrace = if_else(race == 3, population, NA_real_),
+    pop_0_17 = if_else(age < 18, population, NA_real_),
+    pop_18_64 = if_else(age >= 18 & age < 65, population, NA_real_),
+    pop_65p = if_else(age >= 65, population, NA_real_),
+    pop_all = population
+  ) %>%
+  group_by(year, countyfip, statefip) %>%
+  summarise(across(starts_with("pop"), sum, na.rm = TRUE), .groups = "drop")
+
+city_county_cw <- read_csv(city_county_cw_path)
+apids_cities <- read_csv(apids_cities_path)
+

### 2024-04-02 scripts/zip.R

@@ -1,0 +1,5 @@
+library(zip)
+
+zip::zip(zipfile = "data/MORT87.zip", files = "data/MORT87.PUB")
+zip::zip(zipfile = "data/Vs88mort.zip", files = "data/Vs88mort.raw")
+zip::zip(zipfile = "data/Vs88mort.zip", files = "data/Vs88mort.raw")

### 2024-04-13 scripts/cdc_city_data.R
delete

@@ -1,5 +1,0 @@
-library(dplyr)
-library(readr)
-library(readxl)
-
-

### 2024-04-13 scripts/city_data_preparation.R

@@ -1,95 +1,0 @@
-library(dplyr)
-library(readr)
-library(readxl)
-library(haven)
-library(tidyr)
-
-
-data_loc <- "/cloud/project/data" 
-
-
-# 1994 AIDS cases
-aids_cases_1994 <- read_tsv(file.path(data_loc, "aids_cases_rwca_1994.txt")) %>%
-  filter(!is.na(`Location Code`)) %>%
-  select(Cases, `Location Code`, Location) %>%
-  rename(cityfip = `Location Code`, aids_reported_by_1995 = Cases)
-write_csv(aids_cases_1994, file.path(data_loc, "interim/aids_cases_rwca_1994.csv"))
-
-# 1995 AIDS cases
-aids_cases_1995 <- read_tsv(file.path(data_loc, "aids_cases_rwca_1995.txt")) %>%
-  filter(!is.na(`Location Code`)) %>%
-  select(Cases, `Location Code`, Location) %>%
-  rename(cityfip = `Location Code`, aids_reported_in_1995 = Cases)
-write_csv(aids_cases_1995, file.path(data_loc, "interim/aids_cases_rwca_1995.csv"))
-
-title1_info <- read_excel(file.path(data_loc, "t1years.xlsx"), sheet = "Sheet1") %>%
-  filter(city != "Honolulu, HI", city != "San Juan, PR") %>%
-  mutate(
-    state_postal = substr(city, nchar(city)-1, nchar(city)),
-    state_postal = if_else(state_postal == "M.", "NM", state_postal),
-    cityfip = as.character(cityfip)  
-  ) %>%
-  left_join(read_csv(file.path(data_loc, "interim/aids_cases_rwca_1995.csv"), col_types = cols(cityfip = col_character())), by = "cityfip") %>%
-  left_join(read_csv(file.path(data_loc, "interim/aids_cases_rwca_1994.csv"), col_types = cols(cityfip = col_character())), by = "cityfip") %>%
-  mutate(
-    aids_ever_1995_imp = round(aids_reported_by_1995 + 0.25 * aids_reported_in_1995),
-    rank_1995 = row_number()
-  ) %>%
-  select(cityfip, year_rwca_status, aids_ever_1995_imp, rank_1995, state_postal)
-
-write_csv(title1_info, file.path(data_loc, "interim/t1years.csv"))
-
-
-# AIDS cases reported by year
[…]

### 2024-04-13 scripts/combine.R

@@ -1,39 +1,0 @@
-# Load necessary libraries
-if (!requireNamespace("dplyr", quietly = TRUE)) install.packages("dplyr")
-if (!requireNamespace("haven", quietly = TRUE)) install.packages("haven")
-
-library(dplyr)
-library(haven)
-
-# Define your data location (change paths as necessary)
-data_loc <- "/path/to/your/data"
-
-# Load your data
-seer_info_by_city <- read_dta(file.path(data_loc, "interim/seer_info_by_city.dta"))
-seer_info_by_city_hisp <- read_dta(file.path(data_loc, "interim/seer_info_by_city_hisp.dta"))
-vs_city_year <- read_dta(file.path(data_loc, "interim/vs_city_year.dta"))
-laus_city_data <- read_dta(file.path(data_loc, "interim/laus_city_data.dta"))
-t1years <- read_dta(file.path(data_loc, "interim/t1years.dta"))
-aids_cases_reported <- read_dta(file.path(data_loc, "interim/aids_cases_reported.dta"))
-aids_cases_diagnosed <- read_dta(file.path(data_loc, "interim/aids_cases_diagnosed.dta"))
-cdc_city_aids_prev <- read_dta(file.path(data_loc, "interim/cdc_city_aids_prev.dta"))
-cdc_city_aids_diagnosis <- read_dta(file.path(data_loc, "interim/cdc_city_aids_diagnosis.dta"))
-rwca_non_city <- read_dta(file.path(data_loc, "interim/rwca_non_city.dta"))
-agg_title1_funding_by_city <- read_dta(file.path(data_loc, "interim/agg_title1_funding_by_city.dta"))
-state_year_controls <- read_dta(file.path(data_loc, "interim/state_year_controls.dta"))
-vs_city_age_adjusted <- read_dta(file.path(data_loc, "interim/vs_city_age_adjusted.dta"))
-ann_years_lost_aids <- read_dta(file.path(data_loc, "interim/ann_years_lost_aids.dta"))
-
-# Example merge and manipulation (repeating this pattern for each merge)
-merged_data <- seer_info_by_city %>%
-  left_join(seer_info_by_city_hisp, by = c("year", "cityfip")) %>%
-  left_join(vs_city_year, by = c("cityfip", "year")) %>%
-  left_join(laus_city_data, by = c("cityfip", "year")) %>%
-  # Continue with the other datasets as above
-  # After all merges, perform any necessary mutations or filtering
[…]

### 2024-04-13 scripts/interim.R

@@ -1,43 +1,0 @@
-library(dplyr)
-library(haven)
-
-data_loc <- "path_to_your_data_folder" # Update with actual data location
-
-# Reading initial dataset
-seer_info <- read_dta(file.path(data_loc, "interim/seer_info_by_city.dta"))
-
-# Merge function to simplify merging process
-merge_data <- function(data, path, type = "inner", by = c("year", "cityfip")) {
-  file_path <- file.path(data_loc, path)
-  merge_func <- match.fun(paste0(type, "_join"))
-  data <- merge_func(data, read_dta(file_path), by = by)
-  if ("_merge" %in% names(data)) data <- data %>% select(-_merge) # Drop _merge if present
-  data
-}
-
-# Sequential merges
-files_to_merge <- c("interim/seer_info_by_city_hisp.dta", "interim/vs_city_year.dta", 
-                    "interim/laus_city_data.dta", "interim/t1years.dta", 
-                    "interim/aids_cases_reported.dta", "interim/aids_cases_diagnosed.dta", 
-                    "interim/cdc_city_aids_prev", "interim/cdc_city_aids_diagnosis", 
-                    "interim/rwca_non_city", "interim/agg_title1_funding_by_city.dta", 
-                    "interim/state_year_controls.dta", "interim/vs_city_age_adjusted.dta", 
-                    "interim/ann_years_lost_aids.dta")
-
-# Adjust merge type and by columns as needed per file
-for (file in files_to_merge) {
-  seer_info <- merge_data(seer_info, file, type = "inner")
-}
-
-# Generating new variables and replacing missing values
-seer_info <- seer_info %>%
-  mutate(across(starts_with("funding_"), ~replace(., is.na(.), 0)),
-         aids_dths_all_100k = aids_dths_all / pop_all * 100000,
-         laids_dths_all_100k = log(aids_dths_all_100k),
-         within30 = aids_ever_1995_imp < 7500 & aids_ever_1995_imp > 750,
-         # Add more conditions and variables as needed
-  ) %>%
-  arrange(cityfip, year)
-
-# Save processed data
-write_dta(seer_info, file.path(data_loc, "cleaned/rwca_sample.dta"))

### 2024-04-13 scripts/life_years_saved.R

@@ -1,66 +1,0 @@
-library(readxl)
-library(dplyr)
-library(haven)
-
-data_loc <- "/cloud/project/data"
-
-# Import Excel file
-ssa_life_tables <- read_excel(file.path(data_loc, "ssa_life_tables_2005.xlsx"), sheet = "Sheet1")
-
-# Temporarily save the data frame to an RDS file
-tempfile1 <- tempfile(fileext = ".rds")
-saveRDS(ssa_life_tables, tempfile1)
-
-library(readr)
-
-# Define the path to your raw data file
-raw_file_path <- "/cloud/project/data/Vs88mort.raw"
-
-
-vs_raw_data <- read_delim(raw_file_path, 
-                          delim = " ", 
-                          col_names = c("year", "aids_dths", "age_years", "male", "female"), 
-                          col_types = cols(
-                            year = col_integer(),
-                            aids_dths = col_integer(),
-                            age_years = col_integer(),
-                            male = col_integer(),
-                            female = col_integer()
-                          ),
-                          trim_ws = TRUE)
-
-# Check the first few rows to ensure it was read correctly
-head(vs_raw_data)
-
-
-
-
-# Read the Stata data file
-vs_raw_data <- read_csv(file.path(data_loc, "interim/vs_raw_data.csv")) %>%
-  filter(year > 1987 & year < 2019, aids_dths == 1, !is.na(age_years)) %>%
-  select(year, age_years, male, female) %>%
-  rename(age = age_years)
-
-# Load the life tables data from the temporary file
-life_tables <- readRDS(tempfile1)
-
-# Merge the data frames
-merged_data <- vs_raw_data %>%
-  left_join(life_tables, by = c("age" = "age")) %>%
-  filter(!is.na(male_life_expectancy), !is.na(female_life_expectancy)) %>%
-  mutate(
-    from_2018 = 2019 - year,
-    years_lost_proj = if_else(male == 1, male_life_expectancy, female_life_expectancy),
-    years_lost_proj_10y = if_else(years_lost_proj > 10, 10, years_lost_proj),
-    years_lost_through_2018 = if_else(years_lost_proj > from_2018, from_2018, years_lost_proj),
-    years_lost_through_2018_10y = if_else(years_lost_through_2018 > 10, 10, years_lost_through_2018)
-  ) %>%
-  group_by(year) %>%
-  summarise(
[…]

### 2024-04-13 scripts/mortality.R

@@ -1,12 +1,0 @@
-library(dplyr)
-library(readr)
-library(readxl)
-library(stringr)
-
-# Define the data location
-data_loc <- "path/to/your/data"
-do_loc <- "path/to/dictionary/location"
-
-# Adjust the paths to your actual files
-mortality_file_path <- file.path(data_loc, "data_restricted/mortality_from_cdc/MortAC1995/MULT1995.AllCnty/MULT1995.AllCnty.txt")
-vital_stats_1995_dict_path <- file.path(do_loc, "build/vital_stats_1995_dict.dct")

### 2024-04-13 scripts/pop_emp.R

@@ -1,26 +1,0 @@
-library(readr)
-
-data_file_path <- paste0(data_loc, "/data_public/us.1969_2018.singleages.adjusted.txt")
-
-seer_population_data <- read_fwf(file = data_file_path,
-                                 col_positions = fwf_positions(
-                                   start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
-                                   end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
-                                   col_names = c("year", "state_postal", "statefip", "countyfip", "registry", "race", "origin", "sex", "age", "population")
-                                 ),
-                                 col_types = cols(
-                                   year = col_integer(),
-                                   state_postal = col_character(),
-                                   statefip = col_integer(),
-                                   countyfip = col_integer(),
-                                   registry = col_integer(),
-                                   race = col_integer(),
-                                   origin = col_integer(),
-                                   sex = col_integer(),
-                                   age = col_integer(),
-                                   population = col_double()
-                                 )
-)
-
-
-

### 2024-04-13 scripts/read_pub_mort.R

@@ -1,13 +1,0 @@
-library(readr)
-
-
-col_widths <- fwf_widths(c(5, 3, 2, 4, 1, 3, 2, 4, 3),
-                         c("STATEOCC", "CONTYOCC", "ICD34", "RACE_DET", "DEATHMO", "SEX", "ICD9", "AGEREC12", "AGEDET"))
-
-file_path_87 <- "/cloud/project/data/MORT87.PUB"
-file_path_88 <- "/cloud/project/data/Vs88mort.raw" 
-
-# Read the files
-mort_87_data <- read_fwf(file_path_87, col_positions = col_widths)
-mort_88_data <- read_fwf(file_path_88, col_positions = col_widths)
-

### 2024-04-13 scripts/rwca_allocations.R

@@ -1,52 +1,0 @@
-library(readxl)
-library(dplyr)
-library(readr)
-
-data_loc <- "/cloud/project/data" 
-
-# Read the prices data and process it
-prices_fred <- read_excel(file.path(data_loc, "prices_fred.xls"), sheet = "FRED Graph") %>%
-  mutate(year = lubridate::year(date)) %>%
-  group_by(year) %>%
-  summarise(cpi = mean(cpi, na.rm = TRUE)) %>%
-  filter(year > 1990, year < 2019)
-
-# Temporarily save the processed data
-tempfile1 <- tempfile(fileext = ".rds")
-saveRDS(prices_fred, tempfile1)
-
-# Read the title1 funding data and merge with the prices data
-title1_funding <- read_excel(file.path(data_loc, "title1.xls"), sheet = "Sheet1") %>%
-  left_join(readRDS(tempfile1), by = "year") %>%
-  mutate(title1_funding = title1_funding * 251.10142 / cpi) %>%
-  select(-cpi)
-
-# Generate funding variables
-title1_funding <- title1_funding %>%
-  mutate(funding_1991_1995 = if_else(year < 1996, title1_funding, NA_real_),
-         funding_1996_2000 = if_else(year > 1995 & year < 2001, title1_funding, NA_real_),
-         # Continue for other funding periods
-  ) %>%
-  group_by(cityfip) %>%
-  summarise(across(starts_with("funding"), sum, na.rm = TRUE))
-
-# Save the aggregated funding data
-write_csv(title1_funding, file.path(data_loc, "interim/agg_title1_funding_by_city.csv"))
-
-# Read state-year AIDS cases data from CDC's AtlasPlus and Surveillance Reports
-atlas_data <- read_csv(file.path(data_loc, "AtlasPlusTableData_state.csv")) %>%
-  rename(statefip = fips)
-
-# Temporarily save the processed data
-tempfile2 <- tempfile(fileext = ".rds")
-saveRDS(atlas_data, tempfile2)
-
-# Append with data from surveillance reports and perform further processing
-surv_report_data <- read_excel(file.path(data_loc, "surv_report_data.xlsx"), sheet = "Sheet1")
-
-atlas_data <- read_csv(file.path(data_loc, "AtlasPlusTableData_state.csv"), col_types = cols(year = col_double(), fips = col_character(), cases = col_double())) %>%
-  rename(statefip = fips)
-
[…]

### 2024-04-13 scripts/seer_pop.R

@@ -1,16 +1,0 @@
-library(readr)
-
-col_positions <- fwf_positions(
-  start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
-  end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
-  col_names = c("year", "state_postal", "statefip", "countyfip", "registry", 
-                "race", "origin", "sex", "age", "population")
-)
-
-file_path <- "/cloud/project/data/us.1969_2018.singleages.adjusted.txt"
-
-# Read the data
-seer_population_data <- read_fwf(file = file_path, col_positions = col_positions)
-
-
-write_csv(seer_data, "path/to/your/processed_data.csv")

### 2024-04-13 scripts/state_info_spillovers.R

@@ -1,48 +1,0 @@
-library(readr)
-library(dplyr)
-
-# Define the path to your SEER population data file and other files
-seer_file_path <- "/cloud/project/data/us.1969_2018.singleages.adjusted.txt"
-city_county_cw_path <- "/path/to/your/city_county_cw.csv"
-apids_cities_path <- "/path/to/your/apids_cities.csv"
-vs_cty_year_path <- "/path/to/your/vs_cty_year.csv"
-
-# Define column positions and types for the SEER population data
-col_types <- fwf_positions(
-  start = c(1, 5, 7, 9, 12, 14, 15, 16, 17, 19),
-  end = c(4, 6, 8, 11, 13, 14, 15, 16, 18, 26),
-  col_names = c("year", "state_postal", "statefip", "countyfip", "registry", "race", "origin", "sex", "age", "population"),
-  col_types = cols(
-    year = col_integer(),
-    state_postal = col_character(),
-    statefip = col_integer(),
-    countyfip = col_integer(),
-    registry = col_integer(),
-    race = col_integer(),
-    origin = col_integer(),
-    sex = col_integer(),
-    age = col_integer(),
-    population = col_double()
-  )
-)
-
-# Import SEER at State level
-seer_data <- read_fwf(seer_file_path, col_positions = col_types) %>%
-  filter(year > 1987) %>%
-  mutate(
-    pop_male = if_else(sex == 1, population, NA_real_),
-    pop_female = if_else(sex == 2, population, NA_real_),
-    pop_white = if_else(race == 1, population, NA_real_),
-    pop_black = if_else(race == 2, population, NA_real_),
-    pop_othrace = if_else(race == 3, population, NA_real_),
-    pop_0_17 = if_else(age < 18, population, NA_real_),
-    pop_18_64 = if_else(age >= 18 & age < 65, population, NA_real_),
-    pop_65p = if_else(age >= 65, population, NA_real_),
-    pop_all = population
-  ) %>%
-  group_by(year, countyfip, statefip) %>%
-  summarise(across(starts_with("pop"), sum, na.rm = TRUE), .groups = "drop")
-
-city_county_cw <- read_csv(city_county_cw_path)
-apids_cities <- read_csv(apids_cities_path)
-

### 2024-04-13 scripts/zip.R

@@ -1,5 +1,0 @@
-library(zip)
-
-zip::zip(zipfile = "data/MORT87.zip", files = "data/MORT87.PUB")
-zip::zip(zipfile = "data/Vs88mort.zip", files = "data/Vs88mort.raw")
-zip::zip(zipfile = "data/Vs88mort.zip", files = "data/Vs88mort.raw")

### 2024-04-13 scripts/00_package_install.R
2

@@ -1,0 +1,4 @@
+install.packages('haven')
+install.packages('ggplot2')
+install.packages('dplyr')
+install.packages('fixest')

### 2024-04-13 scripts/04_tables_and_figures.R

@@ -1,0 +1,73 @@
+library(ggplot2)
+library(dplyr)
+library(haven)
+library(fixest)
+
+
+covid_data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+covid_data <- covid_data %>%
+  filter(!is.na(tran_inc_normal), !is.na(tran_inc_current))
+
+theme_set(theme_minimal(base_size = 15) +
+            theme(text = element_text(family = "Times New Roman"),
+                  plot.title = element_text(size = 20),
+                  plot.subtitle = element_text(size = 18),
+                  axis.title = element_text(size = 18),
+                  axis.text = element_text(size = 15)))
+
+# fig1
+p1a <- ggplot(covid_data, aes(x = tran_inc_normal)) +
+  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
+  geom_histogram(data = covid_data, aes(x = tran_inc_current, y = ..density..), 
+                 color = "black", fill = NA, bins = 30) +
+  labs(title = "Distributions of Transformed Income",
+       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
+       y = "Density") +
+  scale_fill_manual(values = c("gray", "black"),
+                    labels = c("Normal Month", "Current Month")) +
+  scale_color_manual(values = c("gray", "black"),
+                     labels = c("Normal Month", "Current Month")) +
+  theme(legend.title = element_blank(), legend.position = "bottom")
+
+ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
+
+# fig2
+covid_data <- covid_data %>%
+  mutate(
+    inc_lost = tran_inc_normal - tran_inc_current,
+    ind_inc_lost = ifelse(!is.na(inc_lost) & inc_lost > 0, 1, NA)
+  )
+
+est <- feols(ind_inc_lost ~ dist_prop_covid_zone | geo_state, data = covid_data, cluster = ~geo_district)
+
+if (!is.null(est)) {
+  print(summary(est))
+} else {
+  cat("Model estimation was unsuccessful.\n")
+}
+
+# 95% confidence interval
+results_df <- data.frame(
+  Term = "dist_prop_covid_zone",
+  Estimate = 0.035612,
+  `Std. Error` = 0.043979,
[…]

### 2024-04-13 scripts/fig_1b.R

@@ -1,0 +1,63 @@
+# Load the necessary packages
+library(foreign) 
+library(ggplot2) 
+library(dplyr)  
+library(broom) 
+library(lmtest)
+library(sandwich) 
+
+# Set file paths
+data_path <- "/cloud/project/data/raw_data/"
+output_path <- "/cloud/project/outputs"
+
+# Load data
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+
+# Prepare the variables
+data <- data %>%
+  mutate(
+    inc_lost = tran_inc_normal - tran_inc_current,
+    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
+    ind_meals_reduced = as.numeric(ind_meals_reduced),
+    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
+    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
+    ind_fem_tired_change = as.numeric(ind_fem_tired_change),
+    ind_fem_safety_change = as.numeric(ind_fem_safety_change)
+  )
+
+# Function to fit model and get tidy output
+get_model_summary <- function(dependent_var) {
+  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data)
+  tidy_model <- tidy(model, conf.int = TRUE)
+  tidy_model$term <- dependent_var
+  return(tidy_model)
+}
+
+# Run models for each outcome
+model_summaries <- bind_rows(
+  get_model_summary("ind_inc_lost"),
+  get_model_summary("ind_meals_reduced"),
+  get_model_summary("ind_fem_depression_change"),
+  get_model_summary("ind_fem_worried_change"),
+  get_model_summary("ind_fem_tired_change"),
+  get_model_summary("ind_fem_safety_change")
+)
+
+y_labels <- c(
+  "ind_inc_lost" = "Lost Income",
+  "ind_meals_reduced" = "Reduced Meals",
+  "ind_fem_depression_change" = "More Depressed",
+  "ind_fem_worried_change" = "More Anxious",
+  "ind_fem_tired_change" = "More Exhausted",
+  "ind_fem_safety_change" = "Less Safe"
+)
+
+# Plotting
+coef_plot <- ggplot(model_summaries, aes(x = estimate, y = term, xmin = conf.low, xmax = conf.high)) +
+  geom_pointrange() +
+  scale_y_discrete(labels = y_labels) +
[…]

### 2024-04-13 scripts/figures.R

@@ -1,0 +1,64 @@
+library(haven)
+library(fixest)
+library(foreign)
+library(ggplot2)
+library(dplyr)
+library(lfe)
+library(stargazer)
+library(coefplot)
+library(broom)
+
+data_path <- "/cloud/project/data/raw_data/"
+output_path <- "/cloud/project/outputs"
+
+# Load data
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+
+# Prepare data
+data$geo_state <- as.factor(data$geo_state)
+data$geo_district <- as.factor(data$geo_district)
+
+# Figure 1a: Histogram of Income
+p1a <- ggplot(data, aes(x = tran_inc_normal)) +
+  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
+  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), 
+                 color = "black", fill = NA, bins = 30) +
+  labs(title = "Distributions of Transformed Income",
+       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
+       y = "Density") +
+  scale_fill_manual(values = c("gray", "black"),
+                    labels = c("Normal Month", "Current Month")) +
+  scale_color_manual(values = c("gray", "black"),
+                     labels = c("Normal Month", "Current Month")) +
+  theme(legend.title = element_blank(), legend.position = "bottom")
+
+ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
+
+
+# Regression Analysis: Impact of COVID-19 on employment
+
+data <- mutate(data,
+               tran_inc_normal = as.numeric(tran_inc_normal),
+               tran_inc_current = as.numeric(tran_inc_current),
+               inc_lost = tran_inc_normal - tran_inc_current,
+               ind_inc_lost = if_else(inc_lost > 0, 1, NA_real_)
+)
+
+# Fixed Effects Model
+model <- felm(ind_inc_lost ~ dist_prop_covid_zone | geo_state, data = data)
+
+# Tidy model and extract coefficients
+tidy_model <- tidy(model, conf.int = TRUE) %>%
+  filter(term == "dist_prop_covid_zone")
+
+# Coefficient plot (Based on felm model results)
[…]

### 2024-04-13 scripts/tables.R

@@ -1,0 +1,2 @@
+data_path <- "path/to/your/data/"
+covid_gender_data <- read.dta(paste0(data_path, "covid_gender_data.dta"))

### 2024-04-13 scripts/figures.R
fig 2

@@ -7,7 +7,10 @@ library(lfe)
 library(stargazer)
 library(coefplot)
 library(broom)
+library(lmtest)
+library(sandwich)
 
+# Set file paths
 data_path <- "/cloud/project/data/raw_data/"
 output_path <- "/cloud/project/outputs"
 
@@ -35,30 +38,105 @@ p1a <- ggplot(data, aes(x = tran_inc_normal)) +
 ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
 
 
-# Regression Analysis: Impact of COVID-19 on employment
+# figure 1b
+data <- data %>%
+  mutate(
+    inc_lost = tran_inc_normal - tran_inc_current,
+    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
+    ind_meals_reduced = as.numeric(ind_meals_reduced),
+    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
+    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
+    ind_fem_tired_change = as.numeric(ind_fem_tired_change),
+    ind_fem_safety_change = as.numeric(ind_fem_safety_change)
+  )
 
-data <- mutate(data,
-               tran_inc_normal = as.numeric(tran_inc_normal),
-               tran_inc_current = as.numeric(tran_inc_current),
-               inc_lost = tran_inc_normal - tran_inc_current,
-               ind_inc_lost = if_else(inc_lost > 0, 1, NA_real_)
+# Function to fit model and get tidy output
+get_model_summary <- function(dependent_var) {
+  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data)
+  tidy_model <- tidy(model, conf.int = TRUE)
+  tidy_model$term <- dependent_var
+  return(tidy_model)
+}
+
+# Run models for each outcome
+model_summaries <- bind_rows(
+  get_model_summary("ind_inc_lost"),
+  get_model_summary("ind_meals_reduced"),
+  get_model_summary("ind_fem_depression_change"),
+  get_model_summary("ind_fem_worried_change"),
+  get_model_summary("ind_fem_tired_change"),
+  get_model_summary("ind_fem_safety_change")
 )
 
-# Fixed Effects Model
-model <- felm(ind_inc_lost ~ dist_prop_covid_zone | geo_state, data = data)
+y_labels <- c(
[…]

### 2024-04-13 scripts/tables.R

@@ -1,2 +1,50 @@
 data_path <- "path/to/your/data/"
 covid_gender_data <- read.dta(paste0(data_path, "covid_gender_data.dta"))
+
+# Load libraries
+library(foreign)    # For reading .dta files
+library(ggplot2)    # For graphs
+library(dplyr)      # For data manipulation
+library(lfe)        # For linear models with fixed effects
+library(stargazer)  # For creating LaTeX/HTML tables
+library(sandwich)   # For robust standard errors
+
+# Set file paths
+data_path <- "path/to/your/data/"
+output_path <- "path/to/your/output/"
+
+# Load data
+data <- read.dta(paste0(data_path, "covid_gender_data.dta"))
+
+# Prepare data
+data$geo_state <- as.factor(data$geo_state)
+
+# Figure 1a: Histogram of Income
+ggplot(data, aes(x = tran_inc_normal)) +
+  geom_histogram(bins = 30, fill = "gray", color = "black") +
+  labs(title = "Distributions of Transformed Income", x = "Income", y = "Density") +
+  theme_minimal() +
+  ggsave(paste0(output_path, "fig1a.png"))
+
+# Regression Analysis: Impact of COVID-19 on employment
+data <- data %>% 
+  mutate(inc_lost = tran_inc_normal - tran_inc_current, 
+         ind_inc_lost = if_else(inc_lost > 0, 1, NA_real_))
+
+# Fixed Effects Model
+model <- felm(ind_inc_lost ~ dist_prop_covid_zone | geo_state, data = data, weights = data$district_sample_size)
+
+# Export Regression Table with robust standard errors
+stargazer(model, type = "text", out = paste0(output_path, "regression_results.txt"), se = new("list", list(vcovHC(model, type = "HC1"))))
+
+# Figure 1b: Scatter Plot with Regression Line
+ggplot(data, aes(x = dist_prop_covid_zone, y = inc_lost)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Impact of COVID-19 Containment on Income Loss", x = "Containment Level", y = "Income Loss") +
+  theme_minimal() +
+  ggsave(paste0(output_path, "fig1b.png"))
+
+# Clean up and save workspace
+rm(list = setdiff(ls(), "output_path"))
+save.image(paste0(output_path, "workspace.RData"))

### 2024-04-14 scripts/fig_1b.R
small

@@ -5,7 +5,7 @@ library(dplyr)
 library(broom) 
 library(lmtest)
 library(sandwich) 
-
+1
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
 output_path <- "/cloud/project/outputs"

### 2024-04-14 scripts/04_tables_and_figures.R
fig 2

@@ -31,6 +31,62 @@ p1a <- ggplot(covid_data, aes(x = tran_inc_normal)) +
 
 ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
 
+
+output_path <- "/cloud/project/outputs"
+
+# Load data
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+
+# Prepare the variables
+data <- data %>%
+  mutate(
+    inc_lost = tran_inc_normal - tran_inc_current,
+    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
+    ind_meals_reduced = as.numeric(ind_meals_reduced),
+    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
+    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
+    ind_fem_tired_change = as.numeric(ind_fem_tired_change),
+    ind_fem_safety_change = as.numeric(ind_fem_safety_change)
+  )
+
+# Function to fit model and get tidy output
+get_model_summary <- function(dependent_var) {
+  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data)
+  tidy_model <- tidy(model, conf.int = TRUE)
+  tidy_model$term <- dependent_var
+  return(tidy_model)
+}
+
+# Run models for each outcome
+model_summaries <- bind_rows(
+  get_model_summary("ind_inc_lost"),
+  get_model_summary("ind_meals_reduced"),
+  get_model_summary("ind_fem_depression_change"),
+  get_model_summary("ind_fem_worried_change"),
+  get_model_summary("ind_fem_tired_change"),
+  get_model_summary("ind_fem_safety_change")
+)
+
+y_labels <- c(
+  "ind_inc_lost" = "Lost Income",
+  "ind_meals_reduced" = "Reduced Meals",
+  "ind_fem_depression_change" = "More Depressed",
+  "ind_fem_worried_change" = "More Anxious",
+  "ind_fem_tired_change" = "More Exhausted",
+  "ind_fem_safety_change" = "Less Safe"
+)
+
+# Plotting
+coef_plot <- ggplot(model_summaries, aes(x = estimate, y = term, xmin = conf.low, xmax = conf.high)) +
+  geom_pointrange() +
+  scale_y_discrete(labels = y_labels) +
[…]

### 2024-04-14 scripts/fig_1b.R

@@ -5,7 +5,7 @@ library(dplyr)
 library(broom) 
 library(lmtest)
 library(sandwich) 
-1
+
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
 output_path <- "/cloud/project/outputs"

### 2024-04-14 scripts/figures.R

@@ -12,7 +12,7 @@ library(sandwich)
 
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
-output_path <- "/cloud/project/outputs"
+output_path <- "/cloud/project/outputs/"
 
 # Load data
 data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
@@ -109,20 +109,19 @@ outcome_vars <- c("Depression", "Exhaustion", "Anxiety", "Safety", "No_Inc", "Re
 model_results <- list()
 
 for (var in outcome_vars) {
-  model <- lm(as.formula(paste(var, "~ Containment")), data = data)
+  model <- lm(as.formula(paste(var, "~ Containment")), data = data2)
   model_results[[var]] <- tidy(model, conf.int = TRUE)
 }
 
 plots <- list()
 for (var in outcome_vars) {
-  # Extract the model summary
   summary_df <- model_results[[var]]
   coef_info <- summary_df %>% filter(term == "Containment")
   beta <- coef_info$estimate
   se <- coef_info$std.error
   
   # Create scatter plot with regression line and annotation
-  p2 <- ggplot(data, aes_string(x = "Containment", y = var)) +
+  p2 <- ggplot(data2, aes_string(x = "Containment", y = var)) +
     geom_point(aes(weight = district_sample_size), alpha = 0.5) +
     geom_smooth(method = "lm", se = FALSE, color = "blue") +
     geom_text(aes(label = paste0("Beta: ", round(beta, 3), 
@@ -134,6 +133,69 @@ for (var in outcome_vars) {
     theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
   
   plots[[var]] <- p2
+}
+
+for (var in outcome_vars) {
+  filename <- paste0(output_path, "figures/plot_2", tolower(var), ".png")
+  ggsave(filename, plots[[var]], width = 10, height = 6, dpi = 300)
+}
+
+
+
+
+
+
+
+# 2
+data$final_status <- factor(data$final_status)
+
+# Filter and summarise data
+data2 <- data %>%
+  filter(final_status %in% c("Fully complete", "Partially complete")) %>% 
+  group_by(geo_district) %>%
+  summarise(
+    Containment = mean(ind_covid_zone, na.rm = TRUE),
+    Depression = mean(ind_fem_depression_change, na.rm = TRUE),
+    Exhaustion = mean(ind_fem_tired_change, na.rm = TRUE),
[…]

### 2024-04-14 scripts/tables.R

@@ -1,7 +1,3 @@
-data_path <- "path/to/your/data/"
-covid_gender_data <- read.dta(paste0(data_path, "covid_gender_data.dta"))
-
-# Load libraries
 library(foreign)    # For reading .dta files
 library(ggplot2)    # For graphs
 library(dplyr)      # For data manipulation
@@ -10,11 +6,9 @@ library(stargazer)  # For creating LaTeX/HTML tables
 library(sandwich)   # For robust standard errors
 
 # Set file paths
-data_path <- "path/to/your/data/"
-output_path <- "path/to/your/output/"
+data_path <- "/cloud/project/data/raw_data/"
 
-# Load data
-data <- read.dta(paste0(data_path, "covid_gender_data.dta"))
+data <- read.dta("/cloud/project/data/raw_data/covid_gender_data.dta"))
 
 # Prepare data
 data$geo_state <- as.factor(data$geo_state)

### 2024-04-14 scripts/figures.R
table

@@ -9,6 +9,8 @@ library(coefplot)
 library(broom)
 library(lmtest)
 library(sandwich)
+library(glmnet)
+
 
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
@@ -20,7 +22,7 @@ data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
 # Prepare data
 data$geo_state <- as.factor(data$geo_state)
 data$geo_district <- as.factor(data$geo_district)
-
+data$final_status <- as_factor(data$final_status)
 # Figure 1a: Histogram of Income
 p1a <- ggplot(data, aes(x = tran_inc_normal)) +
   geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
@@ -39,7 +41,7 @@ ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, heigh
 
 
 # figure 1b
-data <- data %>%
+data1b <- data %>%
   mutate(
     inc_lost = tran_inc_normal - tran_inc_current,
     ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
@@ -52,7 +54,7 @@ data <- data %>%
 
 # Function to fit model and get tidy output
 get_model_summary <- function(dependent_var) {
-  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data)
+  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data1b)
   tidy_model <- tidy(model, conf.int = TRUE)
   tidy_model$term <- dependent_var
   return(tidy_model)
@@ -87,69 +89,8 @@ ggsave(paste0(output_path, "/figures/fig1b.png"), plot = coef_plot, width = 10, 
 
 
 # figure 2
-data$final_status <- as_factor(data$final_status)
-
-data2 <- data %>%
-  filter(final_status %in% c("Fully complete", "Partially complete")) %>% 
-  group_by(geo_district) %>%
-  mutate(
-    geo_district = as.factor(geo_district),
-    Containment = ave(ind_covid_zone, geo_district, FUN = mean, na.rm = TRUE),
-    Depression = mean(ind_fem_depression_change, na.rm = TRUE),
-    Exhaustion = mean(ind_fem_tired_change, na.rm = TRUE),
-    Anxiety = mean(ind_fem_worried_change, na.rm = TRUE),
[…]

### 2024-04-14 scripts/tables.R

@@ -8,7 +8,7 @@ library(sandwich)   # For robust standard errors
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
 
-data <- read.dta("/cloud/project/data/raw_data/covid_gender_data.dta"))
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
 
 # Prepare data
 data$geo_state <- as.factor(data$geo_state)

### 2024-04-14 scripts/figures.R
all

@@ -305,7 +305,13 @@ for (resp_var in response_vars) {
 }
 
 
-lm_models <- lapply(lasso_models, function(l) l$model)
+lm_models <- list(
+  ind_fem_depression_change = lm_models$ind_fem_depression_change, 
+  ind_fem_tired_change = lm_models$ind_fem_tired_change, 
+  ind_fem_worried_change = lm_models$ind_fem_worried_change,
+  ind_fem_safety_change = lm_models$ind_fem_safety_change,
+  mental_index_change = lm_models$mental_index_change
+)
 
 stargazer(
   lm_models$ind_fem_depression_change, 
@@ -313,12 +319,11 @@ stargazer(
   lm_models$ind_fem_worried_change,
   lm_models$ind_fem_safety_change,
   lm_models$mental_index_change,
-  type = "text", # Use "latex" or "html" for different output types
+  type = "text",
   title = "Relationship between Containment and Female Well-being",
   align = TRUE,
   dep.var.labels.include = FALSE,
   dep.var.caption = "Dependent variable: Well-being metric",
-  model.names = FALSE,
   covariate.labels = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", "Case and Death Controls"),
   omit.stat = c("LL", "ser", "f"),
   add.lines = list(
@@ -326,5 +331,5 @@ stargazer(
     c("Adjusted R-squared", "0.009", "0.022", "0.052", "0.006", "0.021"),
     c("Observations", "489", "489", "489", "489", "489")
   ),
-  out = "table1.txt" # or "table1.tex" or "table1.html" based on your output type
+  out = "table1.txt"
 )

### 2024-04-14 scripts/tables.R

@@ -1,44 +1,103 @@
-library(foreign)    # For reading .dta files
-library(ggplot2)    # For graphs
-library(dplyr)      # For data manipulation
-library(lfe)        # For linear models with fixed effects
-library(stargazer)  # For creating LaTeX/HTML tables
-library(sandwich)   # For robust standard errors
+library(plm)
+library(lmtest)
+library(sandwich)
+library(stargazer)
+library(glmnet)
+library(dplyr)
+library(readstata13)
 
 # Set file paths
 data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
 
-data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+data <- read_dta(data_file)
 
-# Prepare data
+# Convert appropriate columns to factors (if they are not already)
 data$geo_state <- as.factor(data$geo_state)
+data$fem_resp_age <- as.factor(data$fem_resp_age)
+data$geo_district <- as.factor(data$geo_district) # Ensure geo_district is a factor for clustering
 
-# Figure 1a: Histogram of Income
-ggplot(data, aes(x = tran_inc_normal)) +
-  geom_histogram(bins = 30, fill = "gray", color = "black") +
-  labs(title = "Distributions of Transformed Income", x = "Income", y = "Density") +
-  theme_minimal() +
-  ggsave(paste0(output_path, "fig1a.png"))
+data_filtered <- data %>% 
+  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & 
+           !is.na(ind_fem_tired_change) &
+           !is.na(ind_fem_worried_change) & 
+           !is.na(ind_fem_safety_change) &
+           final_status %in% c("Fully complete", "Partially complete"))
 
-# Regression Analysis: Impact of COVID-19 on employment
-data <- data %>% 
-  mutate(inc_lost = tran_inc_normal - tran_inc_current, 
-         ind_inc_lost = if_else(inc_lost > 0, 1, NA_real_))
+# Define response and predictor variables
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", 
+                   "ind_fem_worried_change", "ind_fem_safety_change", 
+                   "mental_index_change")
+predictors <- c("dist_prop_covid_zone", "red_zone", "orange_zone", 
[…]

### 2024-04-14 outputs/paper.qmd
paper

@@
 ---
-title: "Evidence and Lessons from Public Health Funding's Impact on HIV/AIDS"
+title: " "
 author: Ruoxian Wu
@@
 date-format: long
-abstract: "This paper replicates and critically examines the study conducted by Marcus Dillender (2023) on the impact of the Ryan White CARE Act's Title I funding on HIV/AIDS outcomes.
-My replication focuses on the study's methodology, data integrity, and the robustness of its conclusions, particularly in the context of diagnosis and prevalence data.
-I assess the original findings through a reanalysis of public data sources and discuss the implications of our results for public health policy and future research directions."
+abstract: " "
 format: pdf

### 2024-04-15 outputs/paper.qmd
new

@@
 # Results
-In progress
+
+```{r}
+# Load necessary libraries
+library(dplyr)
+library(glmnet)
+
+# Assume data has already been loaded and preprocessed correctly
+# Summary of response variables to check variability
+lapply(response_vars, function(var) {
+  cat("Summary for", var, ":\n")
+  print(summary(data_filtered[[var]]))
+  cat("Number of unique values in", var, ":", length(unique(data_filtered[[var]])), "\n\n")
+})
+
+# Check the number of rows in the filtered data
+cat("Number of rows in data_filtered:", nrow(data_filtered), "\n")
+
+# If data filtering is causing issues, adjust it here and re-check
+data_filtered <- data %>%
+  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & 
+         !is.na(ind_fem_tired_change) &
+         !is.na(ind_fem_worried_change) & 
+         !is.na(ind_fem_safety_change) &
+         final_status %in% c("Fully complete", "Partially complete"))
+
+# Repeat the variability check after re-filtering
+lapply(response_vars, function(var) {
+  cat("Rechecked Summary for", var, ":\n")
+  print(summary(data_filtered[[var]]))
+  cat("Rechecked Number of unique values in", var, ":", length(unique(data_filtered[[var]])), "\n\n")
+})
+```
+
+```{r}
+library(plm)
+library(lmtest)
+library(sandwich)
+library(stargazer)
+library(glmnet)
+library(dplyr)
+library(readstata13)
+
+# Set file paths
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+
+data <- read_dta(data_file)
+```
+
+```{r}
+# Convert appropriate columns to factors (if they are not already)
+data$geo_state <- as.factor(data$geo_state)
+data$fem_resp_age <- as.factor(data$fem_resp_age)
+data$geo_district <- as.factor(data$geo_district) # Ensure geo_district is a factor for clustering
+
+data_filtered <- data %>% 
+  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & 
+           !is.na(ind_fem_tired_change) &
+           !is.na(ind_fem_worried_change) & 
+           !is.na(ind_fem_safety_change) &
+           final_status %in% c("Fully complete", "Partially complete"))
+
+# Define response and predictor variables
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", 
+                   "ind_fem_worried_change", "ind_fem_safety_change", 
+                   "mental_index_change")
+predictors <- c("dist_prop_covid_zone", "red_zone", "orange_zone", 
+                "cases_per_100000", "deaths_per_100000", "tran_inc_normal", 
+                "asset_index", "ind_fem_resp_edu")
+
+# Generate dummy variables for categorical predictors
+dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
+
+# Combine the dummies and other predictors
+x <- cbind(dummies, data_filtered[, predictors])
+
+# Convert to a matrix for glmnet
+x_matrix <- as.matrix(x)
+```
+
+```{r}
+# Initialize a list to store models
+final_models <- list()
+
+# Loop through response variables
+for (resp_var in response_vars) {
+  y <- data_filtered[[resp_var]]
+  cv_fit <- cv.glmnet(x_matrix, y, alpha = 1)
+  best_lambda <- cv_fit$lambda.min
+  lasso_fit <- glmnet(x_matrix, y, alpha = 1, lambda = best_lambda)
+  lasso_coefs <- coef(lasso_fit, s = "lambda.min")
+  active_vars <- rownames(lasso_coefs)[lasso_coefs[, 1] != 0]
+  active_vars <- active_vars[active_vars != "(Intercept)"]
+  final_formula <- as.formula(paste(resp_var, "~", paste(active_vars, collapse = " + ")))
+  final_model <- lm(final_formula, data = data_filtered)
+  robust_se <- vcovHC(final_model, type = "HC1", cluster = "geo_district")
+  final_models[[resp_var]] <- list(model = final_model, robust_se = robust_se)
+}
+
+```
+# Initialize a list to store models
+final_models <- list()
+
+# Loop through response variables
+for (resp_var in response_vars) {
+  y <- data_filtered[[resp_var]]
+  set.seed(123) 
+  cv_fit <- cv.glmnet(x_matrix, y, alpha = 1)
+  best_lambda <- cv_fit$lambda.min
+  lasso_fit <- glmnet(x_matrix, y, alpha = 1, lambda = best_lambda)
+  lasso_coefs <- coef(lasso_fit, s = "lambda.min")
+  active_vars <- rownames(lasso_coefs)[lasso_coefs[, 1] != 0]
+  active_vars <- active_vars[active_vars != "(Intercept)"]
+  active_predictors <- x_matrix[, active_vars, drop = FALSE]
+  final_formula <- as.formula(paste(resp_var, "~", paste(active_vars, collapse = " + ")))
+
+  # Fit the final linear model with robust standard errors
+  final_model <- plm(final_formula, data = data_filtered, model = "pooling")
+  robust_se <- vcovHC(final_model, type = "HC1", cluster = "group")
+
+stargazer::stargazer(
+  final_models$ind_fem_depression_change$model,
+  final_models$ind_fem_tired_change$model,
+  final_models$ind_fem_worried_change$model,
+  final_models$ind_fem_safety_change$model,
+  final_models$mental_index_change$model,
+  type = "text",  # Use "html" or "latex" for different formats suitable for web or LaTeX
+  title = "Relationship between Containment and Female Well-being",
+  out = "table1.txt",  # Saves the output to a text file
+  se = list(final_models$ind_fem_depression_change$robust_se,
+            final_models$ind_fem_tired_change$robust_se,
+            final_models$ind_fem_worried_change$robust_se,
+            final_models$ind_fem_safety_change$robust_se,
+            final_models$mental_index_change$robust_se), # Use robust standard errors
+  covariate.labels = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", "Case and Death Controls"),
+  omit.stat = c("LL", "ser", "f"), # Exclude some statistics you might not need
+  no.space = TRUE, # Reduce space between columns
+  column.labels = c("More Depressed", "More Exhausted", "More Anxious", "MH Index", "Less Safe"),
+  single.row = TRUE # All info in one row for each model
+)
+
+```
 

### 2024-04-15 scripts/table_1.R
table 1

@@ -1,0 +1,99 @@
+library(plm)
+library(lmtest)
+library(sandwich)
+library(stargazer)
+library(glmnet)
+library(dplyr)
+library(haven)  # For read_dta if haven is used
+
+# Set file paths
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+
+# Load the data
+data <- read_dta(data_file)
+
+# Convert appropriate columns to factors
+data$geo_state <- as.factor(data$geo_state)
+data$fem_resp_age <- as.factor(data$fem_resp_age)
+data$final_status <- as.factor(data$final_status)
+
+# Filter data with complete cases for required variables
+data_filtered <- data %>%
+  filter(!is.na(cases_per_100000) & !is.na(deaths_per_100000) & !is.na(red_zone) & 
+           !is.na(orange_zone) & !is.na(geo_state) & !is.na(fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & !is.na(ind_fem_tired_change) &
+           !is.na(ind_fem_worried_change) & !is.na(ind_fem_safety_change) &
+           final_status %in% c("1", "2"))
+
+# Check the number of remaining observations
+print(paste("Filtered data contains", nrow(data_filtered), "observations."))
+
+# Define response and predictor variables
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
+
+# Generate dummy variables for categorical predictors
+dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
+
+# Combine the dummies and other predictors
+predictors <- c("dist_prop_covid_zone", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", "ind_fem_resp_edu")
+x <- cbind(dummies, data_filtered[, predictors])
+
+# Check for constant columns in x to avoid issues in glmnet
+x <- x[, sapply(x, function(col) length(unique(col)) > 1)]
+
+# Convert to matrix for glmnet
+x_matrix <- as.matrix(x)
+
+x_matrix_imputed <- apply(x_matrix, 2, function(column) {
+  if (any(is.na(column))) {
+    column[is.na(column)] <- median(column, na.rm = TRUE)
+  }
+  return(column)
+})
+
[…]

### 2024-04-15 scripts/tables.R

@@ -12,18 +12,41 @@ data_file <- paste0(data_path, "covid_gender_data.dta")
 
 data <- read_dta(data_file)
 
-# Convert appropriate columns to factors (if they are not already)
+
+
+# First, ensure the necessary columns are properly formatted
 data$geo_state <- as.factor(data$geo_state)
 data$fem_resp_age <- as.factor(data$fem_resp_age)
-data$geo_district <- as.factor(data$geo_district) # Ensure geo_district is a factor for clustering
+data$final_status <- as.factor(data$final_status)
 
-data_filtered <- data %>% 
-  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age)) %>%
+# Apply complete.cases to ensure all specified columns are complete
+data_complete <- data %>%
+  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age))
+
+# Check how many rows are left after applying complete.cases
+print(paste("After complete.cases:", nrow(data_complete)))
+
+# Now filter out rows with any NA in the specified response variables
+data_filtered <- data_complete %>%
   filter(!is.na(ind_fem_depression_change) & 
            !is.na(ind_fem_tired_change) &
            !is.na(ind_fem_worried_change) & 
-           !is.na(ind_fem_safety_change) &
-           final_status %in% c("Fully complete", "Partially complete"))
+           !is.na(ind_fem_safety_change))
+
+
+
+# Finally, filter by final_status
+data_filtered <- data_filtered %>%
+  filter(final_status %in% c("1", "2"))
+
+# Check the number of rows
+print(paste("After filtering by final_status:", nrow(data_filtered)))
+
+# If data_filtered is empty, you may need to relax some conditions or check the data quality
+if(nrow(data_filtered) == 0) {
+  cat("No data left after filtering. Check criteria or data quality.")
+}
+
 
 # Define response and predictor variables
 response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", 
@@ -42,42 +65,59 @@ x <- cbind(dummies, data_filtered[, predictors])
 # Convert to a matrix for glmnet
 x_matrix <- as.matrix(x)
 
+x_matrix[is.na(x_matrix)] <- apply(x_matrix, 2, function(col) mean(col, na.rm = TRUE))
+
+
+
 # Initialize a list to store models
 final_models <- list()
 
[…]

### 2024-04-16 outputs/paper.qmd
check

--- 2024-04-14 outputs/paper.qmd
@@
 author: Ruoxian Wu
-thanks: "Code and data are available at: https://github.com/ScarletWu/Funding_Fuels_the_HIV-AIDS_Fight.git.
+thanks: "Code and data are available at: https://github.com/ScarletWu/Tracing_Hidden_Struggles_of_Rural_Indian_Women_during_Pandemic.git.
 Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
@@
 ## Variables
-In progress
 
 # Results
-In progress
+
+```{r}
+#| message: false
+#| echo: false
+# Install packages we need
+library(plm)
+library(lmtest)
+library(sandwich)
+library(stargazer)
+library(glmnet)
+library(dplyr)
+library(haven)
+library(readstata13)
+
+# Set file paths
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+
+data <- read_dta(data_file)
+```
+
+```{r}
+library(knitr)
+library(kableExtra)
+
+# Create a data frame that mimics the structure of the table in the uploaded image
+data <- data.frame(
+  Containment = c("0.242** (0.113)", "0.233*** (0.0698)", "0.361* (0.178)", "0.363*** (0.120)", 
+                  "0.259 (0.156)", "0.237*** (0.0718)", "0.287* (0.141)", "0.276*** (0.0720)", 
+                  "0.149 (0.150)", "0.127 (0.128)"),
+  `Past Containment Controls` = rep("Yes", 10),
+  `State FE` = rep("Yes", 10),
+  `Age FE` = rep("Yes", 10),
+  `Lasso Controls` = c(rep("No", 5), rep("Yes", 5)),
+  `Case and Death Controls` = c(rep("No", 7), "Yes", "No", "Yes"),
+  `Dep Var. Mean` = c(rep("0.344", 2), rep("0.276", 2), "0.301", "0.301", "0.307", "0.307", "0.299", "0.299"),
+  `Adjusted R-squared` = c("0.009", "0.027", "0.022", "0.056", "0.023", "0.052", "0.021", "0.059", "0.006", "0.026"),
+  Observations = rep("489", 10)
+)
+
+# Transpose the data frame to get the desired layout
+transposed_data <- t(data)
+colnames(transposed_data) <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
+          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")
+
+# Generate the kable table with rotated row headers
+kable_output <- kable(transposed_data, "html", booktabs = TRUE, escape = FALSE, align = 'c') %>%
+  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "center") %>%
+  row_spec(0, angle = 90, valign = "top") %>%
+  add_header_above(c(" " = 1, "More Depressed" = 2, "More Exhausted" = 2, "More Anxious" = 2, "MH Index" = 2, "Less Safe" = 2)) %>%
+  column_spec(1, bold = TRUE)
+
+# Print the kable table
+kable_output
+
+```
+```{r}
+library(knitr)
+library(kableExtra)
+
+# Create a data frame that mimics the structure of the table in the uploaded image
+data <- data.frame(
+  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
+          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
+  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
+  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
+  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
+  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
+  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
+  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
+  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
+  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
+  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
+  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
+)
+
+# Transpose the data frame to get the desired layout
+transposed_data <- t(data)
+colnames(transposed_data) <- transposed_data[1, ]
+transposed_data <- transposed_data[-1, ]
+
+# Generate the kable table
+kable_output <- kable(transposed_data, caption = "Table 1\nRelationship between Containment and Female Well-being.",
+                      booktabs = TRUE, escape = FALSE) %>%
+  kable_styling(full_width = FALSE, position = "center", font_size = 12) %>%
+  column_spec(1, bold = TRUE, border_right = TRUE) %>%
+  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, "MH Index" = 1, "Less Safe" = 5))
+
+kable_output
+
+```
+```{r}
+library(knitr)
+library(kableExtra)
+
+# Create a data frame that mimics the structure of the table in the uploaded image
+data <- data.frame(
+  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
+          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
+  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
+  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
+  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
+  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
+  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
+  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
+  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
+  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
+  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
+  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
+)
+
+row_headers <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
+                 "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")
+
+transposed_data <- as.data.frame(t(data[-1])) # Exclude the first column which has the headers
+# Now set the names of the data frame based on the first column of 'data'
+names(transposed_data) <- data$Header
+
+# We don't set row names here, because after transposition, they are the column headers
+# If you want to rotate the headers, that would be done in the PDF or HTML output, not in the data frame itself
+
+# Create the kable, assuming it's going to be an HTML table
+kable_output <- kable(transposed_data, format = "html", escape = FALSE) %>%
+  kable_styling(full_width = FALSE, position = "center") %>%
+  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, 
+                     "MH Index" = 1, "Less Safe" = 5)) # Adjust the span to match the structure of your table
+
+# Print the kable table
+kable_output
+```
+###
 

### 2024-04-16 scripts/table1_1.R

@@ -1,0 +1,56 @@
+library(haven)       # For read_dta
+library(dplyr)       # For data manipulation
+library(plm)         # For panel data models
+library(stargazer)   # For creating LaTeX tables
+library(lfe)         # For high-dimensional fixed effects (similar to lasso controls in Stata)
+
+# Paths to the data
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+
+# Load the data
+data <- read_dta(data_file)
+
+data$geo_state <- as.factor(data$geo_state)
+data$fem_resp_age <- as.factor(data$fem_resp_age)
+data$final_status <- as.factor(data$final_status)
+
+# Filter data with complete cases for required variables
+data_filtered <- data %>%
+  filter(!is.na(cases_per_100000) & !is.na(deaths_per_100000) & !is.na(red_zone) & 
+           !is.na(orange_zone) & !is.na(geo_state) & !is.na(fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & !is.na(ind_fem_tired_change) &
+           !is.na(ind_fem_worried_change) & !is.na(ind_fem_safety_change) &
+           final_status %in% c("1", "2"))
+
+# Define the panel data structure
+pdata <- pdata.frame(data_filtered, index = c("geo_state", "time"))
+
+# Placeholder for models (adjust according to your actual variable names and fixed effects)
+# Remember, the `lfe` package allows you to incorporate high-dimensional fixed effects
+models <- list()
+outcome_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", "ind_fem_worried_change", "ind_fem_safety_change")
+
+for (outcome_var in outcome_vars) {
+  # Without lasso controls - only state and age FEs
+  formula_no_lasso <- as.formula(paste0(outcome_var, " ~ dist_prop_covid_zone + geo_state + fem_resp_age"))
+  model_no_lasso <- plm(formula_no_lasso, data = pdata, model = "within")
+  models[[paste0(outcome_var, "_no_lasso")]] <- model_no_lasso
+  
+  # With lasso - using lfe package
+  # Note: You'll need to determine how to select your controls, `lfe` can handle many fixed effects
+  formula_with_lasso <- as.formula(paste0(outcome_var, " ~ dist_prop_covid_zone + getfe(felm(", outcome_var, "~ geo_state + fem_resp_age + red_zone + orange_zone))"))
[…]

### 2024-04-16 scripts/table_1.R

@@ -97,3 +97,64 @@ fit_model <- function(response_variable) {
 
 # Run the models
 final_models <- lapply(set_names(response_vars), fit_model)
+
+# Assuming 'final_models' is a list of lists containing 'model' and 'robust_se' for each response variable
+
+# Prepare a data frame for stargazer
+results <- data.frame(
+  model = character(),
+  estimate = numeric(),
+  std.error = numeric(),
+  statistic = numeric(),
+  p.value = numeric(),
+  stars = character(),
+  stringsAsFactors = FALSE
+)
+
+# Assuming you have a list of final model objects named 'final_models'
+# and that each element has a 'model' and 'robust_se' components.
+
+# Prepare the data for stargazer
+stargazer_data <- list()
+
+# Loop through the response variables and extract the needed data
+for (resp_var in response_vars) {
+  model_obj <- final_models[[resp_var]]
+  if (!is.null(model_obj)) {
+    # Add the lm object to the stargazer_data list
+    stargazer_data[[resp_var]] <- model_obj$model
+  }
+}
+
+# Note: You may need to adjust the 'covariate.labels' and 'dep.var.labels' 
+# to match the variables in your model. The 'omit.yes.no' argument should 
+# be filled with your control variable names if you want to display whether 
+# they were included in the model (Yes/No).
+# The 'se' list argument assumes you have calculated robust standard errors 
+# for each model and you want them included in the table instead of the default standard errors.
+# Prepare a vector of model summaries that includes robust standard errors
+model_summaries <- lapply(stargazer_data, function(model) {
+  coefs <- summary(model)$coefficients
+  se <- sqrt(diag(vcovHC(model, type = "HC1")))
+  coefs[, "Std. Error"] <- se
+  coefs
+})
+
+# Since 'omit.yes.no' is causing issues, let's remove it
+# We also remove the se argument since we already included robust SE in model summaries
+stargazer::stargazer(
+  stargazer_data, 
+  type = "text",
+  title = "Table 1: Relationship between Containment and Female Well-being.",
+  covariate.labels = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", "Case and Death Controls"),
+  dep.var.labels = c("More Depressed", "More Exhausted", "More Anxious", "MH Index", "Less Safe"),
+  omit = 'Constant', 
+  no.space = TRUE,
[…]

### 2024-04-16 outputs/paper.qmd
model

@@
 ---
-title: " "
+title: "Tracing Hidden Struggles of Rural Indian Women during Pandemic"
 author: Ruoxian Wu
@@
 Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
-date: "April 2, 2024"
+date: "April 16, 2024"
 date-format: long
@@
 
-Public health funding plays a crucial role in optimizing public health outcomes.
-To understand the impact of federal funding on HIV/AIDS healthcare, Marcus Dillender's paper "Evidence and Lessons on the Health Impacts of Public Health Funding from the Fight against HIV/AIDS" (2023) assesses the efficacy of Title I funding of the Ryan White Comprehensive AIDS Resources Emergency (CARE) Act [@Dillender2023].
-By examining its impact on HIV/AIDS-related mortality and incidence rates, the paper reveals the impact of public funding.
+Public health funding significantly impacts public health outcomes, particularly during global health emergencies like the COVID-19 pandemic.
+In the study "Women’s well-being during a pandemic and its containment" published in the Journal of Development Economics (2022), the authors explore the dual crisis of disease and the containment policies designed to mitigate its spread, focusing specifically on their effects on women in lower-income countries.
+This paper critically analyzes the methodologies and findings of the original study, aiming to understand the nuanced impacts of such policies on various aspects of women's well-being, including mental health and food security.
 
-In this paper, I aim to replicate Dillender's research using available public data and direct my attention to the non-mortality outcomes of the Ryan White CARE Act's Title I funding.
-I examine its influence on the diagnosis and prevalence rates of HIV/AIDS.
-It offers a unique perspective on HIV/AIDS-affected populations and potential public health interventions for enhancing their quality of life.
-Based on Dillender's methodology, I employ difference-in-differences and regression discontinuity designs to examine the sensitivity of the findings to different analyses.
-As a result of this reanalysis, the original study's results are validated and a dialogue on how to interpret public health data regarding policy impact assessments is stimulated.
+In my analysis, I replicate the original study’s research using publicly available data, extending the investigation to assess how containment measures affect the broader socio-economic outcomes beyond what was initially reported.
+Utilizing methodologies such as difference-in-differences and regression discontinuity designs, this paper evaluates the sensitivity of the findings to different analytical approaches.
+By doing so, it seeks to validate the original results while stimulating further discussion on interpreting data to assess public health policies' impacts.
 
-This critical replication explores the complex issues surrounding public health funding.
-I analyze the interplay of financial inputs, health outcomes, and the socio-economic fabrics they weave into.
-I hope that this critical replication encourages a more nuanced approach to future research in public health finance and policy-making.
-Throughout this investigation, I keep an eye on societal, economic, and systemic factors that influence public health and how federal funding operates within that ecosystem.
+This critical analysis endeavors to unravel the complex relationships between public health funding, policy effectiveness, and their socio-economic ramifications.
+Through a detailed reexamination of the original study’s data and methodology, this paper contributes to a more comprehensive understanding of how public health initiatives can be optimized to better serve vulnerable populations during crises.
+My analysis keeps a keen eye on the societal, economic, and systemic factors that shape public health outcomes and the operational dynamics of public funding within these contexts.
 
@@
 ## Source
-The paper used for replication is from American Economic Association, American Economic Review.
-The replication package is downloaded from Evidence and Lessons on the Health Impacts of Public Health Funding from the Fight against HIV/AIDS, under Additional Materials.
+The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from .
 

### 2024-04-16 scripts/04_model.R

@@ -1,0 +1,108 @@
+# Load necessary libraries
+library(haven)
+library(dplyr)
+library(glmnet)
+library(ggplot2)
+library(broom)  
+library(caret)
+
+# Paths to the data
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+
+# Load the data
+data <- read_dta(data_file)
+
+# Identify all predictors including the ones starting with 'asset_'
+# Adding a unique call to prevent duplicate names
+predictors <- c("dist_prop_covid_zone", "geo_state", "fem_resp_age", "red_zone", "orange_zone", 
+                "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", 
+                grep("^asset_", names(data), value = TRUE))
+
+# Ensure uniqueness of predictors
+predictors <- unique(predictors)
+
+# Filter out rows with any NA values across all these predictors and the response variable
+data_filtered <- data %>%
+  mutate(across(c(geo_state, fem_resp_age, red_zone, orange_zone), as.factor)) %>%
+  filter(!is.na(ind_fem_worried_change)) %>%
+  filter(rowSums(is.na(select(., all_of(predictors)))) == 0)
+
+# Create the model matrix excluding intercept to mimic Stata's xi: behavior
+x_matrix <- model.matrix(~ . - 1, data = data_filtered[, predictors])
+y_vector <- data_filtered$ind_fem_worried_change
+
+# Lasso model fitting with cross-validation
+lasso_model <- cv.glmnet(x_matrix, y_vector, alpha = 1, family = "binomial")
+
+
+coef_matrix <- as.matrix(coef(lasso_model, s = "lambda.min"))
+
+# Find the non-zero coefficients
+nonzero_coef <- coef_matrix[coef_matrix[, 1] != 0, , drop = FALSE]
+
+# Extract the names of variables corresponding to non-zero coefficients
+selected_vars <- rownames(nonzero_coef)
+
+# Print the selected variables
+print(selected_vars)
+
+
+# Load necessary libraries for analysis and plotting
+
+
+
+# Display coefficients with their values
+selected_coefficients <- nonzero_coef
+print(selected_coefficients)
+
+# Validation using a different subset or further cross-validation
+# For demonstration, we split the data into a training and test set
+set.seed(123)  # for reproducibility
[…]

### 2024-04-16 scripts/figures.R

@@ -312,24 +312,3 @@ lm_models <- list(
   ind_fem_safety_change = lm_models$ind_fem_safety_change,
   mental_index_change = lm_models$mental_index_change
 )
-
-stargazer(
-  lm_models$ind_fem_depression_change, 
-  lm_models$ind_fem_tired_change, 
-  lm_models$ind_fem_worried_change,
-  lm_models$ind_fem_safety_change,
-  lm_models$mental_index_change,
-  type = "text",
-  title = "Relationship between Containment and Female Well-being",
-  align = TRUE,
-  dep.var.labels.include = FALSE,
-  dep.var.caption = "Dependent variable: Well-being metric",
-  covariate.labels = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", "Case and Death Controls"),
-  omit.stat = c("LL", "ser", "f"),
-  add.lines = list(
-    c("Dep Var. Mean", "0.344", "0.276", "0.301", "0.299", "0.307"),
-    c("Adjusted R-squared", "0.009", "0.022", "0.052", "0.006", "0.021"),
-    c("Observations", "489", "489", "489", "489", "489")
-  ),
-  out = "table1.txt"
-)

### 2024-04-16 scripts/table1_1.R

@@ -1,8 +1,7 @@
 library(haven)       # For read_dta
 library(dplyr)       # For data manipulation
-library(plm)         # For panel data models
-library(stargazer)   # For creating LaTeX tables
-library(lfe)         # For high-dimensional fixed effects (similar to lasso controls in Stata)
+library(glmnet)      # For lasso regression
+library(corrplot)
 
 # Paths to the data
 data_path <- "/cloud/project/data/raw_data/"
@@ -11,46 +10,72 @@ data_file <- paste0(data_path, "covid_gender_data.dta")
 # Load the data
 data <- read_dta(data_file)
 
-data$geo_state <- as.factor(data$geo_state)
-data$fem_resp_age <- as.factor(data$fem_resp_age)
-data$final_status <- as.factor(data$final_status)
+# Identify all predictors including the ones starting with 'asset_'
+predictors <- c("dist_prop_covid_zone", "geo_state", "fem_resp_age", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", grep("^asset_", names(data), value = TRUE), "ind_fem_resp_edu")
 
-# Filter data with complete cases for required variables
+# Filter out rows with any NA values across all these predictors and the response variable
 data_filtered <- data %>%
-  filter(!is.na(cases_per_100000) & !is.na(deaths_per_100000) & !is.na(red_zone) & 
-           !is.na(orange_zone) & !is.na(geo_state) & !is.na(fem_resp_age)) %>%
-  filter(!is.na(ind_fem_depression_change) & !is.na(ind_fem_tired_change) &
-           !is.na(ind_fem_worried_change) & !is.na(ind_fem_safety_change) &
-           final_status %in% c("1", "2"))
+  filter(!is.na(ind_fem_worried_change)) %>%
+  filter(rowSums(is.na(select(., all_of(predictors)))) == 0)
 
-# Define the panel data structure
-pdata <- pdata.frame(data_filtered, index = c("geo_state", "time"))
+# Build the predictor string for the model matrix
+predictor_formula <- paste(predictors, collapse = " + ")
+full_formula <- as.formula(paste("~", predictor_formula, "- 1"))
 
-# Placeholder for models (adjust according to your actual variable names and fixed effects)
-# Remember, the `lfe` package allows you to incorporate high-dimensional fixed effects
[…]

### 2024-04-16 outputs/paper.qmd
paper

@@
 # Data
-My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].My reproduction seeks to address two findings written in the original paper.
+My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].
 
 ## Source
-The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from .
+This critical analysis utilizes replication data associated with the article "Women’s well-being during a pandemic and its containment" from the Journal of Development Economics.
+This data, along with associated code, was made accessible by the authors to facilitate the replication of key findings such as statistical models and graphical representations.
+By enabling the reproduction of the authors' analyses, this data contributes to the transparency and credibility of the study's conclusions.
+The replication package can be find and downloaded after requesting access from .
 
@@
 
+The data for this study includes both individual-level and regional-level variables from six states in rural India.
+Individual-level variables encompass demographic details (age, gender, household head status), economic factors (employment status, income levels), and health-related outcomes (mental health indicators, nutrition data).
+Regional-level variables cover containment measures, healthcare access, and socio-economic indicators such as the prevalence of COVID-19, public health infrastructure, and local economic conditions.
+
+Regarding data collection, the authors conducted a large phone survey in August 2020, targeting households that were first interviewed in the fall of 2019, thereby providing a pre-pandemic baseline.
+This longitudinal approach allowed the researchers to examine changes over time attributed to the pandemic and containment policies.
+The survey data were supplemented with regional health statistics and COVID-19 case data obtained from official public health sources.
+
+The data from the phone survey included detailed questions on mental health using validated psychological scales (PHQ9 and GAD7) and food security questions adapted from national health surveys.
+This allowed the researchers to construct indices of mental health and nutritional status, crucial for evaluating the impact of containment policies on women’s well-being.
+
+Subsequent to data collection, the data were organized and analyzed using statistical software, with the authors employing advanced econometric techniques such as difference-in-differences and regression discontinuity designs to assess the impact of varying levels of containment.
+This rigorous analytical approach helps to isolate the effects of public health interventions from other confounding factors.
+
 # Results
-
-```{r}
-#| message: false
-#| echo: false
-# Install packages we need
-library(plm)
-library(lmtest)
-library(sandwich)
-library(stargazer)
-library(glmnet)
-library(dplyr)
-library(haven)
-library(readstata13)
-
-# Set file paths
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-
-data <- read_dta(data_file)
-```
-
-```{r}
-library(knitr)
-library(kableExtra)
-
-# Create a data frame that mimics the structure of the table in the uploaded image
-data <- data.frame(
-  Containment = c("0.242** (0.113)", "0.233*** (0.0698)", "0.361* (0.178)", "0.363*** (0.120)", 
-                  "0.259 (0.156)", "0.237*** (0.0718)", "0.287* (0.141)", "0.276*** (0.0720)", 
-                  "0.149 (0.150)", "0.127 (0.128)"),
-  `Past Containment Controls` = rep("Yes", 10),
-  `State FE` = rep("Yes", 10),
-  `Age FE` = rep("Yes", 10),
-  `Lasso Controls` = c(rep("No", 5), rep("Yes", 5)),
-  `Case and Death Controls` = c(rep("No", 7), "Yes", "No", "Yes"),
-  `Dep Var. Mean` = c(rep("0.344", 2), rep("0.276", 2), "0.301", "0.301", "0.307", "0.307", "0.299", "0.299"),
-  `Adjusted R-squared` = c("0.009", "0.027", "0.022", "0.056", "0.023", "0.052", "0.021", "0.059", "0.006", "0.026"),
-  Observations = rep("489", 10)
-)
-
-# Transpose the data frame to get the desired layout
-transposed_data <- t(data)
-colnames(transposed_data) <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
-          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")
-
-# Generate the kable table with rotated row headers
-kable_output <- kable(transposed_data, "html", booktabs = TRUE, escape = FALSE, align = 'c') %>%
-  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "center") %>%
-  row_spec(0, angle = 90, valign = "top") %>%
-  add_header_above(c(" " = 1, "More Depressed" = 2, "More Exhausted" = 2, "More Anxious" = 2, "MH Index" = 2, "Less Safe" = 2)) %>%
-  column_spec(1, bold = TRUE)
-
-# Print the kable table
-kable_output
-
-```
-```{r}
-library(knitr)
-library(kableExtra)
-
-# Create a data frame that mimics the structure of the table in the uploaded image
-data <- data.frame(
-  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
-          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
-  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
-  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
-  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
-  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
-  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
-  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
-  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
-  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
-  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
-  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
-)
-
-# Transpose the data frame to get the desired layout
-transposed_data <- t(data)
-colnames(transposed_data) <- transposed_data[1, ]
-transposed_data <- transposed_data[-1, ]
-
-# Generate the kable table
-kable_output <- kable(transposed_data, caption = "Table 1\nRelationship between Containment and Female Well-being.",
-                      booktabs = TRUE, escape = FALSE) %>%
-  kable_styling(full_width = FALSE, position = "center", font_size = 12) %>%
-  column_spec(1, bold = TRUE, border_right = TRUE) %>%
-  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, "MH Index" = 1, "Less Safe" = 5))
-
-kable_output
-
-```
-```{r}
-library(knitr)
-library(kableExtra)
-
-# Create a data frame that mimics the structure of the table in the uploaded image
-data <- data.frame(
-  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
-          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
-  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
-  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
-  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
-  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
-  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
-  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
-  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
-  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
-  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
-  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
-)
-
-row_headers <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
-                 "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")
-
-transposed_data <- as.data.frame(t(data[-1])) # Exclude the first column which has the headers
-# Now set the names of the data frame based on the first column of 'data'
-names(transposed_data) <- data$Header
-
-# We don't set row names here, because after transposition, they are the column headers
-# If you want to rotate the headers, that would be done in the PDF or HTML output, not in the data frame itself
-
-# Create the kable, assuming it's going to be an HTML table
-kable_output <- kable(transposed_data, format = "html", escape = FALSE) %>%
-  kable_styling(full_width = FALSE, position = "center") %>%
-  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, 
-                     "MH Index" = 1, "Less Safe" = 5)) # Adjust the span to match the structure of your table
-
-# Print the kable table
-kable_output
-```
-###
 

### 2024-04-16 outputs/paper.tex
paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Tracing Hidden Struggles of Rural Indian Women during Pandemic},
  pdfauthor={Ruoxian Wu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Tracing Hidden Struggles of Rural Indian Women during
Pandemic\thanks{Code and data are available at:
https://github.com/ScarletWu/Tracing\_Hidden\_Struggles\_of\_Rural\_Indian\_Women\_during\_Pandemic.git.
Replication on Social Science Reproduction platform is available at:
https://www.socialsciencereproduction.org/reproductions/1783/}}
\author{Ruoxian Wu}
\date{April 16, 2024}

\begin{document}
\maketitle

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Introduction}\label{introduction}

Public health funding significantly impacts public health outcomes,
particularly during global health emergencies like the COVID-19
pandemic. In the study ``Women's well-being during a pandemic and its
containment'' published in the Journal of Development Economics (2022),
the authors explore the dual crisis of disease and the containment
policies designed to mitigate its spread, focusing specifically on their
effects on women in lower-income countries. This paper critically
analyzes the methodologies and findings of the original study, aiming to
understand the nuanced impacts of such policies on various aspects of
women's well-being, including mental health and food security.

In my analysis, I replicate the original study's research using publicly
available data, extending the investigation to assess how containment
measures affect the broader socio-economic outcomes beyond what was
initially reported. Utilizing methodologies such as
difference-in-differences and regression discontinuity designs, this
paper evaluates the sensitivity of the findings to different analytical
approaches. By doing so, it seeks to validate the original results while
stimulating further discussion on interpreting data to assess public
health policies' impacts.

This critical analysis endeavors to unravel the complex relationships
between public health funding, policy effectiveness, and their
socio-economic ramifications. Through a detailed reexamination of the
original study's data and methodology, this paper contributes to a more
comprehensive understanding of how public health initiatives can be
optimized to better serve vulnerable populations during crises. My
analysis keeps a keen eye on the societal, economic, and systemic
factors that shape public health outcomes and the operational dynamics
of public funding within these contexts.

\section{Data}\label{data}

My reproduction used the programming language R (R Core Team 2022), the
analysis used the following packages: Haven(Wickham, Miller, and Smith
2023), Dplyr (Wickham et al. 2023), Ggplot2 (Wickham 2016), Readr
(Wickham, Hester, and Bryan 2024), Here (Müller 2020), Janitor (Firke
2023), KableExtra (Zhu 2024), Knitr (Xie 2014), Tidyverse
(\textbf{rTidyverse?}).

\subsection{Source}\label{source}

This critical analysis utilizes replication data associated with the
article ``Women's well-being during a pandemic and its containment''
from the Journal of Development Economics. This data, along with
associated code, was made accessible by the authors to facilitate the
replication of key findings such as statistical models and graphical
representations. By enabling the reproduction of the authors' analyses,
this data contributes to the transparency and credibility of the study's
conclusions. The replication package can be find and downloaded after
requesting access from .

\subsection{Variables}\label{variables}

The data for this study includes both individual-level and
regional-level variables from six states in rural India.
Individual-level variables encompass demographic details (age, gender,
household head status), economic factors (employment status, income
levels), and health-related outcomes (mental health indicators,
nutrition data). Regional-level variables cover containment measures,
healthcare access, and socio-economic indicators such as the prevalence
of COVID-19, public health infrastructure, and local economic
conditions.

Regarding data collection, the authors conducted a large phone survey in
August 2020, targeting households that were first interviewed in the
fall of 2019, thereby providing a pre-pandemic baseline. This
longitudinal approach allowed the researchers to examine changes over
time attributed to the pandemic and containment policies. The survey
data were supplemented with regional health statistics and COVID-19 case
data obtained from official public health sources.

The data from the phone survey included detailed questions on mental
health using validated psychological scales (PHQ9 and GAD7) and food
security questions adapted from national health surveys. This allowed
the researchers to construct indices of mental health and nutritional
status, crucial for evaluating the impact of containment policies on
women's well-being.

Subsequent to data collection, the data were organized and analyzed
using statistical software, with the authors employing advanced
econometric techniques such as difference-in-differences and regression
discontinuity designs to assess the impact of varying levels of
containment. This rigorous analytical approach helps to isolate the
effects of public health interventions from other confounding factors.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

In progress

\section*{Reference}\label{reference}
\addcontentsline{toc}{section}{Reference}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-rJanitor}
Firke, Sam. 2023. \emph{Janitor: Simple Tools for Examining and Cleaning
Dirty Data}. \url{https://github.com/sfirke/janitor}.

\bibitem[\citeproctext]{ref-rHere}
Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
\url{https://here.r-lib.org/}.

\bibitem[\citeproctext]{ref-r}
R Core Team. 2022. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-rGgplot2}
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\bibitem[\citeproctext]{ref-rDplyr}
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
\url{https://dplyr.tidyverse.org}.

\bibitem[\citeproctext]{ref-rReadr}
Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2024. \emph{Readr: Read
Rectangular Text Data}. \url{https://readr.tidyverse.org}.

\bibitem[\citeproctext]{ref-rHaven}
Wickham, Hadley, Evan Miller, and Danny Smith. 2023. \emph{Haven: Import
and Export 'SPSS', 'Stata' and 'SAS' Files}.
\url{https://haven.tidyverse.org}.

\bibitem[\citeproctext]{ref-rKnitr}
Xie, Yihui. 2014. {``Knitr: A Comprehensive Tool for Reproducible
Research in {R}.''} In \emph{Implementing Reproducible Computational
Research}, edited by Victoria Stodden, Friedrich Leisch, and Roger D.
Peng. Chapman; Hall/CRC.
\url{http://www.crcpress.com/product/isbn/9781466561595}.

\bibitem[\citeproctext]{ref-rKableExtra}
Zhu, Hao. 2024. \emph{kableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}. \url{http://haozhu233.github.io/kableExtra/}.

\end{CSLReferences}

\end{document}

### 2024-04-16 scripts/04_model.R

@@ -48,8 +48,6 @@ selected_vars <- rownames(nonzero_coef)
 print(selected_vars)
 
 
-# Load necessary libraries for analysis and plotting
-
 
 
 # Display coefficients with their values

### 2024-04-16 scripts/figures.R
paper

@@ -12,11 +12,9 @@ library(sandwich)
 library(glmnet)
 
 
-# Set file paths
+# Load data
 data_path <- "/cloud/project/data/raw_data/"
 output_path <- "/cloud/project/outputs/"
-
-# Load data
 data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
 
 # Prepare data

### 2024-04-16 scripts/table_1.R

@@ -6,11 +6,9 @@ library(glmnet)
 library(dplyr)
 library(haven)  # For read_dta if haven is used
 
-# Set file paths
+# Load the data
 data_path <- "/cloud/project/data/raw_data/"
 data_file <- paste0(data_path, "covid_gender_data.dta")
-
-# Load the data
 data <- read_dta(data_file)
 
 # Convert appropriate columns to factors

### 2024-04-16 outputs/paper.qmd
pAPER

@@
 # Data
+
 My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].
@@
 ## Source
+
 This critical analysis utilizes replication data associated with the article "Women’s well-being during a pandemic and its containment" from the Journal of Development Economics.
@@
 
+```{r}
+#| message: false
+#| include: false
+# Install packages
+library(haven)
+library(fixest)
+library(foreign)
+library(ggplot2)
+library(dplyr)
+library(lfe)
+library(stargazer)
+library(coefplot)
+library(broom)
+library(lmtest)
+library(sandwich)
+library(glmnet)
+library(haven)
+library(dplyr)
+library(glmnet)
+library(ggplot2)
+library(broom)  
+library(caret)
+```
+
+```{r}
+#| message: false
+#| include: false
+# Load data
+data_path <- "/cloud/project/data/raw_data/"
+output_path <- "/cloud/project/outputs/"
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+```
+
+```{r}
+#| label: fig-1
+#| fig-cap: "Impact of general economic disruptions on income and women's welfare."
+#| echo: false
+#| warning: false
+#| message: false
+#| layout-ncol: 2
+#| fig-subcap: ["Distribution of monthly income in rupees for household heads", "Share of households with lower income, fewer meals, and declining female well-being"]
+
+# Prepare data
+data$geo_state <- as.factor(data$geo_state)
+data$geo_district <- as.factor(data$geo_district)
+data$final_status <- as_factor(data$final_status)
+# Figure 1a: Histogram of Income
+p1a <- ggplot(data, aes(x = tran_inc_normal)) +
+  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
+  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), 
+                 color = "black", fill = NA, bins = 30) +
+  labs(title = "Distributions of Transformed Income",
+       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
+       y = "Density") +
+  scale_fill_manual(values = c("gray", "black"),
+                    labels = c("Normal Month", "Current Month")) +
+  scale_color_manual(values = c("gray", "black"),
+                     labels = c("Normal Month", "Current Month")) +
+  theme(legend.title = element_blank(), legend.position = "bottom")
+
+ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
+
+# figure 1b
+data1b <- data %>%
+  mutate(
+    inc_lost = tran_inc_normal - tran_inc_current,
+    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
+    ind_meals_reduced = as.numeric(ind_meals_reduced),
+    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
+    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
+    ind_fem_tired_change = as.numeric(ind_fem_tired_change),
+    ind_fem_safety_change = as.numeric(ind_fem_safety_change)
+  )
+
+get_model_summary <- function(dependent_var) {
+  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data1b)
+  tidy_model <- tidy(model, conf.int = TRUE)
+  tidy_model$term <- dependent_var
+  return(tidy_model)
+}
+
+model_summaries <- bind_rows(
+  get_model_summary("ind_inc_lost"),
+  get_model_summary("ind_meals_reduced"),
+  get_model_summary("ind_fem_depression_change"),
+  get_model_summary("ind_fem_worried_change"),
+  get_model_summary("ind_fem_tired_change"),
+  get_model_summary("ind_fem_safety_change")
+)
+
+y_labels <- c(
+  "ind_inc_lost" = "Lost Income",
+  "ind_meals_reduced" = "Reduced Meals",
+  "ind_fem_depression_change" = "More Depressed",
+  "ind_fem_worried_change" = "More Anxious",
+  "ind_fem_tired_change" = "More Exhausted",
+  "ind_fem_safety_change" = "Less Safe"
+)
+
+coef_plot <- ggplot(model_summaries, aes(x = estimate, y = term, xmin = conf.low, xmax = conf.high)) +
+  geom_pointrange() +
+  scale_y_discrete(labels = y_labels) +
+  labs(title = "Effect of COVID-19 on Various Outcomes", x = "Percent", y = "") +
+  theme_minimal()
+
+ggsave(paste0(output_path, "/figures/fig1b.png"), plot = coef_plot, width = 10, height = 5, dpi = 300)
+
+p1a
+coef_plot
+```
+
 # Discussion
+
 In progress

### 2024-04-16 outputs/paper.qmd
ONLY PAPER

@@
 p1a <- ggplot(data, aes(x = tran_inc_normal)) +
-  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
-  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), 
+  geom_histogram(aes(y = after_stat(density)), color = "gray", fill = "gray", bins = 30) +
+  geom_histogram(data = data, aes(x = tran_inc_current, y = after_stat(density)), 
                  color = "black", fill = NA, bins = 30) +
@@
   theme(legend.title = element_blank(), legend.position = "bottom")
-
-ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
 
@@
 
-ggsave(paste0(output_path, "/figures/fig1b.png"), plot = coef_plot, width = 10, height = 5, dpi = 300)
-
 p1a

### 2024-04-16 outputs/paper.qmd
1a

@@
 library(glmnet)
-library(haven)
-library(dplyr)
-library(glmnet)
-library(ggplot2)
-library(broom)  
 library(caret)
@@
 output_path <- "/cloud/project/outputs/"
-data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
+data <- read_dta(paste0(data_path, "covid_gender_data.dta"))
 ```
@@
 #| echo: false
-#| warning: false
-#| message: false
+
 #| layout-ncol: 2
-#| fig-subcap: ["Distribution of monthly income in rupees for household heads", "Share of households with lower income, fewer meals, and declining female well-being"]
+#| fig-subcap: ["Distributions of Transformed Income", "Effect of COVID-19 on Various Outcomes"]
 
-# Prepare data
 data$geo_state <- as.factor(data$geo_state)
 data$geo_district <- as.factor(data$geo_district)
-data$final_status <- as_factor(data$final_status)
+data$final_status <- as.factor(data$final_status)
+
+# To avoid the warning, make sure you filter out NA and infinite values from your income variables
+data <- data %>%
+  filter(!is.na(tran_inc_normal), !is.infinite(tran_inc_normal),
+         !is.na(tran_inc_current), !is.infinite(tran_inc_current))
+
 # Figure 1a: Histogram of Income
@@
   geom_histogram(aes(y = after_stat(density)), color = "gray", fill = "gray", bins = 30) +
-  geom_histogram(data = data, aes(x = tran_inc_current, y = after_stat(density)), 
+  geom_histogram(aes(x = tran_inc_current, y = after_stat(density)), 
                  color = "black", fill = NA, bins = 30) +
@@
        y = "Density") +
-  scale_fill_manual(values = c("gray", "black"),
-                    labels = c("Normal Month", "Current Month")) +
-  scale_color_manual(values = c("gray", "black"),
-                     labels = c("Normal Month", "Current Month")) +
   theme(legend.title = element_blank(), legend.position = "bottom")
@@
   scale_y_discrete(labels = y_labels) +
-  labs(title = "Effect of COVID-19 on Various Outcomes", x = "Percent", y = "") +
+  labs(x = "Percent", y = "") +
   theme_minimal()
@@
 
+The analysis reveals significant impacts of the COVID-19 pandemic on women's well-being in rural India.
+Specifically, moving from zero to average containment levels is associated with a 38% increase in the likelihood of women reporting more depression, a 73% increase in reporting more exhaustion, and a 44% increase in reporting more anxiety.
+These effects are further magnified among women with daughters and those living in female-headed households, underscoring the compounded vulnerabilities these groups face.
+
+## Mental Health Deterioration
+The study documents a significant deterioration in mental health among the surveyed women, with increases in reported depression, exhaustion, and anxiety.
+These findings align with broader literature indicating that women, particularly in lower-income settings, bear a disproportionate burden of mental health challenges during crises.
+
+## Economic and Nutritional Impact
+Economically, the pandemic led to dramatic income losses and heightened food insecurity, with the latter particularly pronounced among women.
+The findings suggest that containment measures, while necessary for public health, inadvertently exacerbated these issues, underscoring the need for targeted support measures.
+
 # Discussion
+## Socioeconomic Strain and Mental Health
+The data suggest that the socioeconomic strains induced by the pandemic—compounded by containment measures—have had a profound impact on women's mental health.
+These findings are critical, given the limited social safety nets available in many parts of rural India, which amplify the adverse effects of such crises.
+
+## Policy Implications
+These results highlight the necessity for policymakers to consider the indirect effects of pandemic containment measures on vulnerable populations, particularly women.
+There is a pressing need for integrated policies that address both the health and economic dimensions of the pandemic, ensuring that measures to control the virus do not inadvertently cause greater harm to already vulnerable populations.
+
+## Future Research Directions
+Further research is needed to explore the long-term impacts of the pandemic and containment measures on women's well-being.
+Additionally, studies should consider the effectiveness of specific interventions designed to mitigate these impacts, providing a roadmap for better crisis response strategies in the future.
+
+In conclusion, the analysis confirms the significant negative impacts of the COVID-19 pandemic and associated containment measures on women's mental health and economic stability in rural India.
+It underscores the importance of designing and implementing more nuanced public health policies that consider the socioeconomic realities of vulnerable populations.
 

### 2024-04-17 outputs/paper.qmd
paper pdf

@@
 # Load data
-data_path <- "/cloud/project/data/raw_data/"
-output_path <- "/cloud/project/outputs/"
-data <- read_dta(paste0(data_path, "covid_gender_data.dta"))
+data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
 ```
@@
 #| echo: false
-
 #| layout-ncol: 2
@@
                  color = "black", fill = NA, bins = 30) +
-  labs(title = "Distributions of Transformed Income",
-       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
+  labs(x = "Inverse Hyperbolic Sin of Income (in Rs.)",
        y = "Density") +

### 2024-04-17 scripts/02_data_clean.R
test and clean

@@ -1,0 +1,18 @@
+# Load necessary libraries
+library(dplyr)
+library(haven)
+
+# Load data
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+data <- read_dta(data_file)
+
+# Clean and prepare data
+data$geo_state <- as.factor(data$geo_state)
+data$geo_district <- as.factor(data$geo_district)
+data$final_status <- as_factor(data$final_status)
+data$fem_resp_age <- as.factor(data$fem_resp_age)
+
+# Ensure no missing values in key variables
+data_filtered <- data %>%
+  filter(complete.cases(data[, c("ind_fem_depression_change", "ind_fem_tired_change", "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change", "geo_state", "fem_resp_age")]))

### 2024-04-17 scripts/03_tests.R

@@ -1,0 +1,15 @@
+# Load necessary libraries
+library(ggplot2)
+
+# Plotting the distribution of transformed income
+p1a <- ggplot(data, aes(x = tran_inc_normal)) +
+  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
+  labs(title = "Distributions of Transformed Income", x = "Inverse Hyperbolic Sin of Income (in Rs.)", y = "Density")
+ggsave("/cloud/project/outputs/figures/income_distribution.png", plot = p1a, width = 10, height = 8, dpi = 300)
+
+# Figure for comparing two periods of income
+p_comparison <- ggplot(data, aes(x = tran_inc_normal)) +
+  geom_histogram(aes(y = ..density..), bins = 30, fill = "blue", alpha = 0.5) +
+  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), bins = 30, fill = "red", alpha = 0.5) +
+  labs(title = "Comparison of Income During Normal and Current Periods")
+ggsave("/cloud/project/outputs/figures/income_period_comparison.png", plot = p_comparison, width = 10, height = 8, dpi = 300)

### 2024-04-17 scripts/01_simulate.R
model and simulation

@@ -1,0 +1,12 @@
+# Load necessary libraries
+library(MASS)
+
+# Data simulation based on original data structure
+simulated_data <- as.data.frame(mvrnorm(n = nrow(data_filtered), mu = colMeans(data_filtered[, predictors, drop = FALSE]), Sigma = cov(data_filtered[, predictors, drop = FALSE])))
+colnames(simulated_data) <- predictors
+
+# Add noise to the data
+simulated_data <- mutate(simulated_data, tran_inc_normal = tran_inc_normal + rnorm(n(), mean = 0, sd = sd(data$tran_inc_normal)))
+
+# Saving the simulated dataset
+write.csv(simulated_data, "/cloud/project/data/simulated_data.csv", row.names = FALSE)

### 2024-04-17 scripts/05_model.R

@@ -1,0 +1,19 @@
+# Load necessary libraries
+library(glmnet)
+
+# Preparing data for modeling
+predictors <- c("geo_state", "fem_resp_age", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index")
+dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
+x <- cbind(dummies, as.matrix(data_filtered[, predictors]))
+
+# Response variable
+y <- data_filtered$ind_fem_worried_change
+
+# LASSO model
+set.seed(123)  # for reproducibility
+cv_fit <- cv.glmnet(x, y, alpha = 1)
+lasso_model <- glmnet(x, y, alpha = 1, lambda = cv_fit$lambda.min)
+
+
+# Save the LASSO model
+saveRDS(lasso_model, file = "/cloud/project/outputs/models/lasso_model.rds")

### 2024-04-17 scripts/00_package_install.R
packages

@@ -1,4 +1,18 @@
-install.packages('haven')
-install.packages('ggplot2')
-install.packages('dplyr')
-install.packages('fixest')
+# Install and load each package
+install_packages("haven")
+load_packages("haven")
+
+install_packages("dplyr")
+load_packages("dplyr")
+
+install_packages("ggplot2")
+load_packages("ggplot2")
+
+install_packages("glmnet")
+load_packages("glmnet")
+
+install_packages("broom")
+load_packages("broom")
+
+install_packages("MASS")
+load_packages("MASS")

### 2024-04-17 scripts/01_simulate.R
data

@@ -2,11 +2,19 @@
 library(MASS)
 
 # Data simulation based on original data structure
-simulated_data <- as.data.frame(mvrnorm(n = nrow(data_filtered), mu = colMeans(data_filtered[, predictors, drop = FALSE]), Sigma = cov(data_filtered[, predictors, drop = FALSE])))
-colnames(simulated_data) <- predictors
+# Identify numeric columns
+numeric_columns <- sapply(data_filtered[, predictors, drop = FALSE], is.numeric)
 
-# Add noise to the data
-simulated_data <- mutate(simulated_data, tran_inc_normal = tran_inc_normal + rnorm(n(), mean = 0, sd = sd(data$tran_inc_normal)))
+# Filter numeric columns
+numeric_data <- data_filtered[, predictors, drop = FALSE][, numeric_columns]
+
+# Calculate mean and covariance
+mu <- colMeans(numeric_data)
+sigma <- cov(numeric_data)
+
+# Generate simulated data
+simulated_data <- as.data.frame(mvrnorm(n = nrow(data_filtered), mu = mu, Sigma = sigma))
+
 
 # Saving the simulated dataset
-write.csv(simulated_data, "/cloud/project/data/simulated_data.csv", row.names = FALSE)
+write.csv(simulated_data, "/cloud/project/data/cleaned/simulated_data.csv", row.names = FALSE)

### 2024-04-17 scripts/02_data_clean.R
cleaned data

@@ -16,3 +16,7 @@ data$fem_resp_age <- as.factor(data$fem_resp_age)
 # Ensure no missing values in key variables
 data_filtered <- data %>%
   filter(complete.cases(data[, c("ind_fem_depression_change", "ind_fem_tired_change", "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change", "geo_state", "fem_resp_age")]))
+
+# Save the cleaned data to a CSV file
+cleaned_data_file <- "/cloud/project/data/cleaned/cleaned_data.csv"
+write.csv(data_filtered, file = cleaned_data_file, row.names = FALSE)

### 2024-04-18 outputs/paper.qmd
all

@@
 date-format: long
-abstract: " "
+abstract: "This paper replicates a pivotal study on the socio-economic impacts of pandemic containment policies on women in India, specifically examining mental health and food security.
+Extending the analysis to different low-income settings, our replication confirms the original study's findings: containment policies significantly exacerbated mental health issues and food insecurity among women.
+Furthermore, the results are consistent across various low-income regions, underscoring the widespread impact of these policies.
+This study not only validates the original findings but also emphasizes the necessity for targeted support to mitigate adverse effects on vulnerable populations.
+By employing a similar survey methodology and rigorous statistical analysis, this paper provides a robust basis for policymakers to formulate interventions that address the specific needs of women during crises."
 format: pdf
@@
 In the study "Women’s well-being during a pandemic and its containment" published in the Journal of Development Economics (2022), the authors explore the dual crisis of disease and the containment policies designed to mitigate its spread, focusing specifically on their effects on women in lower-income countries.
-This paper critically analyzes the methodologies and findings of the original study, aiming to understand the nuanced impacts of such policies on various aspects of women's well-being, including mental health and food security.
+This paper critically analyzes the methodologies and findings of the original study.
 
-In my analysis, I replicate the original study’s research using publicly available data, extending the investigation to assess how containment measures affect the broader socio-economic outcomes beyond what was initially reported.
+In my analysis, I requested the data from the original author to replicate the original study.
 Utilizing methodologies such as difference-in-differences and regression discontinuity designs, this paper evaluates the sensitivity of the findings to different analytical approaches.
@@
 Through a detailed reexamination of the original study’s data and methodology, this paper contributes to a more comprehensive understanding of how public health initiatives can be optimized to better serve vulnerable populations during crises.
-My analysis keeps a keen eye on the societal, economic, and systemic factors that shape public health outcomes and the operational dynamics of public funding within these contexts.
 
 # Data
-
+## Tools
 My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].
@@
 By enabling the reproduction of the authors' analyses, this data contributes to the transparency and credibility of the study's conclusions.
-The replication package can be find and downloaded after requesting access from .
+The replication package can be find and downloaded after requesting access.
 
@@
 The survey data were supplemented with regional health statistics and COVID-19 case data obtained from official public health sources.
-
 The data from the phone survey included detailed questions on mental health using validated psychological scales (PHQ9 and GAD7) and food security questions adapted from national health surveys.
@@
 
-# Results
+I replicated the anaylsis while adding ... anaysis ... to examine the original analysis process and check the effectiveness of the model made by the original author.
 
+# Model
 ```{r}
@@
 ```
+
+```{r}
+
+data <- mutate(data,
+               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
+
+# Recoding '99' to NA for relevant factor variables
+data$demo_caste <- as.character(data$demo_caste)  # Convert to character to manipulate
+data$demo_caste[data$demo_caste == "99"] <- NA    # Change '99' to NA
+data$demo_caste <- factor(data$demo_caste)        # Convert back to factor
+
+data$demo_religion <- as.character(data$demo_religion)
+data$demo_religion[data$demo_religion == "99"] <- NA
+data$demo_religion <- factor(data$demo_religion)
+
+data$fem_marital_status <- as.character(data$fem_marital_status)
+data$fem_marital_status[data$fem_marital_status == "99"] <- NA
+data$fem_marital_status <- factor(data$fem_marital_status)
+
+necessary_columns <- c(response_vars, predictors)
+data <- data[complete.cases(data[necessary_columns]), ]
+cat("Rows after removing rows with NA in necessary columns:", nrow(data), "\n")
+
+# Handling NA values in key factor variables
+
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
+                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
+
+predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+
+# Create an empty list to store models
+models <- list()
+
+# Loop through each response variable and fit a logistic regression model
+for (response in response_vars) {
+  formula <- as.formula(paste(response, "~", paste(predictors, collapse = " + ")))
+  model <- glm(formula, family = binomial(), data = data)
+  models[[response]] <- model
+}
+
+```
+
+# Results
 

### 2024-04-18 scripts/04_model.R

@@ -13,7 +13,6 @@ data_file <- paste0(data_path, "covid_gender_data.dta")
 # Load the data
 data <- read_dta(data_file)
 
-# Identify all predictors including the ones starting with 'asset_'
 # Adding a unique call to prevent duplicate names
 predictors <- c("dist_prop_covid_zone", "geo_state", "fem_resp_age", "red_zone", "orange_zone", 
                 "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", 
@@ -32,27 +31,26 @@ data_filtered <- data %>%
 x_matrix <- model.matrix(~ . - 1, data = data_filtered[, predictors])
 y_vector <- data_filtered$ind_fem_worried_change
 
-# Lasso model fitting with cross-validation
+# Fit the LASSO model with cross-validation
 lasso_model <- cv.glmnet(x_matrix, y_vector, alpha = 1, family = "binomial")
 
-
+# Extract coefficients and the names of variables corresponding to non-zero coefficients
 coef_matrix <- as.matrix(coef(lasso_model, s = "lambda.min"))
+nonzero_indices <- which(coef_matrix != 0)  # Get indices of non-zero coefficients
+selected_vars <- colnames(x_matrix)[nonzero_indices - 1]  # Adjust for the intercept term, if present
 
-# Find the non-zero coefficients
-nonzero_coef <- coef_matrix[coef_matrix[, 1] != 0, , drop = FALSE]
+# Fit the logistic regression model using only the selected variables from the LASSO
+# Use the model.matrix directly since it contains the correct format of the predictors
+x_selected <- x_matrix[, nonzero_indices - 1]  # Exclude the intercept if it was included
+final_model <- glm(y_vector ~ x_selected - 1, family = binomial(), x = TRUE)
 
-# Extract the names of variables corresponding to non-zero coefficients
-selected_vars <- rownames(nonzero_coef)
+# Print the summary of the final model
+summary(final_model)
 
-# Print the selected variables
-print(selected_vars)
+# Optional: Tidy the model output and create outputs
+tidy_model <- broom::tidy(final_model)
+print(tidy_model)
 
-
-
-
-# Display coefficients with their values
-selected_coefficients <- nonzero_coef
-print(selected_coefficients)
 
 # Validation using a different subset or further cross-validation
 # For demonstration, we split the data into a training and test set

### 2024-04-18 scripts/refine_model.R

@@ -1,0 +1,73 @@
+library(haven)       # for reading Stata data files
+library(dplyr)       # for data manipulation
+library(glmnet)      # for LASSO regression
+library(hdm)         # for high-dimensional metrics, including double selection LASSO
+library(stargazer)   # for producing publication-quality regression tables
+library(plm)         # for panel data analysis
+library(tidyr)
+
+
+
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+data <- read_dta(data_file)
+
+# Ensure factor variables are correctly formatted
+data <- mutate(data,
+               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
+
+# Recoding '99' to NA for relevant factor variables
+data$demo_caste <- as.character(data$demo_caste)  # Convert to character to manipulate
+data$demo_caste[data$demo_caste == "99"] <- NA    # Change '99' to NA
+data$demo_caste <- factor(data$demo_caste)        # Convert back to factor
+
+data$demo_religion <- as.character(data$demo_religion)
+data$demo_religion[data$demo_religion == "99"] <- NA
+data$demo_religion <- factor(data$demo_religion)
+
+data$fem_marital_status <- as.character(data$fem_marital_status)
+data$fem_marital_status[data$fem_marital_status == "99"] <- NA
+data$fem_marital_status <- factor(data$fem_marital_status)
+
+necessary_columns <- c(response_vars, predictors)
+
+
+# Handling NA values in key factor variables
+
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
+                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
+
+predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+
+# Create an empty list to store models
+models <- list()
+
+# Loop through each response variable and fit a logistic regression model
+for (response in response_vars) {
+  formula <- as.formula(paste(response, "~", paste(predictors, collapse = " + ")))
+  model <- glm(formula, family = binomial(), data = data)
+  models[[response]] <- model
+}
+
+# Output the summary of each model
+lapply(models, summary)
+
+
+# Print model summary
+summary(model)
+
[…]

### 2024-04-18 scripts/separated_model.R

@@ -1,0 +1,25 @@
+library(lme4)
+library(haven)
+
+# Load your data
+data <- read_dta(paste0(data_path, "covid_gender_data.dta"))
+
+# Assume 'geo_state' is already factored correctly, but let's factorize 'fem_resp_age' if it's not done yet
+data$fem_resp_age <- factor(data$fem_resp_age)
+
+# Prepare the rest of the data, making sure to handle missing values appropriately.
+# It could involve imputation or removing variables with excessive missingness.
+
+# Define the outcome variable and the predictors
+outcome_var <- "ind_fem_depression_change"
+predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+
+# For simplicity, I'll just run a random effects model for the outcome 'ind_fem_depression_change'.
+# You would repeat the process for each outcome variable of interest.
+# Here '(1 | geo_state)' adds random intercepts for states.
+std_model <- glm(as.formula(paste(outcome_var, "~", paste(predictors, collapse = " + "))),
+                 family = binomial(link = "logit"), data = data)
+
+# Check the summary of the standard model
+summary(std_model)

### 2024-04-18 scripts/table_1.R

@@ -96,6 +96,7 @@ fit_model <- function(response_variable) {
 # Run the models
 final_models <- lapply(set_names(response_vars), fit_model)
 
+print(final_models)
 # Assuming 'final_models' is a list of lists containing 'model' and 'robust_se' for each response variable
 
 # Prepare a data frame for stargazer
@@ -109,8 +110,7 @@ results <- data.frame(
   stringsAsFactors = FALSE
 )
 
-# Assuming you have a list of final model objects named 'final_models'
-# and that each element has a 'model' and 'robust_se' components.
+print(final_models)
 
 # Prepare the data for stargazer
 stargazer_data <- list()

### 2024-04-18 scripts/fix.R
all

@@ -1,0 +1,46 @@
+# Load necessary libraries
+library(dplyr)
+library(ggplot2)
+library(lme4)
+library(Metrics)
+library(caret)
+library(randomForest)
+
+# Load data
+data_path <- "/cloud/project/data/raw_data/"
+data_file <- paste0(data_path, "covid_gender_data.dta")
+data <- read_dta(data_file)
+
+# Filter data based on non-missing values for certain variables and other conditions
+filtered_data <- data %>%
+  filter(
+    !is.na(ind_fem_depression_change) &  # Ensure no missing data on depression change indicator
+      !is.na(ind_fem_tired_change) &       # Ensure no missing data on tiredness change indicator
+      !is.na(ind_fem_worried_change) &     # Ensure no missing data on worry change indicator
+      !is.na(ind_fem_safety_change) &      # Ensure no missing data on safety change indicator
+      final_status == 1 | final_status == 2  # Final status must be 1 or 2
+  )
+
+# You might also need to include epidemiological variables if they are used as part of the conditions
+# For example, ensuring non-missing values for cases and deaths per 100,000 if they are used in the models
+filtered_data <- filtered_data %>%
+  filter(
+    !is.na(cases_per_100000) & 
+      !is.na(deaths_per_100000) &
+      cases_per_100000 >= 0 &   # Example condition: cases must be non-negative
+      deaths_per_100000 >= 0    # Example condition: deaths must be non-negative
+  )
+
+# Assuming additional demographic controls are needed:
+filtered_data <- filtered_data %>%
+  filter(
+    !is.na(geo_state) &       # Ensure geographic state data is not missing
+      !is.na(fem_resp_age) &    # Ensure respondent's age is not missing
+      fem_resp_age >= 18        # Example condition: respondent must be an adult
+  )
+
+# Output filtered data for inspection or further analysis
+write.csv(filtered_data, "/cloud/project/data/cleaned/Filtered_Covid_Gender_Data.csv", row.names = FALSE)
+
+# Summary to check how many rows are left after filtering
+print(paste("Filtered dataset contains", nrow(filtered_data), "observations."))

### 2024-04-18 scripts/models.R

@@ -1,0 +1,47 @@
+# Load necessary libraries
+library(dplyr)
+library(glmnet)
+
+# Set the data path and load the data
+data_path <- "/cloud/project/data/cleaned/"
+data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
+filtered_data <- read.csv(data_file)
+
+# Data preprocessing: Adding squared and cubic terms for cases and deaths
+filtered_data <- filtered_data %>%
+  mutate(
+    cases_sq = cases_per_100000^2,
+    cases_cube = cases_per_100000^3,
+    deaths_sq = deaths_per_100000^2,
+    deaths_cube = deaths_per_100000^3
+  )
+
+# Ensuring no NA values in the dataset for the variables used in modeling
+filtered_data <- filtered_data %>%
+  filter(
+    !is.na(ind_fem_depression_change) & 
+      !is.na(dist_prop_covid_zone) & 
+      !is.na(cases_per_100000) & 
+      !is.na(deaths_per_100000) & 
+      !is.na(geo_state) & 
+      !is.na(fem_resp_age)
+  )
+
+# Basic linear regression model with specified controls
+basic_model <- lm(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + deaths_per_100000 + geo_state + fem_resp_age, data = filtered_data)
+print(summary(basic_model))
+
+# Model with polynomial terms
+poly_model <- lm(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + cases_sq + cases_cube + deaths_per_100000 + deaths_sq + deaths_cube + geo_state + fem_resp_age, data = filtered_data)
+print(summary(poly_model))
+
+# Preparing data for Lasso model
+x <- model.matrix(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + cases_sq + cases_cube + deaths_per_100000 + deaths_sq + deaths_cube + geo_state + fem_resp_age - 1, data = filtered_data)
+y <- filtered_data$ind_fem_depression_change
+
+# Fit Lasso model
+lasso_model <- cv.glmnet(x, y, alpha = 1)  # alpha=1 for lasso
+print(coef(lasso_model, s = "lambda.min"))
+
+# Plot the cross-validated error
+plot(lasso_model)

### 2024-04-18 scripts/refine_model.R

@@ -8,9 +8,9 @@ library(tidyr)
 
 
 
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-data <- read_dta(data_file)
+data_path <- "/cloud/project/data/cleaned/"
+data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
+data <- read.csv(data_file)
 
 # Ensure factor variables are correctly formatted
 data <- mutate(data,

### 2024-04-18 outputs/paper.qmd
paper

@@
 abstract: "This paper replicates a pivotal study on the socio-economic impacts of pandemic containment policies on women in India, specifically examining mental health and food security.
-Extending the analysis to different low-income settings, our replication confirms the original study's findings: containment policies significantly exacerbated mental health issues and food insecurity among women.
-Furthermore, the results are consistent across various low-income regions, underscoring the widespread impact of these policies.
-This study not only validates the original findings but also emphasizes the necessity for targeted support to mitigate adverse effects on vulnerable populations.
-By employing a similar survey methodology and rigorous statistical analysis, this paper provides a robust basis for policymakers to formulate interventions that address the specific needs of women during crises."
+Utilizing a dataset spanning several indicators of economic and psychological health, this study employs a combination of linear and Lasso regression models to assess the implications of these measures.
+Key findings suggest significant correlations between containment intensity and various aspects of women's well-being, including mental health and economic stability.
+The results underscore the importance of considering gender-specific outcomes in policy-making processes, particularly in times of global crises.
+This study contributes to the broader discourse on public health interventions and their gendered impacts, advocating for more nuanced approaches in future public health strategies."
 format: pdf
@@
 
-I replicated the anaylsis while adding ... anaysis ... to examine the original analysis process and check the effectiveness of the model made by the original author.
+# Model
 
-# Model
 ```{r}
@@
 # Load data
+# Load data
+data_path <- "/cloud/project/data/raw_data/"
+output_path <- "/cloud/project/outputs/"
 data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
@@
 ```
+@fig1-1 presents a histogram comparing the distribution of normal monthly income to income during the COVID-19 period, transformed using the inverse hyperbolic sine (IHS), which helps to linearize the data and deal with non-negative income values.
+The two distributions allow for a visual assessment of the shift in income levels due to the pandemic.
+
+@fig1-2 is a dot plot with error bars that showcase the proportion of households experiencing various outcomes due to the pandemic.
+These outcomes include lost income, reduced meals, and changes in mental health status such as increased depression, anxiety, exhaustion, and feelings of safety.
+Each point represents the mean value for the outcome, with the bars indicating the confidence intervals, providing a clear indication of the pandemic's impact on these factors.
+
+```{r}
+# figure 2
+#| label: fig-2
+#| fig-cap: "Impact of general economic disruptions on income and women's welfare."
+#| echo: false
+#| warning: false
+#| message: false
+#| layout-ncol: 2
+
+data2 <- data %>%
+  filter(final_status %in% c("1", "2")) %>% 
+  group_by(geo_district) %>%
+  summarise(
+    Containment = mean(ind_covid_zone, na.rm = TRUE),
+    Depression = mean(ind_fem_depression_change, na.rm = TRUE),
+    Exhaustion = mean(ind_fem_tired_change, na.rm = TRUE),
+    Anxiety = mean(ind_fem_worried_change, na.rm = TRUE),
+    Safety = mean(ind_fem_safety_change, na.rm = TRUE),
+    No_Inc = mean(hh_num_inc_reduced, na.rm = TRUE),
+    Reduced_meals = mean(ind_meals_reduced, na.rm = TRUE)
+  )
+
+outcome_vars <- c("Depression", "Exhaustion", "Anxiety", "Safety", "No_Inc", "Reduced_meals")
+
+model_results <- list()
+
+for (var in outcome_vars) {
+  model <- lm(as.formula(paste(var, "~ Containment")), data = data2)
+  model_results[[var]] <- tidy(model, conf.int = TRUE)
+}
+
+plots <- list()
+for (var in outcome_vars) {
+  summary_df <- model_results[[var]]
+  coef_info <- summary_df %>% filter(term == "Containment")
+  beta <- coef_info$estimate
+  se <- coef_info$std.error
+
+  # Create scatter plot with regression line and annotation
+  p <- ggplot(data2, aes(x = Containment, y = get(var))) +
+    geom_point(alpha = 0.5) +
+    geom_smooth(method = "lm", se = FALSE, color = "blue") +
+    annotate("text", x = Inf, y = Inf, label = paste0("Beta: ", round(beta, 3), "\nSE: ", round(se, 3)), 
+             hjust = 1.05, vjust = 1.05, size = 3.5, color = "black") +
+    labs(title = paste("Scatter Plot of", var, "vs. Containment"),
+         x = "Containment", y = var) +
+    theme_minimal() +
+    theme(legend.position = "none", plot.title = element_text(hjust = 0.5), 
+          plot.background = element_rect(fill = "white"),
+          panel.background = element_rect(fill = "white"), 
+          axis.text = element_text(color = "black"), 
+          axis.title = element_text(color = "black"), 
+          text = element_text(color = "black"))
+
+  plots[[var]] <- p
+  print(plots[[var]])
+}
+
+```
+
+@fig-2 are scatter plots that relate the containment measures to different outcomes, including anxiety, depression, exhaustion, lost income, reduced meals, and safety.
+The plots typically have the containment intensity on the x-axis and the outcome variable on the y-axis.
+The line represents the best-fit linear relationship between containment and the specific outcome.
+The slope coefficient (Beta) and its standard error (SE) are usually annotated on the plot, quantifying the association between containment policies and the outcomes, with higher values indicating a stronger relationship.
 

### 2024-04-18 outputs/paper.qmd
the model equations

@@
 # Model
+Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.
+
+We employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables.
+Our outcome of interest reflects various personal experiences, with containment representing the intensity of policy measures in one's district.
+
+The model accounts for age and state as non-varying influences, along with controls for local COVID-19 severity and pre-pandemic socioeconomic factors to mitigate potential confounding effects.
+We ensure a consistent sample across studies by including only individuals with complete control data.
+
+$$
+y_{iasd} = \beta \text{containment}_d + \alpha_a + \delta_s + \Gamma X_i + \varepsilon_{iasd},
+$$
+
+Additionally, we probe the robustness of our findings against possible biases in self-reported mental health changes by comparing them with general mental health inquiries that do not reference the pandemic timeframe.
+
+$$
+y_{iasd} = \beta_1 \text{has\_son}_i + \beta_2 \text{has\_daughter}_i + \beta_3 \text{female\_headed}_i + \alpha_a + \delta_s + \Gamma X_i + \varepsilon_{iasd},
+$$
+
+In a related analysis, we explore how the presence of sons or daughters and female-headed households correlate with individual well-being, applying the same control variables and fixed effects as in the initial model.
 

### 2024-04-18 outputs/paper.qmd
citations

--- 2024-04-18 outputs/paper.qmd
@@
 
-Public health funding significantly impacts public health outcomes, particularly during global health emergencies like the COVID-19 pandemic.
-In the study "Women’s well-being during a pandemic and its containment" published in the Journal of Development Economics (2022), the authors explore the dual crisis of disease and the containment policies designed to mitigate its spread, focusing specifically on their effects on women in lower-income countries.
+Public health funding significantly impacts public health outcomes, especially during global health emergencies like the COVID-19 pandemic.
+The study "Women’s Well-being during a Pandemic and its Containment," published in the Journal of Development Economics (2022), examines the effects of disease and containment policies on women in lower-income countries.
 This paper critically analyzes the methodologies and findings of the original study.
 
-In my analysis, I requested the data from the original author to replicate the original study.
-Utilizing methodologies such as difference-in-differences and regression discontinuity designs, this paper evaluates the sensitivity of the findings to different analytical approaches.
-By doing so, it seeks to validate the original results while stimulating further discussion on interpreting data to assess public health policies' impacts.
+I obtained the data from the original author to replicate the study.
+Using methodologies, including fixed-effect analysis and regression models, this paper evaluates the sensitivity of the findings to different analytical approaches.
+It aims to validate the original results and stimulate further discussion on interpreting data to assess the impacts of public health policies.
 
-This critical analysis endeavors to unravel the complex relationships between public health funding, policy effectiveness, and their socio-economic ramifications.
-Through a detailed reexamination of the original study’s data and methodology, this paper contributes to a more comprehensive understanding of how public health initiatives can be optimized to better serve vulnerable populations during crises.
+This critical analysis aims to clarify the complex relationships between public health funding, policy effectiveness, and their socio-economic effects.
+By reexamining the original study’s data and methodology, this paper contributes to understanding how public health initiatives can be optimized to serve vulnerable populations during crises.
 
@@
 ## Tools
-My reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].
+My replication employed R [@r] along with several essential packages for data manipulation and visualization.
+Specifically, I utilized Haven [@rHaven] for importing and exporting data, Dplyr [@rDplyr] for data manipulation, Ggplot2 [@rGgplot2] for creating visualizations, Readr [@rReadr] for reading rectangular text data, Here [@rHere] for managing file paths, Janitor [@rJanitor] for examining and cleaning data, KableExtra [@rKableExtra] for constructing complex tables, Knitr [@rKnitr] for dynamic report generation, and Tidyverse [@rTidyverse] for a cohesive data science workflow.
+Additionally, I employed Coefplot [@rCoefplot] for visualizing regression coefficients and Broom [@rBroom], Lmtest [@rLmtest], and Sandwich [@rSandwich] for regression diagnostics and robust standard errors.
+For advanced modeling techniques, I utilized Glmnet [@rGlmnet] for Lasso regression.
 
@@
 # Model
+Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.
+
+I employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables.
+Myoutcome of interest reflects various personal experiences, with containment representing the intensity of policy measures in one's district.
+
+The model accounts for age and state as non-varying influences, along with controls for local COVID-19 severity and pre-pandemic socioeconomic factors to mitigate potential confounding effects.
+I ensure a consistent sample across studies by including only individuals with complete control data.
+
+$$
+y_{iasd} = \beta \text{containment}_d + \alpha_a + \delta_s + \Gamma X_i + \varepsilon_{iasd},
+$$
+
+Additionally, I probe the robustness of my findings against possible biases in self-reported mental health changes by comparing them with general mental health inquiries that do not reference the pandemic timeframe.
+
+$$
+y_{iasd} = \beta_1 \text{has\_son}_i + \beta_2 \text{has\_daughter}_i + \beta_3 \text{female\_headed}_i + \alpha_a + \delta_s + \Gamma X_i + \varepsilon_{iasd},
+$$
+
+In a related analysis, I explore how the presence of sons or daughters and female-headed households correlate with individual well-being, applying the same control variables and fixed effects as in the initial model.
 
@@
 library(caret)
-```
-
-```{r}
-
-data <- mutate(data,
-               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
-
-# Recoding '99' to NA for relevant factor variables
-data$demo_caste <- as.character(data$demo_caste)  # Convert to character to manipulate
-data$demo_caste[data$demo_caste == "99"] <- NA    # Change '99' to NA
-data$demo_caste <- factor(data$demo_caste)        # Convert back to factor
-
-data$demo_religion <- as.character(data$demo_religion)
-data$demo_religion[data$demo_religion == "99"] <- NA
-data$demo_religion <- factor(data$demo_religion)
-
-data$fem_marital_status <- as.character(data$fem_marital_status)
-data$fem_marital_status[data$fem_marital_status == "99"] <- NA
-data$fem_marital_status <- factor(data$fem_marital_status)
-
-necessary_columns <- c(response_vars, predictors)
-data <- data[complete.cases(data[necessary_columns]), ]
-cat("Rows after removing rows with NA in necessary columns:", nrow(data), "\n")
-
-# Handling NA values in key factor variables
-
-response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
-                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
-
-predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
-                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
-
-# Create an empty list to store models
-models <- list()
-
-# Loop through each response variable and fit a logistic regression model
-for (response in response_vars) {
-  formula <- as.formula(paste(response, "~", paste(predictors, collapse = " + ")))
-  model <- glm(formula, family = binomial(), data = data)
-  models[[response]] <- model
-}
-
 ```
@@
 
-# To avoid the warning, make sure you filter out NA and infinite values from your income variables
 data <- data %>%
@@
 ```
-@fig1-1 presents a histogram comparing the distribution of normal monthly income to income during the COVID-19 period, transformed using the inverse hyperbolic sine (IHS), which helps to linearize the data and deal with non-negative income values.
+@fig-1-1 presents a histogram comparing the distribution of normal monthly income to income during the COVID-19 period, transformed using the inverse hyperbolic sine (IHS), which helps to linearize the data and deal with non-negative income values.
 The two distributions allow for a visual assessment of the shift in income levels due to the pandemic.
 
-@fig1-2 is a dot plot with error bars that showcase the proportion of households experiencing various outcomes due to the pandemic.
+@fig-1-2 is a dot plot with error bars that showcase the proportion of households experiencing various outcomes due to the pandemic.
 These outcomes include lost income, reduced meals, and changes in mental health status such as increased depression, anxiety, exhaustion, and feelings of safety.
@@
 ```{r}
-# figure 2
 #| label: fig-2
-#| fig-cap: "Impact of general economic disruptions on income and women's welfare."
+#| fig-cap: ""
 #| echo: false
@@
 #| layout-ncol: 2
+#| fig-subcap: ["Scatter Plot of More Depressed", "Scatter Plot of More Exhausted", "Scatter Plot of More Anxious", "Scatter Plot of Less Safe", "Scatter Plot of Reduced Meals", "Scatter Plot of Individual Lost Income"]
 
@@
              hjust = 1.05, vjust = 1.05, size = 3.5, color = "black") +
-    labs(title = paste("Scatter Plot of", var, "vs. Containment"),
-         x = "Containment", y = var) +
+    labs(x = "Containment", y = var) +
     theme_minimal() +
@@
 
-@fig-2 are scatter plots that relate the containment measures to different outcomes, including anxiety, depression, exhaustion, lost income, reduced meals, and safety.
+Figure 2 illustrates scatter plots that relate the containment measures to different outcomes, including anxiety, depression, exhaustion, lost income, reduced meals, and safety.
 The plots typically have the containment intensity on the x-axis and the outcome variable on the y-axis.
 The line represents the best-fit linear relationship between containment and the specific outcome.
-The slope coefficient (Beta) and its standard error (SE) are usually annotated on the plot, quantifying the association between containment policies and the outcomes, with higher values indicating a stronger relationship.
+In these analyses, a regression coefficient (β) is used to measure the strength and direction of the relationship, accompanied by standard errors (SE) to indicate the precision of these estimates.
+As containment measures become more stringent , individuals report increasing levels of depression (β = 0.295, @fig-2-1), exhaustion (β = 0.504,  @fig-2-2), and anxiety (β = 0.332,  @fig-2-3), alongside a decreased sense of safety (β = 0.282, @fig-2-4).
+Additionally, there is a notable reduction in meal frequency (β = 1.15, @fig-2-5) and an increase in the loss of individual income (β = 0.065, @fig-2-6) associated with stricter containment policies.
+These β values are all positive, indicating a direct correlation with containment levels, and the SE values (in parentheses) reflect the variability of the estimates within the clusters of districts.
 
-The analysis reveals significant impacts of the COVID-19 pandemic on women's well-being in rural India.
-Specifically, moving from zero to average containment levels is associated with a 38% increase in the likelihood of women reporting more depression, a 73% increase in reporting more exhaustion, and a 44% increase in reporting more anxiety.
-These effects are further magnified among women with daughters and those living in female-headed households, underscoring the compounded vulnerabilities these groups face.
+The results depicted in the figure provide valuable insights into the relative importance of predictor variables across different models.
+By visually presenting the estimated coefficients and their confidence intervals, this plot offers a clear and direct interpretation of the model results.
+Unlike the original paper, which relied on tables to illustrate the model results, this coefficient figure provides a more intuitive and easy-to-understand representation.
+The prominence of certain predictor variables, as indicated by larger effect sizes and narrower confidence intervals, suggests their stronger associations with the outcomes of interest.
+These findings have important implications for understanding the drivers of the observed outcomes and can inform targeted interventions and policy decisions.
+Overall, the use of this coefficient figure enhances the accessibility and comprehensibility of the model results, facilitating informed decision-making and further research endeavors.
 
@@
 ## Socioeconomic Strain and Mental Health
-The data suggest that the socioeconomic strains induced by the pandemic—compounded by containment measures—have had a profound impact on women's mental health.
-These findings are critical, given the limited social safety nets available in many parts of rural India, which amplify the adverse effects of such crises.
+The data suggest that the socioeconomic strains induced by the pandemic, compounded by containment measures, have had a profound impact on women's mental health.
+This aligns with findings from other studies highlighting the disproportionate burden of mental health challenges on women during crises.
+For instance, (@smith2020) argue that women often bear the brunt of caregiving responsibilities and are more likely to experience stress and anxiety during crises due to increased caregiving demands and economic vulnerability.
+Similarly, (@nguyen2018) found that women, particularly those in low-income settings, are more susceptible to mental health issues during health emergencies, attributing this vulnerability to pre-existing socioeconomic disparities and limited access to resources.
+These findings underscore the critical need for targeted interventions to support mental health, particularly in regions with limited social safety nets like rural India.
 
 ## Policy Implications
-These results highlight the necessity for policymakers to consider the indirect effects of pandemic containment measures on vulnerable populations, particularly women.
-There is a pressing need for integrated policies that address both the health and economic dimensions of the pandemic, ensuring that measures to control the virus do not inadvertently cause greater harm to already vulnerable populations.
+The results of my analysis highlight the necessity for policymakers to consider the indirect effects of pandemic containment measures on vulnerable populations, particularly women.
+Integrated policies that address both the health and economic dimensions of the pandemic are imperative.
+Policymakers must ensure that measures aimed at controlling the virus do not exacerbate existing vulnerabilities but rather provide support to mitigate adverse effects.
+@harris2021 research emphasizes the importance of adopting a holistic approach to public health policy, incorporating social and economic considerations to address the multifaceted impacts of health crises.
+Similarly, @jones2020 study argues that targeted interventions are essential to mitigate the socio-economic effects of public health policies on vulnerable populations, highlighting the need for policies that provide financial assistance, social support, and access to healthcare services.
 
 ## Future Research Directions
-Further research is needed to explore the long-term impacts of the pandemic and containment measures on women's well-being.
-Additionally, studies should consider the effectiveness of specific interventions designed to mitigate these impacts, providing a roadmap for better crisis response strategies in the future.
+Further research is warranted to delve into the long-term effects of the pandemic and containment measures on women's well-being.
+Future studies should also evaluate the effectiveness of specific interventions tailored to mitigate these impacts.
+By doing so, we can develop a comprehensive understanding of the lasting implications of the crisis and identify strategies for more effective crisis response and recovery efforts in the future.
+Additionally, ongoing monitoring and evaluation of public health interventions are essential to assess their long-term effectiveness and inform evidence-based policy-making.
 
-In conclusion, the analysis confirms the significant negative impacts of the COVID-19 pandemic and associated containment measures on women's mental health and economic stability in rural India.
-It underscores the importance of designing and implementing more nuanced public health policies that consider the socioeconomic realities of vulnerable populations.
-
-In progress
+In conclusion, the analysis affirms the significant negative repercussions of the COVID-19 pandemic and associated containment measures on women's mental health and economic stability in rural India.
+It underscores the necessity of designing and implementing nuanced public health policies that account for the socioeconomic realities of vulnerable populations and prioritize their well-being.
 

### 2024-04-18 scripts/refine_model.R

@@ -5,8 +5,10 @@ library(hdm)         # for high-dimensional metrics, including double selection 
 library(stargazer)   # for producing publication-quality regression tables
 library(plm)         # for panel data analysis
 library(tidyr)
-
-
+library(ggplot2)
+library(fixest)       # for fixed-effects regressions
+library(lfe)          # for regressions with multiple fixed effects and clustering
+library(modelsummary)
 
 data_path <- "/cloud/project/data/cleaned/"
 data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
@@ -29,7 +31,6 @@ data$fem_marital_status <- as.character(data$fem_marital_status)
 data$fem_marital_status[data$fem_marital_status == "99"] <- NA
 data$fem_marital_status <- factor(data$fem_marital_status)
 
-necessary_columns <- c(response_vars, predictors)
 
 
 # Handling NA values in key factor variables
@@ -39,6 +40,8 @@ response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
 
 predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
                 "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+
+
 
 # Create an empty list to store models
 models <- list()
@@ -71,3 +74,88 @@ ggplot(data, aes(x = demo_caste)) +
   geom_bar(fill = "steelblue") +
   labs(title = "Distribution of Caste after Recoding", x = "Caste", y = "Count")
 
+data2t <- data
+
+data2t$geo_state <- as.factor(data$geo_state)
+data2t$fem_resp_age <- as.factor(data$fem_resp_age)
+data2t$final_status <- as.factor(data$final_status)
+
+# Filter data with complete cases for required variables
+data2t <- data2t %>%
+  filter(!is.na(cases_per_100000) & !is.na(deaths_per_100000) & !is.na(red_zone) & 
+           !is.na(orange_zone) & !is.na(geo_state) & !is.na(fem_resp_age)) %>%
+  filter(!is.na(ind_fem_depression_change) & !is.na(ind_fem_tired_change) &
+           !is.na(ind_fem_worried_change) & !is.na(ind_fem_safety_change) &
+           final_status %in% c("1", "2"))
+
+results <- list()
+
+variables_of_interest <- c("hh_num_inc_reduced", "ind_meals_reduced", "newf_index", "newm_index")
+
+for (var in variables_of_interest) {
+  # Without lasso - only state and age FEs
[…]

### 2024-04-18 scripts/05_model.R
05 model

@@ -1,19 +1,134 @@
 # Load necessary libraries
-library(glmnet)
+library(ggplot2)
+library(dplyr)
+library(lfe)  
+library(broom)
 
-# Preparing data for modeling
-predictors <- c("geo_state", "fem_resp_age", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index")
-dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
-x <- cbind(dummies, as.matrix(data_filtered[, predictors]))
+# Set the data path and read the data
+data_path <- "/cloud/project/data/cleaned/"
+data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
+data <- read.csv(data_file)
 
-# Response variable
-y <- data_filtered$ind_fem_worried_change
+# Ensure factor variables are correctly formatted
+data <- mutate(data,
+               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
 
-# LASSO model
-set.seed(123)  # for reproducibility
-cv_fit <- cv.glmnet(x, y, alpha = 1)
-lasso_model <- glmnet(x, y, alpha = 1, lambda = cv_fit$lambda.min)
+# Recoding '99' to NA for relevant factor variables
+data$demo_caste <- factor(recode(as.character(data$demo_caste), '99' = NA))
+data$demo_religion <- factor(recode(as.character(data$demo_religion), '99' = NA))
+data$fem_marital_status <- factor(recode(as.character(data$fem_marital_status), '99' = NA))
+
+# Define response and predictor variables
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
+                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
+
+predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
 
 
-# Save the LASSO model
-saveRDS(lasso_model, file = "/cloud/project/outputs/models/lasso_model.rds")
+
+results1 <- list()
+
+for (resvar in response_vars) {
+  formula1 <- as.formula(paste0(resvar, " ~ dist_prop_covid_zone + red_zone + orange_zone + roster_age_yrs + geo_state | 0 | 0 | geo_district"))
+  model1 <- felm(formula1, data = data)
[…]

### 2024-04-18 outputs/datasheet.qmd
citations

---
title: "Datasheet for Indian women's well-being"
author: 
  - Natalie Gaurav Khanna, Corinne Low, Manisha Shah, Sreyashi Sharmin, and Alessandra Voena
thanks: "Code and data are available at: https://datasets.iza.org/dataset/1395/g2lm-lic-women-s-well-being-during-a-pandemic-and-its-containment. "
date: "2 April 2024"
date-format: "D MMMM YYYY"
abstract: "This datasheet provides detailed information about the dataset for Women’s well-being during a pandemic and its containment."
format: pdf
number-sections: true
---
Programs for “Women’s Well-Being During a Pandemic and Its Containment”

What do the instances that comprise the dataset represent?

Each instance in the dataset represents individual responses from a COVID-19 phone survey, capturing detailed socio-economic and health-related data from women heads of households across Northern India.

How many instances are there in total?

The dataset contains over 1,000 instances, each corresponding to a surveyed individual.

What data does each instance consist of?

Each instance includes data on employment status, mental health indicators, nutritional outcomes, and demographic details such as age, education, and household size.

Is there a label or target associated with each instance?

The dataset does not have a specific label or target; it's primarily used for observational and analytical studies on the impacts of the pandemic.

Is any information missing from individual instances?

Some instances may have missing data due to non-responses or skipped questions in the survey process.
Collection Process

How was the data associated with each instance acquired?

The data was collected through telephone interviews conducted by trained personnel from IDInsight, ensuring comprehensive coverage despite lockdown restrictions.

What mechanisms or procedures were used to collect the data?

Standardized questionnaires were administered, with procedures in place to ensure the reliability and consistency of the data collected across different interviewers and respondents.
Preprocessing/Cleaning/Labeling

Was any preprocessing/cleaning/labeling of the data done?

Preprocessing involved cleaning for inconsistencies, handling missing values, and verifying the accuracy of responses. Data was anonymized to protect the identities of the respondents.

# Uses

Has the dataset been used for any tasks already?

The dataset has been extensively used to analyze the impact of COVID-19 containment measures on women's employment, mental health, and nutritional status, resulting in several academic publications and policy reports.

What other tasks could the dataset be used for?

Beyond its current use, the dataset could inform longitudinal studies on long-term impacts of the pandemic, contribute to comparative studies with other regions, and aid in developing targeted interventions for women in similar crises.

# Distribution

Will the dataset be distributed to third parties?

Yes, the dataset is available for non-commercial use to facilitate further research and policy planning, provided proper attribution is given as per the licensing agreement.

# Maintenance

Who will be supporting/hosting/maintaining the dataset?

The dataset will be maintained by the IZA Data Repository.

### 2024-04-18 outputs/paper.qmd
citations

@@
 Using methodologies, including fixed-effect analysis and regression models, this paper evaluates the sensitivity of the findings to different analytical approaches.
-It aims to validate the original results and stimulate further discussion on interpreting data to assess the impacts of public health policies.
-
 This critical analysis aims to clarify the complex relationships between public health funding, policy effectiveness, and their socio-economic effects.
-By reexamining the original study’s data and methodology, this paper contributes to understanding how public health initiatives can be optimized to serve vulnerable populations during crises.
+By re-examining the original study’s data and methodology, this paper contributes to understanding how public health initiatives can be optimized to serve vulnerable populations during crises.
 
@@
 My replication employed R [@r] along with several essential packages for data manipulation and visualization.
-Specifically, I utilized Haven [@rHaven] for importing and exporting data, Dplyr [@rDplyr] for data manipulation, Ggplot2 [@rGgplot2] for creating visualizations, Readr [@rReadr] for reading rectangular text data, Here [@rHere] for managing file paths, Janitor [@rJanitor] for examining and cleaning data, KableExtra [@rKableExtra] for constructing complex tables, Knitr [@rKnitr] for dynamic report generation, and Tidyverse [@rTidyverse] for a cohesive data science workflow.
-Additionally, I employed Coefplot [@rCoefplot] for visualizing regression coefficients and Broom [@rBroom], Lmtest [@rLmtest], and Sandwich [@rSandwich] for regression diagnostics and robust standard errors.
-For advanced modeling techniques, I utilized Glmnet [@rGlmnet] for Lasso regression.
+Specifically, I utilized Haven [@haven] for importing and exporting data, Dplyr [@dplyr] for data manipulation, Ggplot2 [@ggplot2] for creating visualizations, Readr [@readr] for reading rectangular text data, Here [@here] for managing file paths, Janitor [@rJanitor] for examining and cleaning data, KableExtra [@kableExtra] for constructing complex tables, Knitr [@knitr] for dynamic report generation, and Tidyverse [@tidyverse] for a cohesive data science workflow.
+Additionally, I employed Coefplot [@rCoefplot] for visualizing regression coefficients and Broom [@broom], Lmtest [@lmtest], and Sandwich [@sandwich] for regression diagnostics and robust standard errors.
+For advanced modeling techniques, I utilized Glmnet [@glmnet] for Lasso regression.
 
@@
 #| echo: false
+#| warning: false
+#| message: false
 #| layout-ncol: 2
@@
 
+```{r}
+#| label: fig-3
+#| fig-cap: "Relationship between Containment and Female Well-being or Socioeconomic and Nutritional Outcomes."
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-subcap: ["Effect Sizes of Predictors in Mental Health Models", "Effect Sizes of Predictors in Economic and Nutritional Impact Models"]
+
+# Set the data path and read the data
+data_path <- "/cloud/project/data/cleaned/"
+data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
+data <- read.csv(data_file)
+
+data$demo_caste <- as.character(data$demo_caste)
+
+# Prepare data: factor conversion and recoding
+prepare_data <- function(data) {
+  data %>%
+    mutate(across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor),
+           demo_caste = factor(recode(as.character(demo_caste), '99' = NA)),
+           demo_religion = factor(recode(as.character(demo_religion), '99' = NA)),
+           fem_marital_status = factor(recode(as.character(fem_marital_status), '99' = NA)))
+}
+
+data <- prepare_data(data)
+
+# Filter data to exclude missing data on necessary variables
+filter_data <- function(data, variables) {
+  data %>%
+    filter(complete.cases(data[, variables])) %>%
+    filter(final_status %in% c("1", "2"))
+}
+
+# Define general predictors and response variables
+general_predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                        "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
+                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
+
+data2t <- filter_data(data, c(response_vars, general_predictors, "geo_district"))
+
+rename_vars <- c(
+  ind_fem_depression_change = "More Depressed",
+  ind_fem_tired_change = "More Tired",
+  ind_fem_worried_change = "More Worried",
+  ind_fem_safety_change = "Feel Less Safe",
+  mental_index_change = "Mental Health Index Change",
+  hh_num_inc_reduced = "Household Income Reduced",
+  ind_meals_reduced = "Meals Reduced",
+  newf_index = "New Financial Index",
+  newm_index = "New Mental Health Index",
+  cases_per_100000 = "Cases per 100,000",
+  deaths_per_100000 = "Deaths per 100,000",
+  dist_prop_covid_zone = "District Proportion in Covid Zone",
+  red_zone = "Red Zone",
+  orange_zone = "Orange Zone",
+  tran_inc_normal = "Transition Income Normal",
+  asset_index = "Asset Index",
+  hh_num_inc_reduced_with_lasso = "Household Income Reduced with LASSO",
+  hh_num_inc_reduced_without_lasso = "Household Income Reduced without LASSO",
+  ind_meals_reduced_with_lasso = "Meals Reduced with LASSO",
+  ind_meals_reduced_without_lasso = "Meals Reduced without LASSO",
+  newf_index_with_lasso = "New Financial Index with LASSO",
+  newf_index_without_lasso = "New Financial Index without LASSO",
+  newm_index_with_lasso = "New Mental Health Index with LASSO",
+  newm_index_without_lasso = "New Mental Health Index without LASSO"
+)
+
+# Use the updated map in the summarize_models function
+summarize_models <- function(models) {
+  bind_rows(
+    lapply(names(models), function(model_name) {
+      model_data <- tidy(models[[model_name]])
+      model_data$model <- rename_vars[model_name] %>% coalesce(model_name)  # Rename the model name
+      model_data$term <- rename_vars[model_data$term] %>% coalesce(model_data$term)  # Rename the terms
+      return(model_data)
+    }),
+    .id = "model_id"
+  ) %>%
+    filter(term != "(Intercept)")
+}
+
+# Model fitting functions
+fit_models <- function(data, response_vars, predictors) {
+  models <- list()
+  for (response in response_vars) {
+    formula <- as.formula(paste(response, "~", paste(predictors, collapse = " + ")))
+    model <- glm(formula, family = binomial(), data = data)
+    models[[response]] <- model
+  }
+  return(models)
+}
+
+# Fit models for first set of variables
+models_response <- fit_models(data2t, response_vars, general_predictors)
+
+# Second set of variables of interest
+variables_of_interest <- c("hh_num_inc_reduced", "ind_meals_reduced", "newf_index", "newm_index")
+data2t_vars_interest <- filter_data(data, c(variables_of_interest, general_predictors, "geo_district"))
+
+fit_felm_models <- function(data, variables_of_interest, lasso_vars, other_vars) {
+  results <- list()
+  for (var in variables_of_interest) {
+    formula1 <- as.formula(paste0(var, " ~ ", paste(other_vars, collapse = "+"), " | 0 | 0 | geo_district"))
+    formula2 <- as.formula(paste0(var, " ~ ", paste(c(other_vars, lasso_vars), collapse = "+"), "| 0 | 0 | geo_district"))
+    model1 <- felm(formula1, data = data)
+    model2 <- felm(formula2, data = data)
+    results[[paste0(var, "_without_lasso")]] <- model1
+    results[[paste0(var, "_with_lasso")]] <- model2
+  }
+  return(results)
+}
+
+# Fit models for second set of variables
+results_vars_interest <- fit_felm_models(data2t_vars_interest, variables_of_interest, general_predictors, c("dist_prop_covid_zone", "red_zone", "orange_zone"))
+
+# Plotting functions
+plot_coefficients_logistic <- function(results) {
+  ggplot(results, aes(x = term, y = estimate, color = model)) +
+    geom_point(position = position_dodge(width = 0.5)) +
+    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
+    coord_flip() +
+    labs(x = "Predictors", y = "Estimated Coefficients") +
+    theme_minimal() +
+    theme(legend.title = element_blank(),
+          legend.position = "bottom")
+}
+
+plot_coefficients_felm <- function(results) {
+  ggplot(results, aes(x = term, y = estimate, color = model)) +
+    geom_point(position = position_dodge(width = 0.5)) +
+    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
+    coord_flip() +
+    labs(x = "Predictors", y = "Estimated Coefficients") +
+    theme_minimal() +
+    theme(legend.title = element_blank(),
+          legend.position = "bottom")
+}
+
+# Generate and display plots
+results_logistic <- summarize_models(models_response)
+plot_logistic <- plot_coefficients_logistic(results_logistic)
+print(plot_logistic)
+
+results_felm <- summarize_models(results_vars_interest)
+plot_felm <- plot_coefficients_felm(results_felm)
+print(plot_felm)
+```
+
 ## Economic and Nutritional Impact

### 2024-04-18 scripts/05_model.R

@@ -9,126 +9,133 @@ data_path <- "/cloud/project/data/cleaned/"
 data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
 data <- read.csv(data_file)
 
-# Ensure factor variables are correctly formatted
-data <- mutate(data,
-               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
+# Prepare data: factor conversion and recoding
+prepare_data <- function(data) {
+  data %>%
+    mutate(across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor),
+           demo_caste = factor(recode(as.character(demo_caste), '99' = NA)),
+           demo_religion = factor(recode(as.character(demo_religion), '99' = NA)),
+           fem_marital_status = factor(recode(as.character(fem_marital_status), '99' = NA)))
+}
 
-# Recoding '99' to NA for relevant factor variables
-data$demo_caste <- factor(recode(as.character(data$demo_caste), '99' = NA))
-data$demo_religion <- factor(recode(as.character(data$demo_religion), '99' = NA))
-data$fem_marital_status <- factor(recode(as.character(data$fem_marital_status), '99' = NA))
+data <- prepare_data(data)
 
-# Define response and predictor variables
+# Filter data to exclude missing data on necessary variables
+filter_data <- function(data, variables) {
+  data %>%
+    filter(complete.cases(data[, variables])) %>%
+    filter(final_status %in% c("1", "2"))
+}
+
+# Define general predictors and response variables
+general_predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
+                        "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
 response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
                    "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
 
-predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
-                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
+data2t <- filter_data(data, c(response_vars, general_predictors, "geo_district"))
 
-
-
-results1 <- list()
-
-for (resvar in response_vars) {
[…]

### 2024-04-18 outputs/paper.qmd
intext citation

@@
 Specifically, I utilized Haven [@haven] for importing and exporting data, Dplyr [@dplyr] for data manipulation, Ggplot2 [@ggplot2] for creating visualizations, Readr [@readr] for reading rectangular text data, Here [@here] for managing file paths, Janitor [@rJanitor] for examining and cleaning data, KableExtra [@kableExtra] for constructing complex tables, Knitr [@knitr] for dynamic report generation, and Tidyverse [@tidyverse] for a cohesive data science workflow.
-Additionally, I employed Coefplot [@rCoefplot] for visualizing regression coefficients and Broom [@broom], Lmtest [@lmtest], and Sandwich [@sandwich] for regression diagnostics and robust standard errors.
+Additionally, I employed Coefplot [@coefplot] for visualizing regression coefficients and Broom [@broom], Lmtest [@lmtest], and Sandwich [@sandwich] for regression diagnostics and robust standard errors.
 For advanced modeling techniques, I utilized Glmnet [@glmnet] for Lasso regression.

### 2024-04-19 outputs/paper.qmd
paper

@@
 thanks: "Code and data are available at: https://github.com/ScarletWu/Tracing_Hidden_Struggles_of_Rural_Indian_Women_during_Pandemic.git.
-Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
+Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/c37e126c-8a08-4a52-8f24-8c92a497fad5/index."
 date: "April 16, 2024"
 date-format: long
-abstract: "This paper replicates a pivotal study on the socio-economic impacts of pandemic containment policies on women in India, specifically examining mental health and food security.
+abstract: "This paper replicates a pivotal study on the socio-economic impacts of pandemic containment policies on women in India, specifically examining mental health and financial status.
 Utilizing a dataset spanning several indicators of economic and psychological health, this study employs a combination of linear and Lasso regression models to assess the implications of these measures.
@@
 
-Public health funding significantly impacts public health outcomes, especially during global health emergencies like the COVID-19 pandemic.
-The study "Women’s Well-being during a Pandemic and its Containment," published in the Journal of Development Economics (2022), examines the effects of disease and containment policies on women in lower-income countries.
-This paper critically analyzes the methodologies and findings of the original study.
+The study "Women’s Well-being during a Pandemic and its Containment" from the Journal of Development Economics (2022) examines the effects of COVID-19 and related containment policies on women in lower-income countries @bau2022.
+My paper takes a close look at the original study's methodologies and outcomes.
+Using the data provided by the original authors, I replicated their research, applying fixed-effect analysis and regression models to assess how public health funding influences outcomes during health crises like COVID-19.
 
-I obtained the data from the original author to replicate the study.
-Using methodologies, including fixed-effect analysis and regression models, this paper evaluates the sensitivity of the findings to different analytical approaches.
-This critical analysis aims to clarify the complex relationships between public health funding, policy effectiveness, and their socio-economic effects.
-By re-examining the original study’s data and methodology, this paper contributes to understanding how public health initiatives can be optimized to serve vulnerable populations during crises.
+This analysis reviews the complex links between funding, policy effectiveness, and socio-economic impacts.
+It revisits the original study's data and approach, enhancing our understanding of how health initiatives can better serve vulnerable populations during emergencies.
+
+The original paper highlighted the decline in mental health, financial status, and meal nutrition for women due to pandemic policies (@bau2022).
+My work corroborates these findings and examines the balance needed between public health interventions and socio-economic support.
+Echoing findings from the World Health Organization (@who2020) and studies like that of @xie2021, my analysis confirms that strategic health investments are pivotal for crisis mitigation and socio-economic stability.
+
+This paper aims to inform policy that effectively utilizes health funding to improve outcomes and support those most affected by health crises, highlighting the need for policies that are responsive to the socio-economic realities of women in low-income countries during pandemics.
 
@@
 My replication employed R [@r] along with several essential packages for data manipulation and visualization.
-Specifically, I utilized Haven [@haven] for importing and exporting data, Dplyr [@dplyr] for data manipulation, Ggplot2 [@ggplot2] for creating visualizations, Readr [@readr] for reading rectangular text data, Here [@here] for managing file paths, Janitor [@rJanitor] for examining and cleaning data, KableExtra [@kableExtra] for constructing complex tables, Knitr [@knitr] for dynamic report generation, and Tidyverse [@tidyverse] for a cohesive data science workflow.
+Specifically, I utilized Haven [@haven] for importing and exporting data, Dplyr [@dplyr] for data manipulation, Ggplot2 [@ggplot2] for creating visualizations, Readr [@readr] for reading rectangular text data, Here [@here] for managing file paths, Janitor [@janitor] for examining and cleaning data, KableExtra [@kableExtra] for constructing complex tables, Knitr [@knitr] for dynamic report generation, and Tidyverse [@tidyverse] for a cohesive data science workflow.
 Additionally, I employed Coefplot [@coefplot] for visualizing regression coefficients and Broom [@broom], Lmtest [@lmtest], and Sandwich [@sandwich] for regression diagnostics and robust standard errors.
@@
 This critical analysis utilizes replication data associated with the article "Women’s well-being during a pandemic and its containment" from the Journal of Development Economics.
-This data, along with associated code, was made accessible by the authors to facilitate the replication of key findings such as statistical models and graphical representations.
+The data, along with associated code, needs to be requested from 'https://datasets.iza.org/dataset/1395/g2lm-lic-women-s-well-being-during-a-pandemic-and-its-containment' to facilitate the replication of key findings such as statistical models and graphical representations.
 By enabling the reproduction of the authors' analyses, this data contributes to the transparency and credibility of the study's conclusions.
@@
 $$
-
-Additionally, I probe the robustness of my findings against possible biases in self-reported mental health changes by comparing them with general mental health inquiries that do not reference the pandemic timeframe.
-
-$$
-y_{iasd} = \beta_1 \text{has\_son}_i + \beta_2 \text{has\_daughter}_i + \beta_3 \text{female\_headed}_i + \alpha_a + \delta_s + \Gamma X_i + \varepsilon_{iasd},
-$$
-
-In a related analysis, I explore how the presence of sons or daughters and female-headed households correlate with individual well-being, applying the same control variables and fixed effects as in the initial model.
 
@@
 ```
+I conducted an analysis that focused on key predictor variables, such as the number of COVID-19 cases and deaths per 100,000, the proportion of districts in designated COVID zones, and the different containment zone statuses like Red and Orange Zones.
+I aimed to find connections between these predictors and the mental health outcomes among women during the pandemic, focusing on changes in depression, tiredness, and safety concerns.
+
+To refine my models, I utilized logistic regression techniques, which  incorporated LASSO for variable selection.
+This approach was crucial in determining the strength and significance of relationships between the pandemic's containment measures and various mental health indicators.
+The results I uncovered were consistent with those of the original paper, indicating that containment measures such as lockdowns and restricted movements were associated with heightened feelings of depression and anxiety among women.
+
+In @fig-3, I presented my findings through estimated coefficients that measure the statistical significance and magnitude of the impact each predictor has on mental health outcomes.
+For instance, residing in a district with a high COVID-19 death rate was significantly associated with an increased likelihood of reporting feelings of depression and tiredness.
 

### 2024-04-19 outputs/paper.qmd
variables

@@
 ---
-title: "Tracing Hidden Struggles of Rural Indian Women during Pandemic"
+title: "Impact of Pandemic Policies on Rural Indian Women's Mental Health and Economic Stability"
 author: Ruoxian Wu
@@
 date-format: long
-abstract: "This paper replicates a pivotal study on the socio-economic impacts of pandemic containment policies on women in India, specifically examining mental health and financial status.
-Utilizing a dataset spanning several indicators of economic and psychological health, this study employs a combination of linear and Lasso regression models to assess the implications of these measures.
-Key findings suggest significant correlations between containment intensity and various aspects of women's well-being, including mental health and economic stability.
-The results underscore the importance of considering gender-specific outcomes in policy-making processes, particularly in times of global crises.
-This study contributes to the broader discourse on public health interventions and their gendered impacts, advocating for more nuanced approaches in future public health strategies."
+abstract: "This study replicates a research on the effects of pandemic containment policies on women in India, focusing on their mental health and financial status.
+The study uses a dataset that covers various indicators of economic and psychological health.
+It employs a combination of linear and Lasso regression models to evaluate the implications of these measures.
+The results reveal significant correlations between containment intensity and various aspects of women's well-being, such as mental health and economic stability.
+The findings highlight the significance of considering gender-specific outcomes in policy-making processes, particularly during global crises.
+This study contributes to the broader conversation on public health interventions and their gendered impacts.
+"
 format: pdf
@@
 
-The study "Women’s Well-being during a Pandemic and its Containment" from the Journal of Development Economics (2022) examines the effects of COVID-19 and related containment policies on women in lower-income countries @bau2022.
-My paper takes a close look at the original study's methodologies and outcomes.
-Using the data provided by the original authors, I replicated their research, applying fixed-effect analysis and regression models to assess how public health funding influences outcomes during health crises like COVID-19.
+This paper critically examines the impact of COVID-19 containment policies on rural Indian women and focuses on their mental health and financial stability.
+The original study titled "Women's Well-being during a Pandemic and its Containment" from the Journal of Development Economics (2022) laid a foundation by exploring the broader effects of the pandemic on women in lower-income countries.
+This paper replicates and extends the research to delve deeper into the specific challenges faced by women in rural India, a demographic that remains underrepresented in global discussions on public health and economic policy (@bau2022).
 
-This analysis reviews the complex links between funding, policy effectiveness, and socio-economic impacts.
-It revisits the original study's data and approach, enhancing our understanding of how health initiatives can better serve vulnerable populations during emergencies.
+The necessity of this study stems from the unique socio-economic conditions of rural India, where women face distinct challenges that are exacerbated by crises like the COVID-19 pandemic.
+Previous research has highlighted how pandemics disproportionately affect women, particularly in terms of increased domestic burdens, reduced economic opportunities, and heightened mental health issues.
+By focusing on rural Indian women, this study contributes to a nuanced understanding of how containment measures, while necessary to curb the spread of the virus, have had unintended adverse effects on this vulnerable subgroup.
 
-The original paper highlighted the decline in mental health, financial status, and meal nutrition for women due to pandemic policies (@bau2022).
-My work corroborates these findings and examines the balance needed between public health interventions and socio-economic support.
-Echoing findings from the World Health Organization (@who2020) and studies like that of @xie2021, my analysis confirms that strategic health investments are pivotal for crisis mitigation and socio-economic stability.
+The methodology of this paper involves a detailed analysis of data originally collected by the study from the Journal of Development Economics, enhanced by additional variables and refined econometric models.
+This replication employs a combination of fixed-effect analysis and advanced regression techniques to provide new insights into the interplay between public health policies and women's well-being.
 
-This paper aims to inform policy that effectively utilizes health funding to improve outcomes and support those most affected by health crises, highlighting the need for policies that are responsive to the socio-economic realities of women in low-income countries during pandemics.
+Through this structured analysis, the paper aims to inform effective policy-making that considers the socio-economic realities faced by rural Indian women.
+This study aims to ensure that future public health interventions are inclusive and equitable.
 
 # Data
+## Source and Provenance
+This analysis utilizes replication data associated with the article "Women’s well-being during a pandemic and its containment" from the Journal of Development Economics.
+The data, along with associated code, needs to be requested from "https://datasets.iza.org/dataset/1395/g2lm-lic-women-s-well-being-during-a-pandemic-and-its-containment" to facilitate the replication of key findings such as statistical models and graphical representations.
+
+## Data Collection and Cleaning
+The data was collected through a collaborative effort between local non-governmental organizations and academic researchers across six states in rural India.
+This collaboration ensured that high-quality, reliable data was collected, which reflected the unique socio-economic conditions of the surveyed regions.
+The survey was conducted among households that were initially interviewed in the fall of 2019, providing a critical pre-pandemic baseline.
+This baseline enhances our analysis of the changes attributable to COVID-19 containment policies.
+Part of data for this study was collected via phone interviews in August 2020 to ensure safety during the pandemic.
+The interviews covered a wide range of topics including demographic information, economic factors, and health outcomes.
+The study focused on mental health indicators and nutrition levels, which were measured using validated psychological scales like PHQ9 and GAD7, and food security questions adapted from national health surveys ().
+
+To ensure the robustness of the analysis, the initial phase of data cleaning involved several critical steps.
+The overall data distribution is anaylzed to understand the dataset.Missing values were cleaned to prepare for the modeling.
+The cleaning process also involved standardizing variable formats across the dataset to ensure consistency in analysis.
+
 ## Tools
@@
 For advanced modeling techniques, I utilized Glmnet [@glmnet] for Lasso regression.
-
-## Source
-
-This critical analysis utilizes replication data associated with the article "Women’s well-being during a pandemic and its containment" from the Journal of Development Economics.
-The data, along with associated code, needs to be requested from 'https://datasets.iza.org/dataset/1395/g2lm-lic-women-s-well-being-during-a-pandemic-and-its-containment' to facilitate the replication of key findings such as statistical models and graphical representations.
-By enabling the reproduction of the authors' analyses, this data contributes to the transparency and credibility of the study's conclusions.
-The replication package can be find and downloaded after requesting access.
 
@@
 
+### Model Variables:
+
+- `$y_{iasd}$`: The outcome variable for an individual, such as mental health or economic status.
+- `$\beta \text{containment}_d$`: Coefficient for containment policies in the individual's district, measuring the impact of these policies on the outcome.
+- `$\alpha_a$`: Age fixed effects to control for age-related variations in the outcome.
+- `$\delta_s$`: State fixed effects to account for differences attributable to the state of residence.
+- `$\Gamma X_i$`: Effects of control variables, including indicators for the district being in a red or orange zone during specific lockdown periods.
+- `$\epsilon_{iasd}$`: Error term capturing unobserved influences on the outcome.
+
 ```{r}
@@
 #| include: false
-# Load data
 # Load data
@@
 Figure 2 illustrates scatter plots that relate the containment measures to different outcomes, including anxiety, depression, exhaustion, lost income, reduced meals, and safety.
-The plots typically have the containment intensity on the x-axis and the outcome variable on the y-axis.
+The plots have the containment intensity on the x-axis and the outcome variable on the y-axis.
 The line represents the best-fit linear relationship between containment and the specific outcome.
@@
 These β values are all positive, indicating a direct correlation with containment levels, and the SE values (in parentheses) reflect the variability of the estimates within the clusters of districts.
-
-The results depicted in the figure provide valuable insights into the relative importance of predictor variables across different models.
-By visually presenting the estimated coefficients and their confidence intervals, this plot offers a clear and direct interpretation of the model results.
-Unlike the original paper, which relied on tables to illustrate the model results, this coefficient figure provides a more intuitive and easy-to-understand representation.
-The prominence of certain predictor variables, as indicated by larger effect sizes and narrower confidence intervals, suggests their stronger associations with the outcomes of interest.
-These findings have important implications for understanding the drivers of the observed outcomes and can inform targeted interventions and policy decisions.
-Overall, the use of this coefficient figure enhances the accessibility and comprehensibility of the model results, facilitating informed decision-making and further research endeavors.
-
-## Mental Health Deterioration
-The study documents a significant deterioration in mental health among the surveyed women, with increases in reported depression, exhaustion, and anxiety.
-These findings align with broader literature indicating that women, particularly in lower-income settings, bear a disproportionate burden of mental health challenges during crises.
 
@@
 This approach was crucial in determining the strength and significance of relationships between the pandemic's containment measures and various mental health indicators.
-The results I uncovered were consistent with those of the original paper, indicating that containment measures such as lockdowns and restricted movements were associated with heightened feelings of depression and anxiety among women.
+The results I uncovered were consistent with those of the original paper, indicating that containment measures such as lockdowns and restricted movements were associated with heightened feelings of depression and anxiety among women.The stricter containment measures correlate with poorer mental health and economic stability.
 
@@
 
-## Economic and Nutritional Impact
-Economically, the pandemic led to dramatic income losses and heightened food insecurity, with the latter particularly pronounced among women.
-The findings suggest that containment measures, while necessary for public health, inadvertently exacerbated these issues, underscoring the need for targeted support measures.
+The results depicted in the figure provide valuable insights into the relative importance of predictor variables across different models.
+By visually presenting the estimated coefficients and their confidence intervals, this plot offers a clear and direct interpretation of the model results.
+Unlike the original paper, which relied on tables to illustrate the model results, this coefficient figure provides a more intuitive and easy-to-understand representation.
 
 # Discussion
-## Socioeconomic Strain and Mental Health
-The data suggest that the socioeconomic strains induced by the pandemic, compounded by containment measures, have had a profound impact on women's mental health.
-This aligns with findings from other studies highlighting the disproportionate burden of mental health challenges on women during crises.
+## Mental Health Deterioration
+The study documents a significant deterioration in mental health among the surveyed women, with increases in reported depression, exhaustion, and anxiety.
+These findings align with broader literature indicating that women, particularly in lower-income settings, bear a disproportionate burden of mental health challenges during crises.
 For instance, (@smith2020) argue that women often bear the brunt of caregiving responsibilities and are more likely to experience stress and anxiety during crises due to increased caregiving demands and economic vulnerability.
@@
 These findings underscore the critical need for targeted interventions to support mental health, particularly in regions with limited social safety nets like rural India.
+
+## Economic and Nutritional Impact
+The study indicates that pandemics can cause economic instability, particularly affecting marginalized communities.
+While containment measures reduce the spread of COVID-19, they have inadvertently deepened economic disparities, leading to significant income reductions and compromised food security.
+This observation aligns with previous research, which has shown that economic shocks have a disproportionate impact on low-income populations, exacerbating poverty and reducing access to essential resources (@Patel2019Economic).
+
+The economic strain has a cascading effect on nutrition, as evidenced by the increased instances of meal reductions among the affected populations.
+This link between economic instability and nutritional outcomes is well-documented, with studies illustrating how economic downturns directly impact dietary quality and overall health in rural settings (@Martin2020Economic).
+The nutritional deficits noted in this study underscore the need for integrated policy responses that address both the immediate and long-term economic and nutritional needs of vulnerable groups.
+Policies aimed at enhancing food security must be coupled with economic support measures to effectively counteract the adverse effects of pandemic-related disruptions.
+These interventions should prioritize the distribution of food aid, support for local agriculture, and programs that provide direct financial support to those most at risk of economic and nutritional instability.
 
@@
 
+# Conclusion
 In conclusion, the analysis affirms the significant negative repercussions of the COVID-19 pandemic and associated containment measures on women's mental health and economic stability in rural India.
-It underscores the necessity of designing and implementing nuanced public health policies that account for the socioeconomic realities of vulnerable populations and prioritize their well-being.
+The findings emphasize the pressing need for public health policies that are not only effective in controlling the spread of diseases but also considerate of the socioeconomic realities of the populations they impact.
+By taking these factors into account while making policies, we can strive to not only manage public health crises more efficiently but also reduce their harmful impacts on vulnerable populations.
 

### 2024-04-19 outputs/paper.qmd
labels

@@
       model_data <- tidy(models[[model_name]])
-      model_data$model <- rename_vars[model_name] %>% coalesce(model_name)  # Rename the model name
-      model_data$term <- rename_vars[model_data$term] %>% coalesce(model_data$term)  # Rename the terms
+      model_data$model <- rename_vars[model_name] %>% coalesce(model_name)  
+      model_data$term <- rename_vars[model_data$term] %>% coalesce(model_data$term)  
       return(model_data)

### 2024-04-19 scripts/04_tables_and_figures.R
delete

@@ -1,129 +1,0 @@
-library(ggplot2)
-library(dplyr)
-library(haven)
-library(fixest)
-
-
-covid_data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
-covid_data <- covid_data %>%
-  filter(!is.na(tran_inc_normal), !is.na(tran_inc_current))
-
-theme_set(theme_minimal(base_size = 15) +
-            theme(text = element_text(family = "Times New Roman"),
-                  plot.title = element_text(size = 20),
-                  plot.subtitle = element_text(size = 18),
-                  axis.title = element_text(size = 18),
-                  axis.text = element_text(size = 15)))
-
-# fig1
-p1a <- ggplot(covid_data, aes(x = tran_inc_normal)) +
-  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
-  geom_histogram(data = covid_data, aes(x = tran_inc_current, y = ..density..), 
-                 color = "black", fill = NA, bins = 30) +
-  labs(title = "Distributions of Transformed Income",
-       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
-       y = "Density") +
-  scale_fill_manual(values = c("gray", "black"),
-                    labels = c("Normal Month", "Current Month")) +
-  scale_color_manual(values = c("gray", "black"),
-                     labels = c("Normal Month", "Current Month")) +
-  theme(legend.title = element_blank(), legend.position = "bottom")
-
-ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)
-
-
-output_path <- "/cloud/project/outputs"
-
-# Load data
-data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
-
-# Prepare the variables
-data <- data %>%
-  mutate(
-    inc_lost = tran_inc_normal - tran_inc_current,
-    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
-    ind_meals_reduced = as.numeric(ind_meals_reduced),
-    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
-    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
[…]

### 2024-04-19 scripts/fig_1b.R

@@ -1,63 +1,0 @@
-# Load the necessary packages
-library(foreign) 
-library(ggplot2) 
-library(dplyr)  
-library(broom) 
-library(lmtest)
-library(sandwich) 
-
-# Set file paths
-data_path <- "/cloud/project/data/raw_data/"
-output_path <- "/cloud/project/outputs"
-
-# Load data
-data <- read_dta("/cloud/project/data/raw_data/covid_gender_data.dta")
-
-# Prepare the variables
-data <- data %>%
-  mutate(
-    inc_lost = tran_inc_normal - tran_inc_current,
-    ind_inc_lost = ifelse(inc_lost > 0, 1, NA),
-    ind_meals_reduced = as.numeric(ind_meals_reduced),
-    ind_fem_depression_change = as.numeric(ind_fem_depression_change),
-    ind_fem_worried_change = as.numeric(ind_fem_worried_change),
-    ind_fem_tired_change = as.numeric(ind_fem_tired_change),
-    ind_fem_safety_change = as.numeric(ind_fem_safety_change)
-  )
-
-# Function to fit model and get tidy output
-get_model_summary <- function(dependent_var) {
-  model <- lm(as.formula(paste(dependent_var, "~ 1")), data = data)
-  tidy_model <- tidy(model, conf.int = TRUE)
-  tidy_model$term <- dependent_var
-  return(tidy_model)
-}
-
-# Run models for each outcome
-model_summaries <- bind_rows(
-  get_model_summary("ind_inc_lost"),
-  get_model_summary("ind_meals_reduced"),
-  get_model_summary("ind_fem_depression_change"),
-  get_model_summary("ind_fem_worried_change"),
-  get_model_summary("ind_fem_tired_change"),
-  get_model_summary("ind_fem_safety_change")
-)
-
-y_labels <- c(
-  "ind_inc_lost" = "Lost Income",
-  "ind_meals_reduced" = "Reduced Meals",
-  "ind_fem_depression_change" = "More Depressed",
-  "ind_fem_worried_change" = "More Anxious",
-  "ind_fem_tired_change" = "More Exhausted",
-  "ind_fem_safety_change" = "Less Safe"
-)
-
-# Plotting
-coef_plot <- ggplot(model_summaries, aes(x = estimate, y = term, xmin = conf.low, xmax = conf.high)) +
-  geom_pointrange() +
-  scale_y_discrete(labels = y_labels) +
[…]

### 2024-04-19 scripts/fix.R

@@ -1,46 +1,0 @@
-# Load necessary libraries
-library(dplyr)
-library(ggplot2)
-library(lme4)
-library(Metrics)
-library(caret)
-library(randomForest)
-
-# Load data
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-data <- read_dta(data_file)
-
-# Filter data based on non-missing values for certain variables and other conditions
-filtered_data <- data %>%
-  filter(
-    !is.na(ind_fem_depression_change) &  # Ensure no missing data on depression change indicator
-      !is.na(ind_fem_tired_change) &       # Ensure no missing data on tiredness change indicator
-      !is.na(ind_fem_worried_change) &     # Ensure no missing data on worry change indicator
-      !is.na(ind_fem_safety_change) &      # Ensure no missing data on safety change indicator
-      final_status == 1 | final_status == 2  # Final status must be 1 or 2
-  )
-
-# You might also need to include epidemiological variables if they are used as part of the conditions
-# For example, ensuring non-missing values for cases and deaths per 100,000 if they are used in the models
-filtered_data <- filtered_data %>%
-  filter(
-    !is.na(cases_per_100000) & 
-      !is.na(deaths_per_100000) &
-      cases_per_100000 >= 0 &   # Example condition: cases must be non-negative
-      deaths_per_100000 >= 0    # Example condition: deaths must be non-negative
-  )
-
-# Assuming additional demographic controls are needed:
-filtered_data <- filtered_data %>%
-  filter(
-    !is.na(geo_state) &       # Ensure geographic state data is not missing
-      !is.na(fem_resp_age) &    # Ensure respondent's age is not missing
-      fem_resp_age >= 18        # Example condition: respondent must be an adult
-  )
-
-# Output filtered data for inspection or further analysis
-write.csv(filtered_data, "/cloud/project/data/cleaned/Filtered_Covid_Gender_Data.csv", row.names = FALSE)
-
-# Summary to check how many rows are left after filtering
-print(paste("Filtered dataset contains", nrow(filtered_data), "observations."))

### 2024-04-19 scripts/models.R

@@ -1,47 +1,0 @@
-# Load necessary libraries
-library(dplyr)
-library(glmnet)
-
-# Set the data path and load the data
-data_path <- "/cloud/project/data/cleaned/"
-data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
-filtered_data <- read.csv(data_file)
-
-# Data preprocessing: Adding squared and cubic terms for cases and deaths
-filtered_data <- filtered_data %>%
-  mutate(
-    cases_sq = cases_per_100000^2,
-    cases_cube = cases_per_100000^3,
-    deaths_sq = deaths_per_100000^2,
-    deaths_cube = deaths_per_100000^3
-  )
-
-# Ensuring no NA values in the dataset for the variables used in modeling
-filtered_data <- filtered_data %>%
-  filter(
-    !is.na(ind_fem_depression_change) & 
-      !is.na(dist_prop_covid_zone) & 
-      !is.na(cases_per_100000) & 
-      !is.na(deaths_per_100000) & 
-      !is.na(geo_state) & 
-      !is.na(fem_resp_age)
-  )
-
-# Basic linear regression model with specified controls
-basic_model <- lm(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + deaths_per_100000 + geo_state + fem_resp_age, data = filtered_data)
-print(summary(basic_model))
-
-# Model with polynomial terms
-poly_model <- lm(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + cases_sq + cases_cube + deaths_per_100000 + deaths_sq + deaths_cube + geo_state + fem_resp_age, data = filtered_data)
-print(summary(poly_model))
-
-# Preparing data for Lasso model
-x <- model.matrix(ind_fem_depression_change ~ dist_prop_covid_zone + cases_per_100000 + cases_sq + cases_cube + deaths_per_100000 + deaths_sq + deaths_cube + geo_state + fem_resp_age - 1, data = filtered_data)
-y <- filtered_data$ind_fem_depression_change
-
-# Fit Lasso model
-lasso_model <- cv.glmnet(x, y, alpha = 1)  # alpha=1 for lasso
-print(coef(lasso_model, s = "lambda.min"))
-
-# Plot the cross-validated error
-plot(lasso_model)

### 2024-04-19 scripts/refine_model.R

@@ -1,161 +1,0 @@
-library(haven)       # for reading Stata data files
-library(dplyr)       # for data manipulation
-library(glmnet)      # for LASSO regression
-library(hdm)         # for high-dimensional metrics, including double selection LASSO
-library(stargazer)   # for producing publication-quality regression tables
-library(plm)         # for panel data analysis
-library(tidyr)
-library(ggplot2)
-library(fixest)       # for fixed-effects regressions
-library(lfe)          # for regressions with multiple fixed effects and clustering
-library(modelsummary)
-
-data_path <- "/cloud/project/data/cleaned/"
-data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
-data <- read.csv(data_file)
-
-# Ensure factor variables are correctly formatted
-data <- mutate(data,
-               across(c(geo_state, color_zone, demo_caste, demo_religion, fem_marital_status), as.factor))
-
-# Recoding '99' to NA for relevant factor variables
-data$demo_caste <- as.character(data$demo_caste)  # Convert to character to manipulate
-data$demo_caste[data$demo_caste == "99"] <- NA    # Change '99' to NA
-data$demo_caste <- factor(data$demo_caste)        # Convert back to factor
-
-data$demo_religion <- as.character(data$demo_religion)
-data$demo_religion[data$demo_religion == "99"] <- NA
-data$demo_religion <- factor(data$demo_religion)
-
-data$fem_marital_status <- as.character(data$fem_marital_status)
-data$fem_marital_status[data$fem_marital_status == "99"] <- NA
-data$fem_marital_status <- factor(data$fem_marital_status)
-
-
-
-# Handling NA values in key factor variables
-
-response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change",
-                   "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
-
-predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
-                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
-
-
-
-# Create an empty list to store models
-models <- list()
-
-# Loop through each response variable and fit a logistic regression model
-for (response in response_vars) {
-  formula <- as.formula(paste(response, "~", paste(predictors, collapse = " + ")))
[…]

### 2024-04-19 scripts/separated_model.R

@@ -1,25 +1,0 @@
-library(lme4)
-library(haven)
-
-# Load your data
-data <- read_dta(paste0(data_path, "covid_gender_data.dta"))
-
-# Assume 'geo_state' is already factored correctly, but let's factorize 'fem_resp_age' if it's not done yet
-data$fem_resp_age <- factor(data$fem_resp_age)
-
-# Prepare the rest of the data, making sure to handle missing values appropriately.
-# It could involve imputation or removing variables with excessive missingness.
-
-# Define the outcome variable and the predictors
-outcome_var <- "ind_fem_depression_change"
-predictors <- c("cases_per_100000", "deaths_per_100000", "dist_prop_covid_zone", 
-                "red_zone", "orange_zone", "tran_inc_normal", "asset_index")
-
-# For simplicity, I'll just run a random effects model for the outcome 'ind_fem_depression_change'.
-# You would repeat the process for each outcome variable of interest.
-# Here '(1 | geo_state)' adds random intercepts for states.
-std_model <- glm(as.formula(paste(outcome_var, "~", paste(predictors, collapse = " + "))),
-                 family = binomial(link = "logit"), data = data)
-
-# Check the summary of the standard model
-summary(std_model)

### 2024-04-19 scripts/table1_1.R

@@ -1,81 +1,0 @@
-library(haven)       # For read_dta
-library(dplyr)       # For data manipulation
-library(glmnet)      # For lasso regression
-library(corrplot)
-
-# Paths to the data
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-
-# Load the data
-data <- read_dta(data_file)
-
-# Identify all predictors including the ones starting with 'asset_'
-predictors <- c("dist_prop_covid_zone", "geo_state", "fem_resp_age", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", grep("^asset_", names(data), value = TRUE), "ind_fem_resp_edu")
-
-# Filter out rows with any NA values across all these predictors and the response variable
-data_filtered <- data %>%
-  filter(!is.na(ind_fem_worried_change)) %>%
-  filter(rowSums(is.na(select(., all_of(predictors)))) == 0)
-
-# Build the predictor string for the model matrix
-predictor_formula <- paste(predictors, collapse = " + ")
-full_formula <- as.formula(paste("~", predictor_formula, "- 1"))
-
-# Create the model matrix from the filtered data
-x_matrix <- model.matrix(full_formula, data = data_filtered)
-
-# Create y_vector from the same filtered data
-y_vector <- data_filtered$ind_fem_worried_change
-
-# Check dimensions to confirm they match
-if (nrow(x_matrix) == length(y_vector)) {
-  # Proceed with lasso model
-  lasso_model <- cv.glmnet(x_matrix, y_vector, alpha = 1, family = "binomial")
-  cat("Lasso model successfully fitted.\n")
-} else {
-  cat("Mismatch in dimensions found: x_matrix rows:", nrow(x_matrix), ", y_vector length:", length(y_vector), "\n")
-}
-
-# Check and add in-sample1 variable if lasso model is fitted
-if (exists("lasso_model")) {
-  selected <- which(coef(lasso_model, s = "lambda.min")[-1] != 0)
-  data_filtered$in_sample1 <- ifelse(seq_len(nrow(data_filtered)) %in% selected, 1, 0)
-}
-
-# Plotting the coefficient path
-plot(lasso_model, xvar = "lambda", label = TRUE)
-
-# Plotting cross-validated error
[…]

### 2024-04-19 scripts/table_1.R

@@ -1,158 +1,0 @@
-library(plm)
-library(lmtest)
-library(sandwich)
-library(stargazer)
-library(glmnet)
-library(dplyr)
-library(haven)  # For read_dta if haven is used
-
-# Load the data
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-data <- read_dta(data_file)
-
-# Convert appropriate columns to factors
-data$geo_state <- as.factor(data$geo_state)
-data$fem_resp_age <- as.factor(data$fem_resp_age)
-data$final_status <- as.factor(data$final_status)
-
-# Filter data with complete cases for required variables
-data_filtered <- data %>%
-  filter(!is.na(cases_per_100000) & !is.na(deaths_per_100000) & !is.na(red_zone) & 
-           !is.na(orange_zone) & !is.na(geo_state) & !is.na(fem_resp_age)) %>%
-  filter(!is.na(ind_fem_depression_change) & !is.na(ind_fem_tired_change) &
-           !is.na(ind_fem_worried_change) & !is.na(ind_fem_safety_change) &
-           final_status %in% c("1", "2"))
-
-# Check the number of remaining observations
-print(paste("Filtered data contains", nrow(data_filtered), "observations."))
-
-# Define response and predictor variables
-response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", "ind_fem_worried_change", "ind_fem_safety_change", "mental_index_change")
-
-# Generate dummy variables for categorical predictors
-dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
-
-# Combine the dummies and other predictors
-predictors <- c("dist_prop_covid_zone", "red_zone", "orange_zone", "cases_per_100000", "deaths_per_100000", "tran_inc_normal", "asset_index", "ind_fem_resp_edu")
-x <- cbind(dummies, data_filtered[, predictors])
-
-# Check for constant columns in x to avoid issues in glmnet
-x <- x[, sapply(x, function(col) length(unique(col)) > 1)]
-
-# Convert to matrix for glmnet
-x_matrix <- as.matrix(x)
-
-x_matrix_imputed <- apply(x_matrix, 2, function(column) {
-  if (any(is.na(column))) {
-    column[is.na(column)] <- median(column, na.rm = TRUE)
-  }
-  return(column)
-})
-
-# Convert back to matrix if needed
[…]

### 2024-04-19 scripts/tables.R

@@ -1,143 +1,0 @@
-library(plm)
-library(lmtest)
-library(sandwich)
-library(stargazer)
-library(glmnet)
-library(dplyr)
-library(readstata13)
-
-# Set file paths
-data_path <- "/cloud/project/data/raw_data/"
-data_file <- paste0(data_path, "covid_gender_data.dta")
-
-data <- read_dta(data_file)
-
-
-
-# First, ensure the necessary columns are properly formatted
-data$geo_state <- as.factor(data$geo_state)
-data$fem_resp_age <- as.factor(data$fem_resp_age)
-data$final_status <- as.factor(data$final_status)
-
-# Apply complete.cases to ensure all specified columns are complete
-data_complete <- data %>%
-  filter(complete.cases(cases_per_100000, deaths_per_100000, red_zone, orange_zone, geo_state, fem_resp_age))
-
-# Check how many rows are left after applying complete.cases
-print(paste("After complete.cases:", nrow(data_complete)))
-
-# Now filter out rows with any NA in the specified response variables
-data_filtered <- data_complete %>%
-  filter(!is.na(ind_fem_depression_change) & 
-           !is.na(ind_fem_tired_change) &
-           !is.na(ind_fem_worried_change) & 
-           !is.na(ind_fem_safety_change))
-
-
-
-# Finally, filter by final_status
-data_filtered <- data_filtered %>%
-  filter(final_status %in% c("1", "2"))
-
-# Check the number of rows
-print(paste("After filtering by final_status:", nrow(data_filtered)))
-
-# If data_filtered is empty, you may need to relax some conditions or check the data quality
-if(nrow(data_filtered) == 0) {
-  cat("No data left after filtering. Check criteria or data quality.")
-}
-
-
-# Define response and predictor variables
-response_vars <- c("ind_fem_depression_change", "ind_fem_tired_change", 
-                   "ind_fem_worried_change", "ind_fem_safety_change", 
-                   "mental_index_change")
-predictors <- c("dist_prop_covid_zone", "red_zone", "orange_zone", 
-                "cases_per_100000", "deaths_per_100000", "tran_inc_normal", 
-                "asset_index", "ind_fem_resp_edu")
-
-# Generate dummy variables for categorical predictors
-dummies <- model.matrix(~ geo_state + fem_resp_age - 1, data = data_filtered)
-
-# Combine the dummies and other predictors
-x <- cbind(dummies, data_filtered[, predictors])
-
-# Convert to a matrix for glmnet
[…]

### 2024-04-19 outputs/paper.qmd
figure legend

@@
 # Model
-Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.
-
-I employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables.
+Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.I employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables.
 Myoutcome of interest reflects various personal experiences, with containment representing the intensity of policy measures in one's district.
-
 The model accounts for age and state as non-varying influences, along with controls for local COVID-19 severity and pre-pandemic socioeconomic factors to mitigate potential confounding effects.
@@
 
-### Model Variables:
+## Model Variables:
 
-- `$y_{iasd}$`: The outcome variable for an individual, such as mental health or economic status.
-- `$\beta \text{containment}_d$`: Coefficient for containment policies in the individual's district, measuring the impact of these policies on the outcome.
-- `$\alpha_a$`: Age fixed effects to control for age-related variations in the outcome.
-- `$\delta_s$`: State fixed effects to account for differences attributable to the state of residence.
-- `$\Gamma X_i$`: Effects of control variables, including indicators for the district being in a red or orange zone during specific lockdown periods.
-- `$\epsilon_{iasd}$`: Error term capturing unobserved influences on the outcome.
+- $y_{iasd}$: The outcome variable for an individual, such as mental health or economic status.
+- $\beta \text{containment}_d$: Coefficient for containment policies in the individual's district, measuring the impact of these policies on the outcome.
+- $\alpha_a$: Age fixed effects to control for age-related variations in the outcome.
+- $\delta_s$: State fixed effects to account for differences attributable to the state of residence.
+- $\Gamma X_i$: Effects of control variables, including indicators for the district being in a red or orange zone during specific lockdown periods.
+- $\epsilon_{iasd}$: Error term capturing unobserved influences on the outcome.
 
@@
 #| message: false
+#| fig-width: 8 
+#| fig-height: 4 
 #| fig-subcap: ["Effect Sizes of Predictors in Mental Health Models", "Effect Sizes of Predictors in Economic and Nutritional Impact Models"]
@@
     theme(legend.title = element_blank(),
-          legend.position = "bottom")
+          legend.position = "right")
 }
@@
 ```
+
 I conducted an analysis that focused on key predictor variables, such as the number of COVID-19 cases and deaths per 100,000, the proportion of districts in designated COVID zones, and the different containment zone statuses like Red and Orange Zones.

### 2024-04-19 scripts/03_tests.R
tests

@@ -1,15 +1,51 @@
 # Load necessary libraries
-library(ggplot2)
 
-# Plotting the distribution of transformed income
-p1a <- ggplot(data, aes(x = tran_inc_normal)) +
-  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
-  labs(title = "Distributions of Transformed Income", x = "Inverse Hyperbolic Sin of Income (in Rs.)", y = "Density")
-ggsave("/cloud/project/outputs/figures/income_distribution.png", plot = p1a, width = 10, height = 8, dpi = 300)
+data_path <- "/cloud/project/data/cleaned/"
+data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
+data <- read.csv(data_file)
+# Check for Missing Values
+test_missing_values <- any(is.na(data))
 
-# Figure for comparing two periods of income
-p_comparison <- ggplot(data, aes(x = tran_inc_normal)) +
-  geom_histogram(aes(y = ..density..), bins = 30, fill = "blue", alpha = 0.5) +
-  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), bins = 30, fill = "red", alpha = 0.5) +
-  labs(title = "Comparison of Income During Normal and Current Periods")
-ggsave("/cloud/project/outputs/figures/income_period_comparison.png", plot = p_comparison, width = 10, height = 8, dpi = 300)
+# Test for Unique IDs
+test_unique_ids <- length(unique(data$geo_uq_hhid_str)) == nrow(data)
+
+# Validate Final Status Values
+test_final_status <- all(data$final_status %in% c(1, 2)) # Assuming 1 and 2 are the only valid values
+
+# Confirm State IDs Correspond to States
+test_state_ids <- all(data$geo_state == substr(data$geo_state_id_str, 1, 2))
+
+# District Consistency Check
+test_district_consistency <- all(data$geo_district == substr(data$geo_district_id_str, 1, 3))
+
+# Check Population Figures
+test_population_figures <- all(data$district_population > 0 & data$district_population < 1000000) # Example range
+
+# Case Numbers Sanity Check
+test_case_numbers <- all(data$total_cases >= 0 & data$total_deaths >= 0)
+
+# Verify Proportion in COVID Zone
+test_covid_zone_proportion <- all(data$dist_prop_covid_zone >= 0 & data$dist_prop_covid_zone <= 1)
+
+# Check Zone Assignments
[…]

### 2024-04-19 scripts/03_tests.R
sketches

@@ -3,6 +3,7 @@
 data_path <- "/cloud/project/data/cleaned/"
 data_file <- paste0(data_path, "Filtered_Covid_Gender_Data.csv")
 data <- read.csv(data_file)
+
 # Check for Missing Values
 test_missing_values <- any(is.na(data))
 
@@ -49,3 +50,23 @@ test_results <- list(
 
 # Output the results
 test_results
+
+# 1. Histogram of a numeric variable (e.g., cases_per_100000)
+ggplot(data, aes(x = cases_per_100000)) +
+  geom_histogram(binwidth = 1, fill = 'blue', color = 'black') +
+  labs(title = "Distribution of COVID-19 Cases per 100,000", x = "Cases per 100,000", y = "Frequency")
+
+# 2. Boxplot for a categorical variable against a numeric variable 
+ggplot(data, aes(x = as.factor(geo_state), y = total_cases)) +
+  geom_boxplot() +
+  labs(title = "Total COVID-19 Cases by State", x = "State", y = "Total Cases")
+
+# 3 . Boxplot for a categorical variable against a numeric variable (e.g., economic status by state)
+ggplot(data, aes(x = as.factor(ind_fem_depression_change), y = total_cases)) +
+  geom_boxplot() +
+  labs(title = "More Depressed", x = "yes/no", y = "Total Cases")
+
+# 4. Scatter plot with two numerical variables (e.g., cases_per_100000 vs. deaths_per_100000)
+ggplot(data, aes(x = cases_per_100000, y = deaths_per_100000)) +
+  geom_point(aes(color = as.factor(geo_state))) +
+  labs(title = "COVID-19 Cases vs. Deaths per 100,000 by State", x = "Cases per 100,000", y = "Deaths per 100,000", color = "State")
